---
title: "09a_Antecedent_Conditions_models"
author: "Jake Cavaiani, Tamara Harms"
date: "9/2/2022, edited 9/22/2025"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---
The purpose of this script is to model HI/BETA against storm attributes, antecedent moisture conditions, and seasonality for each individual catchment and constituent using linear regression 

Input: Antecedent moisture conditions with HI_FI_BETA and catchment characteristics!

Step 1) import full file 
Step 2) standardize and center the data
Step 3) Model! Model structure is lm(Hyst_index ~ StormPrecip + PrecipWeek + PrecipMonth + TimeSinceChena_z, data = HI_FI_NO3_xxxx)
Step 4) Check model assumptions
Step 5) Plot all models 

Output: linear model plot 

```{r load-packages, include=FALSE}
library(magrittr)
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(data.table)
library(scales)
library(lme4)
library(nlme)
library(datasets)
library(arm)
library(AICcmodavg)
library(gridExtra)
library(grid)
library(ggpmisc)
library(boot)
library(here)
library(broom)
library(viridis)
library(car)
library(MuMIn)
library(ggeffects)
library(dotwhisker)
library(jtools)
library(GGally)

```

```{r}
# Read in data # 

AMC <- read.csv(here("Output_from_analysis", "compare_JSC_ATW_storm_totals", "updated_AMC_HI_BETA_file_2509.csv"))

AMC <- AMC %>% mutate(date = as.Date(date, format = "%Y-%m-%d")) %>%
               mutate(year = format(date, "%Y"))

```

```{r, echo=FALSE}
### Prelim visualize data ###
pNO3 <- AMC %>% filter(response_var == "NO3")
ggpairs(pNO3, columns = c("precip.week", "precip.month", "ThreeMonth", "temp.week", "Intensity", "TimeSinceChena_z", "Hyst_index"), mapping = aes(color = site.ID))

NO3_POKE <- AMC %>% filter(response_var == "NO3") %>% filter(site.ID == "VAUL")
ggpairs(NO3_POKE, columns = c("precip.week", "precip.month", "ThreeMonth", "Intensity", "TimeSinceChena_z", "Hyst_index"), mapping = aes(color = as.factor(year)))

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena_z + Hyst_index, data = NO3_POKE, col = as.factor(NO3_POKE$year))

```
### Uncorrelated antecedent conditions to include: precip.week, precip.month, Intensity, TimeSinceChena_z
## precip.week & precip.month might be correlated for some years and are correlated across all years. Using year as random effect

### Scaling and normalizing data ### 
```{r, echo=FALSE}

# scale & standardize predictors # 
# add hard code ln-HI & beta for use w/ ggpairs plotting
varnames <- c("precip.week", "precip.month", "ThreeMonth", "Intensity", "TimeSinceChena_z")
AMC <- AMC %>% mutate(across(starts_with(varnames), ~as.numeric(scale (., center = TRUE, scale = TRUE)), .names = "{.col}_z")) %>%
               mutate(TimeSinceChena_z_cent = as.numeric(scale(TimeSinceChena_z, center = TRUE, scale = FALSE))) %>%
               mutate(ln_HI = log(Hyst_index + 1)) %>%
               mutate(ln_beta = log(Beta_index + 7))
  

```

```{r}
#########################
### Regression models ###
#########################
### HI ###
## NO3 ##

# MOOS #
pairs <- AMC %>% filter(site.ID == "MOOS" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_lnNO3_MOOS_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.no3.moos.lmer <- AMC %>% filter(site.ID == "MOOS" & response_var == "NO3") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.no3.moos.lmer)
qqnorm(resid(hi.no3.moos.lmer,  type = "pearson"))
qqline(resid(hi.no3.moos.lmer,  type = "pearson"))
plot(hi.no3.moos.lmer)
summary(hi.no3.moos.lmer)
confint(hi.no3.moos.lmer)
r.squaredGLMM(hi.no3.moos.lmer)

## Check effect of outlier
mod1.out <- AMC %>% filter(site.ID == "MOOS" & response_var == "NO3") %>%
                    filter(precip.week_z < 2) %>%
                    lmer(Hyst_index ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

summary(mod1.out)
confint(mod1.out)
# Same qualitative result

# FRCH #
pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_NO3_FRCH_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.no3.frch.lmer <- AMC %>% filter(site.ID == "FRCH" & response_var == "NO3") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.no3.frch.lmer)
qqnorm(resid(hi.no3.frch.lmer,  type = "pearson"))
qqline(resid(hi.no3.frch.lmer,  type = "pearson"))
plot(hi.no3.frch.lmer)
summary(hi.no3.frch.lmer)
confint(hi.no3.frch.lmer)
r.squaredGLMM(hi.no3.frch.lmer)

# POKE #
pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_NO3_POKE_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.no3.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "NO3") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.no3.poke.lmer)
# ppt month & week too strongly correlated

# Remove precip.week from model
hi.no3.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "NO3") %>%
                lmer(ln_HI ~ precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.no3.poke.lmer)
qqnorm(resid(hi.no3.poke.lmer,  type = "pearson"))
qqline(resid(hi.no3.poke.lmer,  type = "pearson"))
plot(hi.no3.poke.lmer)
summary(hi.no3.poke.lmer)
confint(hi.no3.poke.lmer)
r.squaredGLMM(hi.no3.poke.lmer)

## Random var = 0. Check lm
mod3.lm <- AMC %>% filter(site.ID == "POKE" & response_var == "NO3") %>%
                lm(ln_HI ~ precip.month_z + TimeSinceChena_z + Intensity_z, data = .)
summary(mod3.lm)
# same qualitative result. Nothing significant.

# CARI #
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z_cent", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_NO3_CARI_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.no3.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "NO3") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.no3.cari.lmer)
# ppt month & week too strongly correlated

# Remove precip.week from model
hi.no3.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "NO3") %>%
                lmer(ln_HI ~ precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.no3.cari.lmer)
qqnorm(resid(hi.no3.cari.lmer,  type = "pearson"))
qqline(resid(hi.no3.cari.lmer,  type = "pearson"))
plot(hi.no3.cari.lmer)
summary(hi.no3.cari.lmer)
confint(hi.no3.cari.lmer)
r.squaredGLMM(hi.no3.cari.lmer)

# STRT #
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_NO3_STRT_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.no3.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "NO3") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.no3.strt.lmer)
#ppt_week & ppt_month too strongly correlated

hi.no3.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "NO3") %>%
                lmer(ln_HI ~ precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.no3.strt.lmer)
qqnorm(resid(hi.no3.strt.lmer,  type = "pearson"))
qqline(resid(hi.no3.strt.lmer,  type = "pearson"))
plot(hi.no3.strt.lmer)
summary(hi.no3.strt.lmer)
confint(hi.no3.strt.lmer)
r.squaredGLMM(hi.no3.strt.lmer)

# VAUL #
pairs <- AMC %>% filter(site.ID == "VAUL" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_NO3_VAUL_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

NO3_VAUL <- AMC %>% filter(response_var == "NO3") %>% filter(site.ID == "VAUL")

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena_z + ln_HI, data = NO3_VAUL, col = as.factor(NO3_VAUL$year))

hi.no3.vaul.lmer <- AMC %>% filter(site.ID == "VAUL" & response_var == "NO3") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.no3.vaul.lmer)
qqnorm(resid(hi.no3.vaul.lmer,  type = "pearson"))
qqline(resid(hi.no3.vaul.lmer,  type = "pearson"))
plot(hi.no3.vaul.lmer)
summary(hi.no3.vaul.lmer)
confint(hi.no3.vaul.lmer)
r.squaredGLMM(hi.no3.vaul.lmer)
```

```{r}
## fDOM ##

# MOOS #
pairs <- AMC %>% filter(site.ID == "MOOS" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_fDOM_MOOS_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.fdom.moos.lmer <- AMC %>% filter(site.ID == "MOOS" & response_var == "fDOM") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.fdom.moos.lmer)
qqnorm(resid(hi.fdom.moos.lmer,  type = "pearson"))
qqline(resid(hi.fdom.moos.lmer,  type = "pearson"))
plot(hi.fdom.moos.lmer)
summary(hi.fdom.moos.lmer)
confint(hi.fdom.moos.lmer)
r.squaredGLMM(hi.fdom.moos.lmer)

# random var = 0. Compare w/ lm
hi.fdom.moos.lm <- AMC %>% filter(site.ID == "MOOS" & response_var == "fDOM") %>%
                lm(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z, data = .)
summary(hi.fdom.moos.lm)
# qualitatively same as lmer

# FRCH #
pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_fDOM_FRCH_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.fdom.frch.lmer <- AMC %>% filter(site.ID == "FRCH" & response_var == "fDOM") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.fdom.frch.lmer)
qqnorm(resid(hi.fdom.frch.lmer,  type = "pearson"))
qqline(resid(hi.fdom.frch.lmer,  type = "pearson"))
plot(hi.fdom.frch.lmer)
summary(hi.fdom.frch.lmer)
confint(hi.fdom.frch.lmer)
r.squaredGLMM(hi.fdom.frch.lmer)

# CARI #
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_fDOM_CARI_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.fdom.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "fDOM") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.fdom.cari.lmer)
# ppt week & ppt month too strongly correlated

hi.fdom.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "fDOM") %>%
                lmer(ln_HI ~ precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.fdom.cari.lmer)
qqnorm(resid(hi.fdom.cari.lmer,  type = "pearson"))
qqline(resid(hi.fdom.cari.lmer,  type = "pearson"))
plot(hi.fdom.cari.lmer)
summary(hi.fdom.cari.lmer)
confint(hi.fdom.cari.lmer)
r.squaredGLMM(hi.fdom.cari.lmer)

pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_fDOM_POKE_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.fdom.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "fDOM") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.fdom.poke.lmer)
# ppt week & ppt month too strongly correlated

hi.fdom.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "fDOM") %>%
                lmer(ln_HI ~ precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.fdom.poke.lmer)
qqnorm(resid(hi.fdom.poke.lmer,  type = "pearson"))
qqline(resid(hi.fdom.poke.lmer,  type = "pearson"))
plot(hi.fdom.poke.lmer)
summary(hi.fdom.poke.lmer)
confint(hi.fdom.poke.lmer)
r.squaredGLMM(hi.fdom.poke.lmer)

# STRT #
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_fDOM_STRT_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.fdom.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "fDOM") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.fdom.strt.lmer)
qqnorm(resid(hi.fdom.strt.lmer,  type = "pearson"))
qqline(resid(hi.fdom.strt.lmer,  type = "pearson"))
plot(hi.fdom.strt.lmer)
summary(hi.fdom.strt.lmer)
confint(hi.fdom.strt.lmer)
r.squaredGLMM(hi.fdom.strt.lmer)

# VAUL #
pairs <- AMC %>% filter(site.ID == "VAUL" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_fDOM_VAUL_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

fdom_VAUL <- AMC %>% filter(response_var == "fDOM") %>% filter(site.ID == "VAUL")

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena_z + ln_HI, data = fdom_VAUL, col = as.factor(fdom_VAUL$year))

hi.fdom.vaul.lmer <- AMC %>% filter(site.ID == "VAUL" & response_var == "fDOM") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.fdom.vaul.lmer)
qqnorm(resid(hi.fdom.vaul.lmer,  type = "pearson"))
qqline(resid(hi.fdom.vaul.lmer,  type = "pearson"))
plot(hi.fdom.vaul.lmer)
summary(hi.fdom.vaul.lmer)
confint(hi.fdom.vaul.lmer)
r.squaredGLMM(hi.fdom.vaul.lmer)

# random var = 0. Check lm
hi.fdom.vaul.lm <- AMC %>% filter(site.ID == "VAUL" & response_var == "fDOM") %>%
                lm(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z, data = .)
summary(hi.fdom.vaul.lm)
# same qualitative result
```

```{r}
## SpCond ##

# MOOS #
pairs <- AMC %>% filter(site.ID == "MOOS" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_SPC_MOOS_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.spc.moos.lmer <- AMC %>% filter(site.ID == "MOOS" & response_var == "SPC") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.spc.moos.lmer)
qqnorm(resid(hi.spc.moos.lmer,  type = "pearson"))
qqline(resid(hi.spc.moos.lmer,  type = "pearson"))
plot(hi.spc.moos.lmer)
summary(hi.spc.moos.lmer)
confint(hi.spc.moos.lmer)
r.squaredGLMM(hi.spc.moos.lmer)

# random var = 0. Compare w/ lm
hi.spc.moos.lm <- AMC %>% filter(site.ID == "MOOS" & response_var == "SPC") %>%
                lm(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z, data = .)
summary(hi.spc.moos.lm)
# qualitatively same as lmer

# FRCH #
pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_SPC_FRCH_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.spc.frch.lmer <- AMC %>% filter(site.ID == "FRCH" & response_var == "SPC") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.spc.frch.lmer)
qqnorm(resid(hi.spc.frch.lmer,  type = "pearson"))
qqline(resid(hi.spc.frch.lmer,  type = "pearson"))
plot(hi.spc.frch.lmer)
summary(hi.spc.frch.lmer)
confint(hi.spc.frch.lmer)
r.squaredGLMM(hi.spc.frch.lmer)

# Random var low relative to resid. Check lm.
hi.spc.frch.lm <- AMC %>% filter(site.ID == "FRCH" & response_var == "SPC") %>%
                lm(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z, data = .)
summary(hi.spc.frch.lm)
# qualitatively similar to lmer

# POKE #
pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_SPC_POKE_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

# filter 2 outliers
pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "SPC" & ln_HI > 0) %>% 
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_SPC_POKE_pairs_2out.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.spc.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "SPC" & ln_HI > 0) %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.spc.poke.lmer)
# ppt_week & ppt_month too correlated

hi.spc.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "SPC" & ln_HI > 0) %>%
                lmer(ln_HI ~ precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.spc.poke.lmer)
qqnorm(resid(hi.spc.poke.lmer,  type = "pearson"))
qqline(resid(hi.spc.poke.lmer,  type = "pearson"))
plot(hi.spc.poke.lmer)
summary(hi.spc.poke.lmer)
confint(hi.spc.poke.lmer)
r.squaredGLMM(hi.spc.poke.lmer)

# CARI #
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_SPC_CARI_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.spc.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "SPC") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.spc.cari.lmer)
# ppt_week & ppt_month too correlated

hi.spc.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "SPC") %>%
                lmer(ln_HI ~ precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.spc.cari.lmer)
qqnorm(resid(hi.spc.cari.lmer,  type = "pearson"))
qqline(resid(hi.spc.cari.lmer,  type = "pearson"))
plot(hi.spc.cari.lmer)
summary(hi.spc.cari.lmer)
confint(hi.spc.cari.lmer)
r.squaredGLMM(hi.spc.cari.lmer)

# STRT #
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_SPC_STRT_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.spc.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "SPC") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.fdom.strt.lmer)
qqnorm(resid(hi.fdom.strt.lmer,  type = "pearson"))
qqline(resid(hi.fdom.strt.lmer,  type = "pearson"))
plot(hi.fdom.strt.lmer)
summary(hi.fdom.strt.lmer)
confint(hi.fdom.strt.lmer)
r.squaredGLMM(hi.fdom.strt.lmer)

# VAUL #
pairs <- AMC %>% filter(site.ID == "VAUL" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))

spc_VAUL <- AMC %>% filter(response_var == "SPC") %>% filter(site.ID == "VAUL")

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena_z + ln_HI, data = spc_VAUL, col = as.factor(spc_VAUL$year))
# 1 large negative outlier- remove

spc_VAUL <- AMC %>% filter(response_var == "SPC") %>% filter(site.ID == "VAUL") %>% filter(ln_HI >= -0.5)

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena_z + ln_HI, data = spc_VAUL, col = as.factor(spc_VAUL$year))

hi.spc.vaul.lmer <- AMC %>% filter(site.ID == "VAUL" & response_var == "SPC" & ln_HI >= -0.5) %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.spc.vaul.lmer)
qqnorm(resid(hi.spc.vaul.lmer,  type = "pearson"))
qqline(resid(hi.spc.vaul.lmer,  type = "pearson"))
plot(hi.spc.vaul.lmer)
# not great
summary(hi.spc.vaul.lmer)
confint(hi.spc.vaul.lmer)
r.squaredGLMM(hi.spc.vaul.lmer)

# random var = 0. Check lm
hi.fdom.vaul.lm <- AMC %>% filter(site.ID == "VAUL" & response_var == "fDOM") %>%
                lm(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z, data = .)
summary(hi.fdom.vaul.lm)
# same qualitative result
```

```{r}
## Turb ##

# MOOS #
pairs <- AMC %>% filter(site.ID == "MOOS" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_turb_MOOS_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.turb.moos.lmer <- AMC %>% filter(site.ID == "MOOS" & response_var == "turb") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.turb.moos.lmer)
qqnorm(resid(hi.turb.moos.lmer,  type = "pearson"))
qqline(resid(hi.turb.moos.lmer,  type = "pearson"))
plot(hi.turb.moos.lmer)
summary(hi.turb.moos.lmer)
confint(hi.turb.moos.lmer)
r.squaredGLMM(hi.turb.moos.lmer)

# FRCH #
pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_turb_FRCH_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.turb.frch.lmer <- AMC %>% filter(site.ID == "FRCH" & response_var == "turb") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.turb.frch.lmer)
qqnorm(resid(hi.turb.frch.lmer,  type = "pearson"))
qqline(resid(hi.turb.frch.lmer,  type = "pearson"))
plot(hi.turb.frch.lmer)
summary(hi.turb.frch.lmer)
confint(hi.turb.frch.lmer)
r.squaredGLMM(hi.turb.frch.lmer)

# POKE #
pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_turb_POKE_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.turb.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "turb") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.turb.poke.lmer)
qqnorm(resid(hi.turb.poke.lmer,  type = "pearson"))
qqline(resid(hi.turb.poke.lmer,  type = "pearson"))
plot(hi.turb.poke.lmer)
summary(hi.turb.poke.lmer)
confint(hi.turb.poke.lmer)
r.squaredGLMM(hi.turb.poke.lmer)

# CARI #
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_turb_CARI_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.turb.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "turb") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.turb.cari.lmer)
# ppt_week & ppt_month too correlated

hi.turb.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "turb") %>%
                lmer(ln_HI ~ precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.turb.cari.lmer)
qqnorm(resid(hi.turb.cari.lmer,  type = "pearson"))
qqline(resid(hi.turb.cari.lmer,  type = "pearson"))
plot(hi.turb.cari.lmer)
summary(hi.turb.cari.lmer)
confint(hi.turb.cari.lmer)
r.squaredGLMM(hi.turb.cari.lmer)

# No variance associated with year. Check lm
hi.turb.cari.lm <- AMC %>% filter(site.ID == "CARI" & response_var == "turb") %>%
                           lm(ln_HI ~ precip.month_z + TimeSinceChena_z + Intensity_z , data = .)
summary(hi.turb.cari.lm)

# STRT #
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_turb_STRT_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.turb.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "turb") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.turb.strt.lmer)
qqnorm(resid(hi.turb.strt.lmer,  type = "pearson"))
qqline(resid(hi.turb.strt.lmer,  type = "pearson"))
plot(hi.turb.strt.lmer)
summary(hi.turb.strt.lmer)
confint(hi.turb.strt.lmer)
r.squaredGLMM(hi.turb.strt.lmer)

# VAUL #
pairs <- AMC %>% filter(site.ID == "VAUL" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_fDOM_VAUL_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

turb_VAUL <- AMC %>% filter(response_var == "turb") %>% filter(site.ID == "VAUL")

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena_z + ln_HI, data = turb_VAUL, col = as.factor(turb_VAUL$year))

hi.turb.vaul.lmer <- AMC %>% filter(site.ID == "VAUL" & response_var == "turb") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(hi.turb.vaul.lmer)
qqnorm(resid(hi.turb.vaul.lmer,  type = "pearson"))
qqline(resid(hi.turb.vaul.lmer,  type = "pearson"))
plot(hi.turb.vaul.lmer)
summary(hi.turb.vaul.lmer)
confint(hi.turb.vaul.lmer)
r.squaredGLMM(hi.turb.vaul.lmer)

```

```{r}
### BETA ###
## NO3 ##

# MOOS #
pairs <- AMC %>% filter(site.ID == "MOOS" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_lnbeta_NO3_MOOS_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.no3.moos.lmer <- AMC %>% filter(site.ID == "MOOS" & response_var == "NO3") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.no3.moos.lmer)
qqnorm(resid(beta.no3.moos.lmer,  type = "pearson"))
qqline(resid(beta.no3.moos.lmer,  type = "pearson"))
plot(beta.no3.moos.lmer)
summary(beta.no3.moos.lmer)
confint(beta.no3.moos.lmer)
r.squaredGLMM(beta.no3.moos.lmer)

# FRCH #
pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_lnbeta_NO3_FRCH_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.no3.frch.lmer <- AMC %>% filter(site.ID == "FRCH" & response_var == "NO3") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.no3.frch.lmer)
qqnorm(resid(beta.no3.frch.lmer,  type = "pearson"))
qqline(resid(beta.no3.frch.lmer,  type = "pearson"))
plot(beta.no3.frch.lmer)
summary(beta.no3.frch.lmer)
confint(beta.no3.frch.lmer)
r.squaredGLMM(beta.no3.frch.lmer)

# POKE #
pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
# remove 1 outlier
pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "NO3" & ln_beta <= 2.4) %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_lnbeta_NO3_POKE_pairs_1out.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.no3.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "NO3" & ln_beta <= 2.4) %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.no3.poke.lmer)
# ppt month & week too strongly correlated

# Remove precip.week from model
beta.no3.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "NO3" & ln_beta <= 2.4) %>%
                lmer(ln_beta ~ precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.no3.poke.lmer)
qqnorm(resid(beta.no3.poke.lmer,  type = "pearson"))
qqline(resid(beta.no3.poke.lmer,  type = "pearson"))
plot(beta.no3.poke.lmer)
summary(beta.no3.poke.lmer)
confint(beta.no3.poke.lmer)
r.squaredGLMM(hi.no3.poke.lmer)

# CARI #
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_lnbeta_NO3_CARI_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

# remove 3 outliers
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "NO3" & ln_beta >= 1.5) %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_lnbeta_NO3_CARI_pairs_3out.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.no3.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "NO3" & ln_beta >= 1.5) %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.no3.cari.lmer)
# ppt month & week too strongly correlated

# Remove precip.week from model
beta.no3.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "NO3" & ln_beta >= 1.5) %>%
                lmer(ln_HI ~ precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.no3.cari.lmer)
qqnorm(resid(beta.no3.cari.lmer,  type = "pearson"))
qqline(resid(beta.no3.cari.lmer,  type = "pearson"))
plot(beta.no3.cari.lmer)
summary(beta.no3.cari.lmer)
confint(beta.no3.cari.lmer)
r.squaredGLMM(beta.no3.cari.lmer)

# STRT #
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_NO3_STRT_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.no3.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "NO3") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.no3.strt.lmer)
#ppt_week & ppt_month too strongly correlated

beta.no3.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "NO3") %>%
                lmer(ln_beta ~ precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.no3.strt.lmer)
qqnorm(resid(beta.no3.strt.lmer,  type = "pearson"))
qqline(resid(beta.no3.strt.lmer,  type = "pearson"))
plot(beta.no3.strt.lmer)
summary(beta.no3.strt.lmer)
confint(beta.no3.strt.lmer)
r.squaredGLMM(beta.no3.strt.lmer)

# VAUL #
pairs <- AMC %>% filter(site.ID == "VAUL" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_NO3_VAUL_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

NO3_VAUL <- AMC %>% filter(response_var == "NO3") %>% filter(site.ID == "VAUL")

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena_z + ln_beta, data = NO3_VAUL, col = as.factor(NO3_VAUL$year))
# low outlier - remove

NO3_VAUL <- AMC %>% filter(response_var == "NO3") %>% filter(site.ID == "VAUL") %>% filter(ln_beta > 1.6)

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena_z + ln_beta, data = NO3_VAUL, col = as.factor(NO3_VAUL$year))

beta.no3.vaul.lmer <- AMC %>% filter(site.ID == "VAUL" & response_var == "NO3" & ln_beta >= 1.6) %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.no3.vaul.lmer)
qqnorm(resid(beta.no3.vaul.lmer,  type = "pearson"))
qqline(resid(beta.no3.vaul.lmer,  type = "pearson"))
plot(beta.no3.vaul.lmer)
summary(beta.no3.vaul.lmer)
confint(beta.no3.vaul.lmer)
r.squaredGLMM(beta.no3.vaul.lmer)
```

```{r}
## fDOM ##

# MOOS #
pairs <- AMC %>% filter(site.ID == "MOOS" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_fDOM_MOOS_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.fdom.moos.lmer <- AMC %>% filter(site.ID == "MOOS" & response_var == "fDOM") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.fdom.moos.lmer)
qqnorm(resid(beta.fdom.moos.lmer,  type = "pearson"))
qqline(resid(beta.fdom.moos.lmer,  type = "pearson"))
plot(beta.fdom.moos.lmer)
summary(beta.fdom.moos.lmer)
confint(beta.fdom.moos.lmer)
r.squaredGLMM(beta.fdom.moos.lmer)

# FRCH #
pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
#low loutlier- remove

pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "fDOM" & ln_beta > 1.6) %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))

ggsave(pairs, file = "beta_fDOM_FRCH_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.fdom.frch.lmer <- AMC %>% filter(site.ID == "FRCH" & response_var == "fDOM" & ln_beta >= 1.6) %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.fdom.frch.lmer)
qqnorm(resid(beta.fdom.frch.lmer,  type = "pearson"))
qqline(resid(beta.fdom.frch.lmer,  type = "pearson"))
plot(beta.fdom.frch.lmer)
summary(beta.fdom.frch.lmer)
confint(beta.fdom.frch.lmer)
r.squaredGLMM(beta.fdom.frch.lmer)

# CARI #
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_fDOM_CARI_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.fdom.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "fDOM") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.fdom.cari.lmer)
# ppt week & ppt month too strongly correlated

beta.fdom.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "fDOM") %>%
                lmer(ln_beta ~ precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.fdom.cari.lmer)
qqnorm(resid(beta.fdom.cari.lmer,  type = "pearson"))
qqline(resid(beta.fdom.cari.lmer,  type = "pearson"))
plot(beta.fdom.cari.lmer)
summary(beta.fdom.cari.lmer)
confint(beta.fdom.cari.lmer)
r.squaredGLMM(beta.fdom.cari.lmer)

# POKE #
pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_fDOM_POKE_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.fdom.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "fDOM") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.fdom.poke.lmer)
qqnorm(resid(beta.fdom.poke.lmer,  type = "pearson"))
qqline(resid(beta.fdom.poke.lmer,  type = "pearson"))
plot(beta.fdom.poke.lmer)
summary(beta.fdom.poke.lmer)
confint(beta.fdom.poke.lmer)
r.squaredGLMM(beta.fdom.poke.lmer)

# STRT #
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_fDOM_STRT_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.fdom.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "fDOM") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.fdom.strt.lmer)
qqnorm(resid(beta.fdom.strt.lmer,  type = "pearson"))
qqline(resid(beta.fdom.strt.lmer,  type = "pearson"))
plot(beta.fdom.strt.lmer)
summary(beta.fdom.strt.lmer)
confint(beta.fdom.strt.lmer)
r.squaredGLMM(beta.fdom.strt.lmer)

# VAUL #
pairs <- AMC %>% filter(site.ID == "VAUL" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_fDOM_VAUL_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

fdom_VAUL <- AMC %>% filter(response_var == "fDOM") %>% filter(site.ID == "VAUL")

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena_z + ln_beta, data = fdom_VAUL, col = as.factor(fdom_VAUL$year))

beta.fdom.vaul.lmer <- AMC %>% filter(site.ID == "VAUL" & response_var == "fDOM") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.fdom.vaul.lmer)
qqnorm(resid(beta.fdom.vaul.lmer,  type = "pearson"))
qqline(resid(beta.fdom.vaul.lmer,  type = "pearson"))
plot(beta.fdom.vaul.lmer)
summary(beta.fdom.vaul.lmer)
confint(beta.fdom.vaul.lmer)
r.squaredGLMM(beta.fdom.vaul.lmer)


```

```{r}
## SpCond ##

# MOOS #
pairs <- AMC %>% filter(site.ID == "MOOS" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_SPC_MOOS_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.spc.moos.lmer <- AMC %>% filter(site.ID == "MOOS" & response_var == "SPC") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.spc.moos.lmer)
qqnorm(resid(beta.spc.moos.lmer,  type = "pearson"))
qqline(resid(beta.spc.moos.lmer,  type = "pearson"))
plot(beta.spc.moos.lmer)
# not great
summary(beta.spc.moos.lmer)
confint(beta.spc.moos.lmer)
r.squaredGLMM(beta.spc.moos.lmer)

# FRCH #
pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
# two large positive ouliers, both from 2020- removing
pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "SPC" & ln_beta < 2) %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))

ggsave(pairs, file = "beta_SPC_FRCH_pairs_rem2out.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.spc.frch.lmer <- AMC %>% filter(site.ID == "FRCH" & response_var == "SPC" & ln_beta < 2) %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.spc.frch.lmer)
qqnorm(resid(beta.spc.frch.lmer,  type = "pearson"))
qqline(resid(beta.spc.frch.lmer,  type = "pearson"))
plot(beta.spc.frch.lmer)
summary(beta.spc.frch.lmer)
confint(beta.spc.frch.lmer)
r.squaredGLMM(beta.spc.frch.lmer)

# POKE #
pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_SPC_POKE_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.spc.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "SPC") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.spc.poke.lmer)
qqnorm(resid(beta.spc.poke.lmer,  type = "pearson"))
qqline(resid(beta.spc.poke.lmer,  type = "pearson"))
plot(beta.spc.poke.lmer)
summary(beta.spc.poke.lmer)
confint(beta.spc.poke.lmer)
r.squaredGLMM(beta.spc.poke.lmer)

# CARI #
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
      
ggsave(pairs, file = "beta_SPC_CARI_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

# negative outlier- remove
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "SPC" & ln_beta > 0) %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))

ggsave(pairs, file = "HI_SPC_CARI_pairs_out.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.spc.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "SPC" & ln_beta > 0) %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.spc.cari.lmer)
# ppt_week & ppt_month too correlated

beta.spc.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "SPC" & ln_beta > 0) %>%
                lmer(ln_beta ~ precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.spc.cari.lmer)
qqnorm(resid(beta.spc.cari.lmer,  type = "pearson"))
qqline(resid(beta.spc.cari.lmer,  type = "pearson"))
plot(beta.spc.cari.lmer)
summary(beta.spc.cari.lmer)
confint(beta.spc.cari.lmer)
r.squaredGLMM(beta.spc.cari.lmer)

# STRT #
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_SPC_STRT_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

# positive outlier- remove
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "SPC" & ln_beta < 2) %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_SPC_STRT_pairs_out.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")


beta.spc.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "SPC" & ln_beta < 2) %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.fdom.strt.lmer)
qqnorm(resid(beta.fdom.strt.lmer,  type = "pearson"))
qqline(resid(beta.fdom.strt.lmer,  type = "pearson"))
plot(beta.fdom.strt.lmer)
summary(beta.fdom.strt.lmer)
confint(beta.fdom.strt.lmer)
r.squaredGLMM(beta.fdom.strt.lmer)

# VAUL #
pairs <- AMC %>% filter(site.ID == "VAUL" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
spc_VAUL <- AMC %>% filter(response_var == "SPC") %>% filter(site.ID == "VAUL")

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena_z + ln_beta, data = spc_VAUL, col = as.factor(spc_VAUL$year))
# 1 large negative outlier- remove

spc_VAUL <- AMC %>% filter(response_var == "SPC") %>% filter(site.ID == "VAUL") %>% filter(ln_beta >= 1.6)

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena_z + ln_beta, data = spc_VAUL, col = as.factor(spc_VAUL$year))

beta.spc.vaul.lmer <- AMC %>% filter(site.ID == "VAUL" & response_var == "SPC" & ln_beta >= 1.6) %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.spc.vaul.lmer)
qqnorm(resid(beta.spc.vaul.lmer,  type = "pearson"))
qqline(resid(beta.spc.vaul.lmer,  type = "pearson"))
plot(beta.spc.vaul.lmer)
summary(beta.spc.vaul.lmer)
confint(beta.spc.vaul.lmer)
r.squaredGLMM(beta.spc.vaul.lmer)

```

```{r}
## Turb ##

# MOOS #
pairs <- AMC %>% filter(site.ID == "MOOS" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_turb_MOOS_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.turb.moos.lmer <- AMC %>% filter(site.ID == "MOOS" & response_var == "turb") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.turb.moos.lmer)
qqnorm(resid(beta.turb.moos.lmer,  type = "pearson"))
qqline(resid(beta.turb.moos.lmer,  type = "pearson"))
plot(beta.turb.moos.lmer)
summary(beta.turb.moos.lmer)
confint(beta.turb.moos.lmer)
r.squaredGLMM(beta.turb.moos.lmer)

# FRCH #
pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_turb_FRCH_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.turb.frch.lmer <- AMC %>% filter(site.ID == "FRCH" & response_var == "turb") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.turb.frch.lmer)
qqnorm(resid(beta.turb.frch.lmer,  type = "pearson"))
qqline(resid(beta.turb.frch.lmer,  type = "pearson"))
plot(beta.turb.frch.lmer)
summary(beta.turb.frch.lmer)
confint(beta.turb.frch.lmer)
r.squaredGLMM(beta.turb.frch.lmer)

# POKE #
pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_turb_POKE_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.turb.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "turb") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.turb.poke.lmer)
qqnorm(resid(beta.turb.poke.lmer,  type = "pearson"))
qqline(resid(beta.turb.poke.lmer,  type = "pearson"))
plot(beta.turb.poke.lmer)
summary(beta.turb.poke.lmer)
confint(beta.turb.poke.lmer)
r.squaredGLMM(beta.turb.poke.lmer)

# CARI #
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_turb_CARI_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.turb.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "turb") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.turb.cari.lmer)
# ppt_week & ppt_month too correlated

beta.turb.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "turb") %>%
                lmer(ln_beta ~ precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.turb.cari.lmer)
qqnorm(resid(beta.turb.cari.lmer,  type = "pearson"))
qqline(resid(beta.turb.cari.lmer,  type = "pearson"))
plot(beta.turb.cari.lmer)
summary(beta.turb.cari.lmer)
confint(beta.turb.cari.lmer)
r.squaredGLMM(beta.turb.cari.lmer)

# STRT #
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_turb_STRT_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

# remove low outlier
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "turb" & ln_beta > 1.9) %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))
   
ggsave(pairs, file = "beta_turb_STRT_pairs_out.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.turb.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "turb") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.turb.strt.lmer)
qqnorm(resid(beta.turb.strt.lmer,  type = "pearson"))
qqline(resid(beta.turb.strt.lmer,  type = "pearson"))
# not great- lower tail
plot(beta.turb.strt.lmer)
summary(beta.turb.strt.lmer)
confint(beta.turb.strt.lmer)
r.squaredGLMM(beta.turb.strt.lmer)

# VAUL #
pairs <- AMC %>% filter(site.ID == "VAUL" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena_z", "ln_beta"), mapping = aes(color = as.factor(year)))

turb_VAUL <- AMC %>% filter(response_var == "turb") %>% filter(site.ID == "VAUL")

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena_z + ln_beta, data = turb_VAUL, col = as.factor(turb_VAUL$year))

beta.turb.vaul.lmer <- AMC %>% filter(site.ID == "VAUL" & response_var == "turb") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena_z + Intensity_z + (1|year), data = .)

vif(beta.turb.vaul.lmer)
qqnorm(resid(beta.turb.vaul.lmer,  type = "pearson"))
qqline(resid(beta.turb.vaul.lmer,  type = "pearson"))
plot(beta.turb.vaul.lmer)
summary(beta.turb.vaul.lmer)
confint(beta.turb.vaul.lmer)
r.squaredGLMM(beta.turb.vaul.lmer)

```

```{r Coefficient plots 12/23/2025}
### PLOTS ###
# Data frames: 
# hi.no3.moos.lmer, hi.no3.frch.lmer, hi.no3.cari.lmer, hi.no3.poke.lmer, hi.no3.strt.lmer, hi.no3.vaul.lmer

## Effect sizes: Multiple models on one figure ##
## HI ##
# HI NO3 ####
HI_no3 <- dwplot(list(hi.no3.moos.lmer, hi.no3.frch.lmer, hi.no3.cari.lmer, hi.no3.poke.lmer, hi.no3.strt.lmer, hi.no3.vaul.lmer), 
                  effects="fixed",
                  dot_args = list(size = 6),
                  whisker_args = list(size = 2)) +
  scale_color_manual(labels = rev(c(bquote(paste("MOOS ", R^{2} == .(format(r.squaredGLMM(hi.no3.moos.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.no3.moos.lmer)))), 
                                bquote(paste("FRCH ", R^{2} == .(format(r.squaredGLMM(hi.no3.frch.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.no3.frch.lmer)))),
                                bquote(paste("CARI ", R^{2} == .(format(r.squaredGLMM(hi.no3.cari.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.no3.cari.lmer)))),
                                bquote(paste("POKE ", R^{2} == .(format(r.squaredGLMM(hi.no3.poke.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.no3.poke.lmer)))),
                                bquote(paste("STRT ", R^{2} == .(format(r.squaredGLMM(hi.no3.strt.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.no3.strt.lmer)))),
                     bquote(paste("VAUL ", R^{2} == .(format(r.squaredGLMM(hi.no3.vaul.lmer)[[1]][1], digits = 2)),  " n" == .(nobs(hi.no3.vaul.lmer)))))),
                     values = c("#E7298A", "#66C2A5", "#6A3D9A", "#3288BD", "#FF7F00", "#A6761D"), drop = FALSE) +
  geom_vline(xintercept=0, lty=2) + 
  xlab("effect size") +
  xlim(-0.4, 0.5) +
  scale_y_discrete(labels=c(precip.week_z = "ppt 1 week", precip.month_z = "ppt 1 month", Intensity_z = "ppt event intensity", TimeSinceChena_z = "days since snowmelt")) +
  theme_bw() +
  theme(legend.position = c(0.78, 0.38),
        legend.title = element_blank(),
        legend.text = element_text(size = 18),
        legend.background = element_blank(),
        legend.box.background = element_rect(color = "black", size = 1),
        plot.title = element_text(face = "bold", hjust = 0.5, size =22),
        panel.grid = element_blank(),
        panel.border = element_rect(color = "black", size = 2),
        axis.text = element_text(size = 22),
        axis.title.x = element_text(size = 22),
        plot.margin = margin(0.5,1.5,0.5,0.5, "cm"))

ggsave(HI_no3, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_HI_NO3_coef_", Sys.Date(), ".pdf"),
       width = 10, height = 8, units = "in")

ggsave(HI_no3, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_HI_NO3_coef_", Sys.Date(), ".jpg"),
       width = 10, height = 8, units = "in")

# BETA NO3 ####
beta_no3 <- dwplot(list(beta.no3.moos.lmer, beta.no3.frch.lmer, beta.no3.cari.lmer, beta.no3.poke.lmer, beta.no3.strt.lmer, beta.no3.vaul.lmer), 
                  effects="fixed",
                  dot_args = list(size = 6),
                  whisker_args = list(size = 2)) +
  scale_color_manual(labels = rev(c(bquote(paste("MOOS ", R^{2} == .(format(r.squaredGLMM(beta.no3.moos.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.no3.moos.lmer)))), 
                                bquote(paste("FRCH ", R^{2} == .(format(r.squaredGLMM(beta.no3.frch.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.no3.frch.lmer)))),
                                bquote(paste("CARI ", R^{2} == .(format(r.squaredGLMM(beta.no3.cari.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.no3.cari.lmer)))),
                                bquote(paste("POKE ", R^{2} == .(format(r.squaredGLMM(beta.no3.poke.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.no3.poke.lmer)))),
                                bquote(paste("STRT ", R^{2} == .(format(r.squaredGLMM(beta.no3.strt.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.no3.strt.lmer)))),
                     bquote(paste("VAUL ", R^{2} == .(format(r.squaredGLMM(beta.no3.vaul.lmer)[[1]][1], digits = 2)),  " n" == .(nobs(beta.no3.vaul.lmer)))))),
                     values = c("#E7298A", "#66C2A5", "#6A3D9A", "#3288BD", "#FF7F00", "#A6761D"), drop = FALSE) +
  geom_vline(xintercept=0, lty=2) + 
  xlab("effect size") +
  xlim(-0.2, 0.4) +
  scale_y_discrete(labels=c(precip.week_z = "ppt 1 week", precip.month_z = "ppt 1 month", Intensity_z = "ppt event intensity", TimeSinceChena_z = "days since snowmelt")) +
  theme_bw() +
  theme(legend.position = c(0.78, 0.38),
        legend.title = element_blank(),
        legend.text = element_text(size = 18),
        legend.background = element_blank(),
        legend.box.background = element_rect(color = "black", size = 1),
        plot.title = element_text(face = "bold", hjust = 0.5, size =22),
        panel.grid = element_blank(),
        panel.border = element_rect(color = "black", size = 2),
        axis.text = element_text(size = 22),
        axis.title.x = element_text(size = 22),
        plot.margin = margin(0.5,1.5,0.5,0.5, "cm"))

ggsave(beta_no3, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_beta_NO3_coef_", Sys.Date(), ".pdf"),
       width = 10, height = 8, units = "in")

ggsave(beta_no3, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_beta_NO3_coef_", Sys.Date(), ".jpg"),
       width = 10, height = 8, units = "in")

#### 2 panel NO3 FIGURE 2/8/2026 ####
# Packages
library(ggplot2)
library(cowplot)
library(here)
# 1) Prepare the base panels (your plots: HI_NO3 & beta_no3)
# LEFT panel (A): keep y tick labels; bottom legend; title
p1 <- HI_no3 +
  labs(title = "HI - Nitrate") +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold", hjust = 0.5, size = 22),
    # seam: keep a very small right margin
    plot.margin = margin(t = 18, r = 0, b = 30, l = 12),
    axis.text.y = element_text(size = 22),
    axis.title.x = element_text(size = 22),
    axis.text.x = element_text(size = 22),
    legend.text = element_text(size = 16),
    # ensure no opaque background that would show during overlap
    plot.background = element_rect(fill = NA, color = NA)
  )

# RIGHT panel (B): remove y tick labels; bottom legend; title
p2 <- beta_no3 +
  labs(title = "β - Nitrate") +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold", hjust = 0.5, size = 22),
    # seam: zero left margin to hug panel A
    plot.margin = margin(t = 18, r = 12, b = 30, l = 0),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.x = element_text(size = 22),
    axis.text.x = element_text(size = 22),
    legend.text = element_text(size = 16),
    plot.background = element_rect(fill = NA, color = NA)
  )


# 2) Compose with ggdraw + draw_plot (explicit positioning)
#    - Equal widths for both panels (0.50 each)
#    - Shift panel B slightly left to minimize seam
# Tweak this small offset if needed; typical range 0.004 to 0.02
seam_offset <- 0.0001

combined <- ggdraw() +
  # Panel A: exact left half
  draw_plot(p1, x = 0.00, y = 0.00, width = 0.50, height = 1.00) +
  # Panel B: same width but nudged left by seam_offset
  draw_plot(p2, x = 0.50 - seam_offset, y = 0.00, width = 0.375, height = 1.00) +
  # A/B labels (top-left of each panel area)
  draw_plot_label(
    label = c("A", "B"),
    x = c(0.11, 0.51 - seam_offset),  # keep tag near left of each panel
    y = c(0.98, 0.98),
    size = 22,
    fontface = "bold"
  )
# 3) Save (keep your large width to protect bottom legends)

ggsave(combined, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_2_panel_NO3_coef_", Sys.Date(), ".jpg"),
       width = 23, height = 10, units = "in")

# HI fDOM ####
HI_fDOM <- dwplot(list(hi.fdom.moos.lmer, hi.fdom.frch.lmer, hi.fdom.cari.lmer, hi.fdom.poke.lmer, hi.fdom.strt.lmer, hi.fdom.vaul.lmer), 
                  effects="fixed",
                  dot_args = list(size = 6),
                  whisker_args = list(size = 2)) +
  scale_color_manual(labels = rev(c(bquote(paste("MOOS ", R^{2} == .(format(r.squaredGLMM(hi.fdom.moos.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.fdom.moos.lmer)))), 
                                bquote(paste("FRCH ", R^{2} == .(format(r.squaredGLMM(hi.fdom.frch.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.fdom.frch.lmer)))),
                                bquote(paste("CARI ", R^{2} == .(format(r.squaredGLMM(hi.fdom.cari.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.fdom.cari.lmer)))),
                                bquote(paste("POKE ", R^{2} == .(format(r.squaredGLMM(hi.fdom.poke.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.fdom.poke.lmer)))),
                                bquote(paste("STRT ", R^{2} == .(format(r.squaredGLMM(hi.fdom.strt.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.fdom.strt.lmer)))),
                     bquote(paste("VAUL ", R^{2} == .(format(r.squaredGLMM(hi.fdom.vaul.lmer)[[1]][1], digits = 2)),  " n" == .(nobs(hi.fdom.vaul.lmer)))))),
                     values = c("#E7298A", "#66C2A5", "#6A3D9A", "#3288BD", "#FF7F00", "#A6761D"), drop = FALSE) +
  geom_vline(xintercept=0, lty=2) + 
  xlab("effect size") +
  xlim(-0.4, 0.5) +
  scale_y_discrete(labels=c(precip.week_z = "ppt 1 week", precip.month_z = "ppt 1 month", Intensity_z = "ppt event intensity", TimeSinceChena_z = "days since snowmelt")) +
  theme_bw() +
  theme(legend.position = c(0.78, 0.38),
        legend.title = element_blank(),
        legend.text = element_text(size = 18),
        legend.background = element_blank(),
        legend.box.background = element_rect(color = "black", size = 1),
        plot.title = element_text(face = "bold", hjust = 0.5, size =22),
        panel.grid = element_blank(),
        panel.border = element_rect(color = "black", size = 2),
        axis.text = element_text(size = 22),
        axis.title.x = element_text(size = 22),
        plot.margin = margin(0.5,1.5,0.5,0.5, "cm"))

ggsave(HI_fDOM, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_HI_fdom_coef_", Sys.Date(), ".pdf"),
       width = 10, height = 8, units = "in")

ggsave(HI_fDOM, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_HI_fdom_coef_", Sys.Date(), ".jpg"),
       width = 10, height = 8, units = "in")

# beta fDOM ####
beta.fDOM <- dwplot(list(beta.fdom.moos.lmer, beta.fdom.frch.lmer, beta.fdom.cari.lmer, beta.fdom.poke.lmer, beta.fdom.strt.lmer, beta.fdom.vaul.lmer), 
                  effects="fixed",
                  dot_args = list(size = 6),
                  whisker_args = list(size = 2)) +
  scale_color_manual(labels = rev(c(bquote(paste("MOOS ", R^{2} == .(format(r.squaredGLMM(beta.fdom.moos.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.fdom.moos.lmer)))), 
                                bquote(paste("FRCH ", R^{2} == .(format(r.squaredGLMM(beta.fdom.frch.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.fdom.frch.lmer)))),
                                bquote(paste("CARI ", R^{2} == .(format(r.squaredGLMM(beta.fdom.cari.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.fdom.cari.lmer)))),
                                bquote(paste("POKE ", R^{2} == .(format(r.squaredGLMM(beta.fdom.poke.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.fdom.poke.lmer)))),
                                bquote(paste("STRT ", R^{2} == .(format(r.squaredGLMM(beta.fdom.strt.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.fdom.strt.lmer)))),
                     bquote(paste("VAUL ", R^{2} == .(format(r.squaredGLMM(beta.fdom.vaul.lmer)[[1]][1], digits = 2)),  " n" == .(nobs(beta.fdom.vaul.lmer)))))),
                     values = c("#E7298A", "#66C2A5", "#6A3D9A", "#3288BD", "#FF7F00", "#A6761D"), drop = FALSE) +
  geom_vline(xintercept=0, lty=2) + 
  xlab("effect size") +
  xlim(-0.15, 0.15) +
  scale_y_discrete(labels=c(precip.week_z = "ppt 1 week", precip.month_z = "ppt 1 month", Intensity_z = "ppt event intensity", TimeSinceChena_z = "days since snowmelt")) +
  theme_bw() +
  theme(legend.position = c(0.78, 0.38),
        legend.title = element_blank(),
        legend.text = element_text(size = 18),
        legend.background = element_blank(),
        legend.box.background = element_rect(color = "black", size = 1),
        plot.title = element_text(face = "bold", hjust = 0.5, size =22),
        panel.grid = element_blank(),
        panel.border = element_rect(color = "black", size = 2),
        axis.text = element_text(size = 22),
        axis.title.x = element_text(size = 22),
        plot.margin = margin(0.5,1.5,0.5,0.5, "cm"))

ggsave(beta.fDOM, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_beta_fdom_coef_", Sys.Date(), ".pdf"),
       width = 10, height = 8, units = "in")

ggsave(beta.fDOM, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_beta_fdom_coef_", Sys.Date(), ".jpg"),
       width = 10, height = 8, units = "in")

#### 2 panel fDOM FIGURE 2/14/2026 ####
# 1) Prepare the base panels (your plots: HI_NO3 & beta_no3)
# LEFT panel (A): keep y tick labels; bottom legend; title
p1 <- HI_fDOM +
  labs(title = "HI - fDOM") +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold", hjust = 0.5, size = 22),
    # seam: keep a very small right margin
    plot.margin = margin(t = 18, r = 0, b = 30, l = 12),
    axis.text.y = element_text(size = 22),
    axis.title.x = element_text(size = 22),
    axis.text.x = element_text(size = 22),
    legend.text = element_text(size = 16),
    # ensure no opaque background that would show during overlap
    plot.background = element_rect(fill = NA, color = NA)
  )

# RIGHT panel (B): remove y tick labels; bottom legend; title
p2 <- beta.fDOM +
  labs(title = "β - fDOM") +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold", hjust = 0.5, size = 22),
    # seam: zero left margin to hug panel A
    plot.margin = margin(t = 18, r = 12, b = 30, l = 0),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.x = element_text(size = 22),
    axis.text.x = element_text(size = 22),
    legend.text = element_text(size = 16),
    plot.background = element_rect(fill = NA, color = NA)
  )


# 2) Compose with ggdraw + draw_plot (explicit positioning)
#    - Equal widths for both panels (0.50 each)
#    - Shift panel B slightly left to minimize seam
# Tweak this small offset if needed; typical range 0.004 to 0.02
seam_offset <- 0.0001

combined <- ggdraw() +
  # Panel A: exact left half
  draw_plot(p1, x = 0.00, y = 0.00, width = 0.50, height = 1.00) +
  # Panel B: same width but nudged left by seam_offset
  draw_plot(p2, x = 0.50 - seam_offset, y = 0.00, width = 0.375, height = 1.00) +
  # A/B labels (top-left of each panel area)
  draw_plot_label(
    label = c("A", "B"),
    x = c(0.11, 0.51 - seam_offset),  # keep tag near left of each panel
    y = c(0.98, 0.98),
    size = 22,
    fontface = "bold"
  )
# 3) Save (keep your large width to protect bottom legends)

ggsave(combined, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_2_panel_fDOM_coef_", Sys.Date(), ".jpg"),
       width = 23, height = 10, units = "in")

# HI SPC ####
HI_SPC <- dwplot(list(hi.spc.moos.lmer, hi.spc.frch.lmer, hi.spc.cari.lmer, hi.spc.poke.lmer, hi.spc.strt.lmer, hi.spc.vaul.lmer), 
                  effects="fixed",
                  dot_args = list(size = 6),
                  whisker_args = list(size = 2)) +
  scale_color_manual(labels = rev(c(bquote(paste("MOOS ", R^{2} == .(format(r.squaredGLMM(hi.spc.moos.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.spc.moos.lmer)))), 
                                bquote(paste("FRCH ", R^{2} == .(format(r.squaredGLMM(hi.spc.frch.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.spc.frch.lmer)))),
                                bquote(paste("CARI ", R^{2} == .(format(r.squaredGLMM(hi.spc.cari.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.spc.cari.lmer)))),
                                bquote(paste("POKE ", R^{2} == .(format(r.squaredGLMM(hi.spc.poke.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.spc.poke.lmer)))),
                                bquote(paste("STRT ", R^{2} == .(format(r.squaredGLMM(hi.spc.strt.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.spc.strt.lmer)))),
                     bquote(paste("VAUL ", R^{2} == .(format(r.squaredGLMM(hi.spc.vaul.lmer)[[1]][1], digits = 2)),  " n" == .(nobs(hi.spc.vaul.lmer)))))),
                     values = c("#E7298A", "#66C2A5", "#6A3D9A", "#3288BD", "#FF7F00", "#A6761D"), drop = FALSE) +
  geom_vline(xintercept=0, lty=2) + 
  xlab("effect size") +
  xlim(-0.3, 0.3) +
  scale_y_discrete(labels=c(precip.week_z = "ppt 1 week", precip.month_z = "ppt 1 month", Intensity_z = "ppt event intensity", TimeSinceChena_z = "days since snowmelt")) +
  theme_bw() +
  theme(legend.position = c(0.78, 0.38),
        legend.title = element_blank(),
        legend.text = element_text(size = 18),
        legend.background = element_blank(),
        legend.box.background = element_rect(color = "black", size = 1),
        plot.title = element_text(face = "bold", hjust = 0.5, size =22),
        panel.grid = element_blank(),
        panel.border = element_rect(color = "black", size = 2),
        axis.text = element_text(size = 22),
        axis.title.x = element_text(size = 22),
        plot.margin = margin(0.5,1.5,0.5,0.5, "cm"))

ggsave(HI_SPC, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_HI_spc_coef_", Sys.Date(), ".pdf"),
       width = 10, height = 8, units = "in")

ggsave(HI_SPC, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_HI_spc_coef_", Sys.Date(), ".jpg"),
       width = 10, height = 8, units = "in")

# beta spc ####
beta_SPC <- dwplot(list(beta.spc.moos.lmer, beta.spc.frch.lmer, beta.spc.cari.lmer, beta.spc.poke.lmer, beta.spc.strt.lmer, beta.spc.vaul.lmer), 
                  effects="fixed",
                  dot_args = list(size = 6),
                  whisker_args = list(size = 2)) +
  scale_color_manual(labels = rev(c(bquote(paste("MOOS ", R^{2} == .(format(r.squaredGLMM(beta.spc.moos.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.spc.moos.lmer)))), 
                                bquote(paste("FRCH ", R^{2} == .(format(r.squaredGLMM(beta.spc.frch.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.spc.frch.lmer)))),
                                bquote(paste("CARI ", R^{2} == .(format(r.squaredGLMM(beta.spc.cari.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.spc.cari.lmer)))),
                                bquote(paste("POKE ", R^{2} == .(format(r.squaredGLMM(beta.spc.poke.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.spc.poke.lmer)))),
                                bquote(paste("STRT ", R^{2} == .(format(r.squaredGLMM(beta.spc.strt.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.spc.strt.lmer)))),
                     bquote(paste("VAUL ", R^{2} == .(format(r.squaredGLMM(beta.spc.vaul.lmer)[[1]][1], digits = 2)),  " n" == .(nobs(beta.spc.vaul.lmer)))))),
                     values = c("#E7298A", "#66C2A5", "#6A3D9A", "#3288BD", "#FF7F00", "#A6761D"), drop = FALSE) +
  geom_vline(xintercept=0, lty=2) + 
  xlab("effect size") +
  xlim(-0.1, 0.1) +
  scale_y_discrete(labels=c(precip.week_z = "ppt 1 week", precip.month_z = "ppt 1 month", Intensity_z = "ppt event intensity", TimeSinceChena_z = "days since snowmelt")) +
  theme_bw() +
  theme(legend.position = c(0.78, 0.38),
        legend.title = element_blank(),
        legend.text = element_text(size = 18),
        legend.background = element_blank(),
        legend.box.background = element_rect(color = "black", size = 1),
        plot.title = element_text(face = "bold", hjust = 0.5, size =22),
        panel.grid = element_blank(),
        panel.border = element_rect(color = "black", size = 2),
        axis.text = element_text(size = 22),
        axis.title.x = element_text(size = 22),
        plot.margin = margin(0.5,1.5,0.5,0.5, "cm"))

ggsave(beta_SPC, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_beta_spc_coef_", Sys.Date(), ".pdf"),
       width = 10, height = 8, units = "in")

ggsave(beta_SPC, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_beta_spc_coef_", Sys.Date(), ".jpg"),
       width = 10, height = 8, units = "in")

#### 2 panel SPC FIGURE 2/14/2026 ####
# 1) Prepare the base panels (your plots: HI_NO3 & beta_no3)
# LEFT panel (A): keep y tick labels; bottom legend; title
p1 <- HI_SPC +
  labs(title = "HI - SPC") +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold", hjust = 0.5, size = 22),
    # seam: keep a very small right margin
    plot.margin = margin(t = 18, r = 0, b = 30, l = 12),
    axis.text.y = element_text(size = 22),
    axis.title.x = element_text(size = 22),
    axis.text.x = element_text(size = 22),
    legend.text = element_text(size = 16),
    # ensure no opaque background that would show during overlap
    plot.background = element_rect(fill = NA, color = NA)
  )

# RIGHT panel (B): remove y tick labels; bottom legend; title
p2 <- beta_SPC +
  labs(title = "β - SPC") +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold", hjust = 0.5, size = 22),
    # seam: zero left margin to hug panel A
    plot.margin = margin(t = 18, r = 12, b = 30, l = 0),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.x = element_text(size = 22),
    axis.text.x = element_text(size = 22),
    legend.text = element_text(size = 16),
    plot.background = element_rect(fill = NA, color = NA)
  )


# 2) Compose with ggdraw + draw_plot (explicit positioning)
#    - Equal widths for both panels (0.50 each)
#    - Shift panel B slightly left to minimize seam
# Tweak this small offset if needed; typical range 0.004 to 0.02
seam_offset <- 0.0001

combined <- ggdraw() +
  # Panel A: exact left half
  draw_plot(p1, x = 0.00, y = 0.00, width = 0.50, height = 1.00) +
  # Panel B: same width but nudged left by seam_offset
  draw_plot(p2, x = 0.50 - seam_offset, y = 0.00, width = 0.375, height = 1.00) +
  # A/B labels (top-left of each panel area)
  draw_plot_label(
    label = c("A", "B"),
    x = c(0.11, 0.51 - seam_offset),  # keep tag near left of each panel
    y = c(0.98, 0.98),
    size = 22,
    fontface = "bold"
  )
# 3) Save (keep your large width to protect bottom legends)

ggsave(combined, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_2_panel_SPC_coef_", Sys.Date(), ".jpg"),
       width = 23, height = 10, units = "in")

# HI turb ####
HI_turb <- dwplot(list(hi.turb.moos.lmer, hi.turb.frch.lmer, hi.turb.cari.lmer, hi.turb.poke.lmer, hi.turb.strt.lmer, hi.turb.vaul.lmer), 
                  effects="fixed",
                  dot_args = list(size = 6),
                  whisker_args = list(size = 2)) +
  scale_color_manual(labels = rev(c(bquote(paste("MOOS ", R^{2} == .(format(r.squaredGLMM(hi.turb.moos.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.turb.moos.lmer)))), 
                                bquote(paste("FRCH ", R^{2} == .(format(r.squaredGLMM(hi.turb.frch.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.turb.frch.lmer)))),
                                bquote(paste("CARI ", R^{2} == .(format(r.squaredGLMM(hi.turb.cari.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.turb.cari.lmer)))),
                                bquote(paste("POKE ", R^{2} == .(format(r.squaredGLMM(hi.turb.poke.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.turb.poke.lmer)))),
                                bquote(paste("STRT ", R^{2} == .(format(r.squaredGLMM(hi.turb.strt.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.turb.strt.lmer)))),
                     bquote(paste("VAUL ", R^{2} == .(format(r.squaredGLMM(hi.turb.vaul.lmer)[[1]][1], digits = 2)),  " n" == .(nobs(hi.turb.vaul.lmer)))))),
                     values = c("#E7298A", "#66C2A5", "#6A3D9A", "#3288BD", "#FF7F00", "#A6761D"), drop = FALSE) +
  geom_vline(xintercept=0, lty=2) + 
  xlab("effect size") +
  xlim(-0.25, 0.25) +
  scale_y_discrete(labels=c(precip.week_z = "ppt 1 week", precip.month_z = "ppt 1 month", Intensity_z = "ppt event intensity", TimeSinceChena_z = "days since snowmelt")) +
  theme_bw() +
  theme(legend.position = c(0.78, 0.38),
        legend.title = element_blank(),
        legend.text = element_text(size = 18),
        legend.background = element_blank(),
        legend.box.background = element_rect(color = "black", size = 1),
        plot.title = element_text(face = "bold", hjust = 0.5, size =22),
        panel.grid = element_blank(),
        panel.border = element_rect(color = "black", size = 2),
        axis.text = element_text(size = 22),
        axis.title.x = element_text(size = 22),
        plot.margin = margin(0.5,1.5,0.5,0.5, "cm"))

ggsave(HI_turb, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_HI_turb_coef_", Sys.Date(), ".pdf"),
       width = 10, height = 8, units = "in")

ggsave(HI_turb, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_HI_turb_coef_", Sys.Date(), ".jpg"),
       width = 10, height = 8, units = "in")

# beta turb ####
beta_turb <- dwplot(list(beta.turb.moos.lmer, beta.turb.frch.lmer, beta.turb.cari.lmer, beta.turb.poke.lmer, beta.turb.strt.lmer, beta.turb.vaul.lmer), 
                  effects="fixed",
                  dot_args = list(size = 6),
                  whisker_args = list(size = 2)) +
  scale_color_manual(labels = rev(c(bquote(paste("MOOS ", R^{2} == .(format(r.squaredGLMM(beta.turb.moos.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.turb.moos.lmer)))), 
                                bquote(paste("FRCH ", R^{2} == .(format(r.squaredGLMM(beta.turb.frch.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.turb.frch.lmer)))),
                                bquote(paste("CARI ", R^{2} == .(format(r.squaredGLMM(beta.turb.cari.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.turb.cari.lmer)))),
                                bquote(paste("POKE ", R^{2} == .(format(r.squaredGLMM(beta.turb.poke.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.turb.poke.lmer)))),
                                bquote(paste("STRT ", R^{2} == .(format(r.squaredGLMM(beta.turb.strt.lmer)[[1]][1], digits = 2)), " n" == .(nobs(beta.turb.strt.lmer)))),
                     bquote(paste("VAUL ", R^{2} == .(format(r.squaredGLMM(beta.turb.vaul.lmer)[[1]][1], digits = 2)),  " n" == .(nobs(beta.turb.vaul.lmer)))))),
                     values = c("#E7298A", "#66C2A5", "#6A3D9A", "#3288BD", "#FF7F00", "#A6761D"), drop = FALSE) +
  geom_vline(xintercept=0, lty=2) + 
  xlab("effect size") +
  xlim(-0.1, 0.1) +
  scale_y_discrete(labels=c(precip.week_z = "ppt 1 week", precip.month_z = "ppt 1 month", Intensity_z = "ppt event intensity", TimeSinceChena_z = "days since snowmelt")) +
  theme_bw() +
  theme(legend.position = c(0.82, 0.38),
        legend.title = element_blank(),
        legend.text = element_text(size = 18),
        legend.background = element_blank(),
        legend.box.background = element_rect(color = "black", size = 1),
        plot.title = element_text(face = "bold", hjust = 0.5, size =22),
        panel.grid = element_blank(),
        panel.border = element_rect(color = "black", size = 2),
        axis.text = element_text(size = 22),
        axis.title.x = element_text(size = 22),
        plot.margin = margin(0.5,1.5,0.5,0.5, "cm"))

ggsave(beta_turb, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_beta_turb_coef_", Sys.Date(), ".pdf"),
       width = 10, height = 8, units = "in")

ggsave(beta_turb, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_beta_turb_coef_", Sys.Date(), ".jpg"),
       width = 10, height = 8, units = "in")


#### 2 panel turbidity FIGURE 2/14/2026 ####
# 1) Prepare the base panels (your plots: HI_NO3 & beta_no3)
# LEFT panel (A): keep y tick labels; bottom legend; title
p1 <- HI_turb +
  labs(title = "HI - Turb") +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold", hjust = 0.5, size = 22),
    # seam: keep a very small right margin
    plot.margin = margin(t = 18, r = 0, b = 30, l = 12),
    axis.text.y = element_text(size = 22),
    axis.title.x = element_text(size = 22),
    axis.text.x = element_text(size = 22),
    legend.text = element_text(size = 16),
    # ensure no opaque background that would show during overlap
    plot.background = element_rect(fill = NA, color = NA)
  )

# RIGHT panel (B): remove y tick labels; bottom legend; title
p2 <- beta_turb +
  labs(title = "β - Turb") +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold", hjust = 0.5, size = 22),
    # seam: zero left margin to hug panel A
    plot.margin = margin(t = 18, r = 12, b = 30, l = 0),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.x = element_text(size = 22),
    axis.text.x = element_text(size = 22),
    legend.text = element_text(size = 16),
    plot.background = element_rect(fill = NA, color = NA)
  )


# 2) Compose with ggdraw + draw_plot (explicit positioning)
#    - Equal widths for both panels (0.50 each)
#    - Shift panel B slightly left to minimize seam
# Tweak this small offset if needed; typical range 0.004 to 0.02
seam_offset <- 0.0001

combined <- ggdraw() +
  # Panel A: exact left half
  draw_plot(p1, x = 0.00, y = 0.00, width = 0.50, height = 1.00) +
  # Panel B: same width but nudged left by seam_offset
  draw_plot(p2, x = 0.50 - seam_offset, y = 0.00, width = 0.375, height = 1.00) +
  # A/B labels (top-left of each panel area)
  draw_plot_label(
    label = c("A", "B"),
    x = c(0.11, 0.51 - seam_offset),  # keep tag near left of each panel
    y = c(0.98, 0.98),
    size = 22,
    fontface = "bold"
  )
# 3) Save (keep your large width to protect bottom legends)

ggsave(combined, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_2_panel_TURB_coef_", Sys.Date(), ".jpg"),
       width = 23, height = 10, units = "in")



```







# ============================= GRAVEYARD ========================================
```{r}
<<<<<<< Updated upstream
ggsave(multi.coef, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_beta_turb_coef_", Sys.Date(), ".pdf"),
       width = 10, height = 8, units = "in")
<<<<<<< Updated upstream

ggsave(multi.coef, path = here("plots", "Coefficient_Plots"),
       file = paste0("FigX_beta_turb_coef_", Sys.Date(), ".jpg"),
       width = 10, height = 8, units = "in")

=======
=======
ggsave(multi.coef, path = here("plots", "Coefficient_Plots"), file = "FigX_HI_NO3_coef.pdf", width = 10, height = 8, units = "in")

# NO3 beta mods = beta.no3.moos.lmer, etc.

>>>>>>> Stashed changes
>>>>>>> Stashed changes




```