---
title: "09a_Antecedent_Conditions_models"
author: "Jake Cavaiani, Tamara Harms"
date: "9/2/2022, edited 9/22/2025"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---
The purpose of this script is to model HI/BETA against storm attributes, antecedent moisture conditions, and seasonality for each individual catchment and constituent using linear regression 

Input: Antecedent moisture conditions with HI_FI_BETA and catchment characteristics!

Step 1) import full file 
Step 2) standardize and center the data
Step 3) Model! Model structure is lm(Hyst_index ~ StormPrecip + PrecipWeek + PrecipMonth + TimeSinceChena, data = HI_FI_NO3_xxxx)
Step 4) Check model assumptions
Step 5) Plot all models 

Output: linear model plot 

```{r load-packages, include=FALSE}
library(magrittr)
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(data.table)
library(scales)
library(lme4)
library(nlme)
library(datasets)
library(arm)
library(AICcmodavg)
library(gridExtra)
library(grid)
library(ggpmisc)
library(boot)
library(here)
library(broom)
library(viridis)
library(car)
library(MuMIn)
library(ggeffects)
library(dotwhisker)
library(jtools)
library(GGally)
library(dotwhisker)

```

```{r}
# Read in data # 

AMC <- read.csv(here("Output_from_analysis", "compare_JSC_ATW_storm_totals", "updated_AMC_HI_BETA_file_2509.csv"))

AMC <- AMC %>% mutate(date = as.Date(date, format = "%Y-%m-%d")) %>%
               mutate(year = format(date, "%Y"))

```

```{r, echo=FALSE}
### Prelim visualize data ###
pNO3 <- AMC %>% filter(response_var == "NO3")
ggpairs(pNO3, columns = c("precip.week", "precip.month", "ThreeMonth", "temp.week", "Intensity", "TimeSinceChena", "Hyst_index"), mapping = aes(color = site.ID))

NO3_POKE <- AMC %>% filter(response_var == "NO3") %>% filter(site.ID == "VAUL")
ggpairs(NO3_POKE, columns = c("precip.week", "precip.month", "ThreeMonth", "Intensity", "TimeSinceChena", "Hyst_index"), mapping = aes(color = as.factor(year)))

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena + Hyst_index, data = NO3_POKE, col = as.factor(NO3_POKE$year))

```
### Uncorrelated antecedent conditions to include: precip.week, precip.month, Intensity, TimeSinceChena
## precip.week & precip.month might be correlated for some years and are correlated across all years. Using year as random effect

### Scaling and normalizing data ### 
```{r, echo=FALSE}

# scale & standardize predictors # 
# add hard code ln-HI & beta for use w/ ggparis plotting
varnames <- c("precip.week", "precip.month", "ThreeMonth", "Intensity", "TimeSinceChena")
AMC <- AMC %>% mutate(across(starts_with(varnames), ~as.numeric(scale (., center = TRUE, scale = TRUE)), .names = "{.col}_z")) %>%
               mutate(ln_HI = log(Hyst_index + 1)) %>%
               mutate(ln_beta = log(Beta_index + 7))
  

```

```{r}
#########################
### Regression models ###
#########################
### HI ###
## NO3 ##

# MOOS #
pairs <- AMC %>% filter(site.ID == "MOOS" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_lnNO3_MOOS_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.no3.moos.lmer <- AMC %>% filter(site.ID == "MOOS" & response_var == "NO3") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.no3.moos.lmer)
qqnorm(resid(hi.no3.moos.lmer,  type = "pearson"))
qqline(resid(hi.no3.moos.lmer,  type = "pearson"))
plot(hi.no3.moos.lmer)
summary(hi.no3.moos.lmer)
confint(hi.no3.moos.lmer)
r.squaredGLMM(hi.no3.moos.lmer)

## Check effect of outlier
mod1.out <- AMC %>% filter(site.ID == "MOOS" & response_var == "NO3") %>%
                    filter(precip.week_z < 2) %>%
                    lmer(Hyst_index ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

summary(mod1.out)
confint(mod1.out)
# Same qualitative result

# FRCH #
pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_NO3_FRCH_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.no3.frch.lmer <- AMC %>% filter(site.ID == "FRCH" & response_var == "NO3") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.no3.frch.lmer)
qqnorm(resid(hi.no3.frch.lmer,  type = "pearson"))
qqline(resid(hi.no3.frch.lmer,  type = "pearson"))
plot(hi.no3.frch.lmer)
summary(hi.no3.frch.lmer)
confint(hi.no3.frch.lmer)
r.squaredGLMM(hi.no3.frch.lmer)

# POKE #
pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_NO3_POKE_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.no3.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "NO3") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.no3.poke.lmer)
# ppt month & week too strongly correlated

# Remove precip.week from model
hi.no3.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "NO3") %>%
                lmer(ln_HI ~ precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.no3.poke.lmer)
qqnorm(resid(hi.no3.poke.lmer,  type = "pearson"))
qqline(resid(hi.no3.poke.lmer,  type = "pearson"))
plot(hi.no3.poke.lmer)
summary(hi.no3.poke.lmer)
confint(hi.no3.poke.lmer)
r.squaredGLMM(hi.no3.poke.lmer)

## Random var = 0. Check lm
mod3.lm <- AMC %>% filter(site.ID == "POKE" & response_var == "NO3") %>%
                lm(ln_HI ~ precip.month_z + TimeSinceChena + Intensity_z, data = .)
summary(mod3.lm)
# same qualitative result. Nothing significant.

# CARI #
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_NO3_CARI_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.no3.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "NO3") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.no3.cari.lmer)
# ppt month & week too strongly correlated

# Remove precip.week from model
hi.no3.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "NO3") %>%
                lmer(ln_HI ~ precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.no3.cari.lmer)
qqnorm(resid(hi.no3.cari.lmer,  type = "pearson"))
qqline(resid(hi.no3.cari.lmer,  type = "pearson"))
plot(hi.no3.cari.lmer)
summary(hi.no3.cari.lmer)
confint(hi.no3.cari.lmer)
r.squaredGLMM(hi.no3.cari.lmer)

# STRT #
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_NO3_STRT_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.no3.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "NO3") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.no3.strt.lmer)
#ppt_week & ppt_month too strongly correlated

hi.no3.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "NO3") %>%
                lmer(ln_HI ~ precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.no3.strt.lmer)
qqnorm(resid(hi.no3.strt.lmer,  type = "pearson"))
qqline(resid(hi.no3.strt.lmer,  type = "pearson"))
plot(hi.no3.strt.lmer)
summary(hi.no3.strt.lmer)
confint(hi.no3.strt.lmer)
r.squaredGLMM(hi.no3.strt.lmer)

# VAUL #
pairs <- AMC %>% filter(site.ID == "VAUL" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_NO3_VAUL_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

NO3_VAUL <- AMC %>% filter(response_var == "NO3") %>% filter(site.ID == "VAUL")

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena + ln_HI, data = NO3_VAUL, col = as.factor(NO3_VAUL$year))

hi.no3.vaul.lmer <- AMC %>% filter(site.ID == "VAUL" & response_var == "NO3") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.no3.vaul.lmer)
qqnorm(resid(hi.no3.vaul.lmer,  type = "pearson"))
qqline(resid(hi.no3.vaul.lmer,  type = "pearson"))
plot(hi.no3.vaul.lmer)
summary(hi.no3.vaul.lmer)
confint(hi.no3.vaul.lmer)
r.squaredGLMM(hi.no3.vaul.lmer)
```

```{r}
## fDOM ##

# MOOS #
pairs <- AMC %>% filter(site.ID == "MOOS" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_fDOM_MOOS_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.fdom.moos.lmer <- AMC %>% filter(site.ID == "MOOS" & response_var == "fDOM") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.fdom.moos.lmer)
qqnorm(resid(hi.fdom.moos.lmer,  type = "pearson"))
qqline(resid(hi.fdom.moos.lmer,  type = "pearson"))
plot(hi.fdom.moos.lmer)
summary(hi.fdom.moos.lmer)
confint(hi.fdom.moos.lmer)
r.squaredGLMM(hi.fdom.moos.lmer)

# random var = 0. Compare w/ lm
hi.fdom.moos.lm <- AMC %>% filter(site.ID == "MOOS" & response_var == "fDOM") %>%
                lm(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z, data = .)
summary(hi.fdom.moos.lm)
# qualitatively same as lmer

# FRCH #
pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_fDOM_FRCH_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.fdom.frch.lmer <- AMC %>% filter(site.ID == "FRCH" & response_var == "fDOM") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.fdom.frch.lmer)
qqnorm(resid(hi.fdom.frch.lmer,  type = "pearson"))
qqline(resid(hi.fdom.frch.lmer,  type = "pearson"))
plot(hi.fdom.frch.lmer)
summary(hi.fdom.frch.lmer)
confint(hi.fdom.frch.lmer)
r.squaredGLMM(hi.fdom.frch.lmer)

# CARI #
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_fDOM_CARI_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.fdom.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "fDOM") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.fdom.cari.lmer)
# ppt week & ppt month too strongly correlated

hi.fdom.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "fDOM") %>%
                lmer(ln_HI ~ precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.fdom.cari.lmer)
qqnorm(resid(hi.fdom.cari.lmer,  type = "pearson"))
qqline(resid(hi.fdom.cari.lmer,  type = "pearson"))
plot(hi.fdom.cari.lmer)
summary(hi.fdom.cari.lmer)
confint(hi.fdom.cari.lmer)
r.squaredGLMM(hi.fdom.cari.lmer)

pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_fDOM_POKE_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.fdom.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "fDOM") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.fdom.poke.lmer)
# ppt week & ppt month too strongly correlated

hi.fdom.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "fDOM") %>%
                lmer(ln_HI ~ precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.fdom.poke.lmer)
qqnorm(resid(hi.fdom.poke.lmer,  type = "pearson"))
qqline(resid(hi.fdom.poke.lmer,  type = "pearson"))
plot(hi.fdom.poke.lmer)
summary(hi.fdom.poke.lmer)
confint(hi.fdom.poke.lmer)
r.squaredGLMM(hi.fdom.poke.lmer)

# STRT #
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_fDOM_STRT_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.fdom.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "fDOM") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.fdom.strt.lmer)
qqnorm(resid(hi.fdom.strt.lmer,  type = "pearson"))
qqline(resid(hi.fdom.strt.lmer,  type = "pearson"))
plot(hi.fdom.strt.lmer)
summary(hi.fdom.strt.lmer)
confint(hi.fdom.strt.lmer)
r.squaredGLMM(hi.fdom.strt.lmer)

# VAUL #
pairs <- AMC %>% filter(site.ID == "VAUL" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_fDOM_VAUL_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

fdom_VAUL <- AMC %>% filter(response_var == "fDOM") %>% filter(site.ID == "VAUL")

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena + ln_HI, data = fdom_VAUL, col = as.factor(fdom_VAUL$year))

hi.fdom.vaul.lmer <- AMC %>% filter(site.ID == "VAUL" & response_var == "fDOM") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.fdom.vaul.lmer)
qqnorm(resid(hi.fdom.vaul.lmer,  type = "pearson"))
qqline(resid(hi.fdom.vaul.lmer,  type = "pearson"))
plot(hi.fdom.vaul.lmer)
summary(hi.fdom.vaul.lmer)
confint(hi.fdom.vaul.lmer)
r.squaredGLMM(hi.fdom.vaul.lmer)

# random var = 0. Check lm
hi.fdom.vaul.lm <- AMC %>% filter(site.ID == "VAUL" & response_var == "fDOM") %>%
                lm(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z, data = .)
summary(hi.fdom.vaul.lm)
# same qualitative result
```

```{r}
## SpCond ##

# MOOS #
pairs <- AMC %>% filter(site.ID == "MOOS" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_SPC_MOOS_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.spc.moos.lmer <- AMC %>% filter(site.ID == "MOOS" & response_var == "SPC") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.spc.moos.lmer)
qqnorm(resid(hi.spc.moos.lmer,  type = "pearson"))
qqline(resid(hi.spc.moos.lmer,  type = "pearson"))
plot(hi.spc.moos.lmer)
summary(hi.spc.moos.lmer)
confint(hi.spc.moos.lmer)
r.squaredGLMM(hi.spc.moos.lmer)

# random var = 0. Compare w/ lm
hi.spc.moos.lm <- AMC %>% filter(site.ID == "MOOS" & response_var == "SPC") %>%
                lm(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z, data = .)
summary(hi.spc.moos.lm)
# qualitatively same as lmer

# FRCH #
pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_SPC_FRCH_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.spc.frch.lmer <- AMC %>% filter(site.ID == "FRCH" & response_var == "SPC") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.spc.frch.lmer)
qqnorm(resid(hi.spc.frch.lmer,  type = "pearson"))
qqline(resid(hi.spc.frch.lmer,  type = "pearson"))
plot(hi.spc.frch.lmer)
summary(hi.spc.frch.lmer)
confint(hi.spc.frch.lmer)
r.squaredGLMM(hi.spc.frch.lmer)

# Random var low relative to resid. Check lm.
hi.spc.frch.lm <- AMC %>% filter(site.ID == "FRCH" & response_var == "SPC") %>%
                lm(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z, data = .)
summary(hi.spc.frch.lm)
# qualitatively similar to lmer

# POKE #
pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_SPC_POKE_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

# filter 2 outliers
pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "SPC" & ln_HI > 0) %>% 
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_SPC_POKE_pairs_2out.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.spc.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "SPC" & ln_HI > 0) %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.spc.poke.lmer)
# ppt_week & ppt_month too correlated

hi.spc.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "SPC" & ln_HI > 0) %>%
                lmer(ln_HI ~ precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.spc.poke.lmer)
qqnorm(resid(hi.spc.poke.lmer,  type = "pearson"))
qqline(resid(hi.spc.poke.lmer,  type = "pearson"))
plot(hi.spc.poke.lmer)
summary(hi.spc.poke.lmer)
confint(hi.spc.poke.lmer)
r.squaredGLMM(hi.spc.poke.lmer)

# CARI #
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_SPC_CARI_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.spc.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "SPC") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.spc.cari.lmer)
# ppt_week & ppt_month too correlated

hi.spc.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "SPC") %>%
                lmer(ln_HI ~ precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.spc.cari.lmer)
qqnorm(resid(hi.spc.cari.lmer,  type = "pearson"))
qqline(resid(hi.spc.cari.lmer,  type = "pearson"))
plot(hi.spc.cari.lmer)
summary(hi.spc.cari.lmer)
confint(hi.spc.cari.lmer)
r.squaredGLMM(hi.spc.cari.lmer)

# STRT #
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_SPC_STRT_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.fdom.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "SPC") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.fdom.strt.lmer)
qqnorm(resid(hi.fdom.strt.lmer,  type = "pearson"))
qqline(resid(hi.fdom.strt.lmer,  type = "pearson"))
plot(hi.fdom.strt.lmer)
summary(hi.fdom.strt.lmer)
confint(hi.fdom.strt.lmer)
r.squaredGLMM(hi.fdom.strt.lmer)

# VAUL #
pairs <- AMC %>% filter(site.ID == "VAUL" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))

spc_VAUL <- AMC %>% filter(response_var == "SPC") %>% filter(site.ID == "VAUL")

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena + ln_HI, data = spc_VAUL, col = as.factor(spc_VAUL$year))
# 1 large negative outlier- remove

spc_VAUL <- AMC %>% filter(response_var == "SPC") %>% filter(site.ID == "VAUL") %>% filter(ln_HI >= -0.5)

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena + ln_HI, data = spc_VAUL, col = as.factor(spc_VAUL$year))

hi.spc.vaul.lmer <- AMC %>% filter(site.ID == "VAUL" & response_var == "SPC" & ln_HI >= -0.5) %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.spc.vaul.lmer)
qqnorm(resid(hi.spc.vaul.lmer,  type = "pearson"))
qqline(resid(hi.spc.vaul.lmer,  type = "pearson"))
plot(hi.spc.vaul.lmer)
# not great
summary(hi.spc.vaul.lmer)
confint(hi.spc.vaul.lmer)
r.squaredGLMM(hi.spc.vaul.lmer)

# random var = 0. Check lm
hi.fdom.vaul.lm <- AMC %>% filter(site.ID == "VAUL" & response_var == "fDOM") %>%
                lm(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z, data = .)
summary(hi.fdom.vaul.lm)
# same qualitative result
```

```{r}
## Turb ##

# MOOS #
pairs <- AMC %>% filter(site.ID == "MOOS" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_turb_MOOS_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.turb.moos.lmer <- AMC %>% filter(site.ID == "MOOS" & response_var == "turb") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.turb.moos.lmer)
qqnorm(resid(hi.turb.moos.lmer,  type = "pearson"))
qqline(resid(hi.turb.moos.lmer,  type = "pearson"))
plot(hi.turb.moos.lmer)
summary(hi.turb.moos.lmer)
confint(hi.turb.moos.lmer)
r.squaredGLMM(hi.turb.moos.lmer)

# FRCH #
pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_turb_FRCH_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.turb.frch.lmer <- AMC %>% filter(site.ID == "FRCH" & response_var == "turb") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.turb.frch.lmer)
qqnorm(resid(hi.turb.frch.lmer,  type = "pearson"))
qqline(resid(hi.turb.frch.lmer,  type = "pearson"))
plot(hi.turb.frch.lmer)
summary(hi.turb.frch.lmer)
confint(hi.turb.frch.lmer)
r.squaredGLMM(hi.turb.frch.lmer)

# POKE #
pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_turb_POKE_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.turb.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "turb") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.turb.poke.lmer)
qqnorm(resid(hi.turb.poke.lmer,  type = "pearson"))
qqline(resid(hi.turb.poke.lmer,  type = "pearson"))
plot(hi.turb.poke.lmer)
summary(hi.turb.poke.lmer)
confint(hi.turb.poke.lmer)
r.squaredGLMM(hi.turb.poke.lmer)

# CARI #
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_turb_CARI_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.turb.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "turb") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.turb.cari.lmer)
# ppt_week & ppt_month too correlated

hi.turb.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "turb") %>%
                lmer(ln_HI ~ precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.turb.cari.lmer)
qqnorm(resid(hi.turb.cari.lmer,  type = "pearson"))
qqline(resid(hi.turb.cari.lmer,  type = "pearson"))
plot(hi.turb.cari.lmer)
summary(hi.turb.cari.lmer)
confint(hi.turb.cari.lmer)
r.squaredGLMM(hi.turb.cari.lmer)

# No variance associated with year. Check lm
hi.turb.cari.lm <- AMC %>% filter(site.ID == "CARI" & response_var == "turb") %>%
                           lm(ln_HI ~ precip.month_z + TimeSinceChena + Intensity_z , data = .)
summary(hi.turb.cari.lm)

# STRT #
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_turb_STRT_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

hi.turb.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "turb") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.turb.strt.lmer)
qqnorm(resid(hi.turb.strt.lmer,  type = "pearson"))
qqline(resid(hi.turb.strt.lmer,  type = "pearson"))
plot(hi.turb.strt.lmer)
summary(hi.turb.strt.lmer)
confint(hi.turb.strt.lmer)
r.squaredGLMM(hi.turb.strt.lmer)

# VAUL #
pairs <- AMC %>% filter(site.ID == "VAUL" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_HI"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_fDOM_VAUL_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

turb_VAUL <- AMC %>% filter(response_var == "turb") %>% filter(site.ID == "VAUL")

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena + ln_HI, data = turb_VAUL, col = as.factor(turb_VAUL$year))

hi.turb.vaul.lmer <- AMC %>% filter(site.ID == "VAUL" & response_var == "turb") %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(hi.turb.vaul.lmer)
qqnorm(resid(hi.turb.vaul.lmer,  type = "pearson"))
qqline(resid(hi.turb.vaul.lmer,  type = "pearson"))
plot(hi.turb.vaul.lmer)
summary(hi.turb.vaul.lmer)
confint(hi.turb.vaul.lmer)
r.squaredGLMM(hi.turb.vaul.lmer)

```

```{r}
### BETA ###
## NO3 ##

# MOOS #
pairs <- AMC %>% filter(site.ID == "MOOS" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_lnbeta_NO3_MOOS_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.no3.moos.lmer <- AMC %>% filter(site.ID == "MOOS" & response_var == "NO3") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.no3.moos.lmer)
qqnorm(resid(beta.no3.moos.lmer,  type = "pearson"))
qqline(resid(beta.no3.moos.lmer,  type = "pearson"))
plot(beta.no3.moos.lmer)
summary(beta.no3.moos.lmer)
confint(beta.no3.moos.lmer)
r.squaredGLMM(beta.no3.moos.lmer)

# FRCH #
pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_lnbeta_NO3_FRCH_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.no3.frch.lmer <- AMC %>% filter(site.ID == "FRCH" & response_var == "NO3") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.no3.frch.lmer)
qqnorm(resid(beta.no3.frch.lmer,  type = "pearson"))
qqline(resid(beta.no3.frch.lmer,  type = "pearson"))
plot(beta.no3.frch.lmer)
summary(beta.no3.frch.lmer)
confint(beta.no3.frch.lmer)
r.squaredGLMM(beta.no3.frch.lmer)

# POKE #
pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
# remove 1 outlier
pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "NO3" & ln_beta <= 2.4) %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_lnbeta_NO3_POKE_pairs_1out.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.no3.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "NO3" & ln_beta <= 2.4) %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.no3.poke.lmer)
# ppt month & week too strongly correlated

# Remove precip.week from model
beta.no3.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "NO3" & ln_beta <= 2.4) %>%
                lmer(ln_beta ~ precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.no3.poke.lmer)
qqnorm(resid(beta.no3.poke.lmer,  type = "pearson"))
qqline(resid(beta.no3.poke.lmer,  type = "pearson"))
plot(beta.no3.poke.lmer)
summary(beta.no3.poke.lmer)
confint(beta.no3.poke.lmer)
r.squaredGLMM(hi.no3.poke.lmer)

# CARI #
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_lnbeta_NO3_CARI_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

# remove 3 outliers
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "NO3" & ln_beta >= 1.5) %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "HI_lnbeta_NO3_CARI_pairs_3out.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.no3.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "NO3" & ln_beta >= 1.5) %>%
                lmer(ln_HI ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.no3.cari.lmer)
# ppt month & week too strongly correlated

# Remove precip.week from model
beta.no3.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "NO3" & ln_beta >= 1.5) %>%
                lmer(ln_HI ~ precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.no3.cari.lmer)
qqnorm(resid(beta.no3.cari.lmer,  type = "pearson"))
qqline(resid(beta.no3.cari.lmer,  type = "pearson"))
plot(beta.no3.cari.lmer)
summary(beta.no3.cari.lmer)
confint(beta.no3.cari.lmer)
r.squaredGLMM(beta.no3.cari.lmer)

# STRT #
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_NO3_STRT_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.no3.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "NO3") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.no3.strt.lmer)
#ppt_week & ppt_month too strongly correlated

beta.no3.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "NO3") %>%
                lmer(ln_beta ~ precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.no3.strt.lmer)
qqnorm(resid(beta.no3.strt.lmer,  type = "pearson"))
qqline(resid(beta.no3.strt.lmer,  type = "pearson"))
plot(beta.no3.strt.lmer)
summary(beta.no3.strt.lmer)
confint(beta.no3.strt.lmer)
r.squaredGLMM(beta.no3.strt.lmer)

# VAUL #
pairs <- AMC %>% filter(site.ID == "VAUL" & response_var == "NO3") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_NO3_VAUL_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

NO3_VAUL <- AMC %>% filter(response_var == "NO3") %>% filter(site.ID == "VAUL")

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena + ln_beta, data = NO3_VAUL, col = as.factor(NO3_VAUL$year))
# low outlier - remove

NO3_VAUL <- AMC %>% filter(response_var == "NO3") %>% filter(site.ID == "VAUL") %>% filter(ln_beta > 1.6)

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena + ln_beta, data = NO3_VAUL, col = as.factor(NO3_VAUL$year))

beta.no3.vaul.lmer <- AMC %>% filter(site.ID == "VAUL" & response_var == "NO3" & ln_beta >= 1.6) %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.no3.vaul.lmer)
qqnorm(resid(beta.no3.vaul.lmer,  type = "pearson"))
qqline(resid(beta.no3.vaul.lmer,  type = "pearson"))
plot(beta.no3.vaul.lmer)
summary(beta.no3.vaul.lmer)
confint(beta.no3.vaul.lmer)
r.squaredGLMM(beta.no3.vaul.lmer)
```

```{r}
## fDOM ##

# MOOS #
pairs <- AMC %>% filter(site.ID == "MOOS" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_fDOM_MOOS_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.fdom.moos.lmer <- AMC %>% filter(site.ID == "MOOS" & response_var == "fDOM") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.fdom.moos.lmer)
qqnorm(resid(beta.fdom.moos.lmer,  type = "pearson"))
qqline(resid(beta.fdom.moos.lmer,  type = "pearson"))
plot(beta.fdom.moos.lmer)
summary(beta.fdom.moos.lmer)
confint(beta.fdom.moos.lmer)
r.squaredGLMM(beta.fdom.moos.lmer)

# FRCH #
pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
#low loutlier- remove

pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "fDOM" & ln_beta > 1.6) %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))

ggsave(pairs, file = "beta_fDOM_FRCH_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.fdom.frch.lmer <- AMC %>% filter(site.ID == "FRCH" & response_var == "fDOM" & ln_beta >= 1.6) %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.fdom.frch.lmer)
qqnorm(resid(beta.fdom.frch.lmer,  type = "pearson"))
qqline(resid(beta.fdom.frch.lmer,  type = "pearson"))
plot(beta.fdom.frch.lmer)
summary(beta.fdom.frch.lmer)
confint(beta.fdom.frch.lmer)
r.squaredGLMM(beta.fdom.frch.lmer)

# CARI #
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_fDOM_CARI_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.fdom.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "fDOM") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.fdom.cari.lmer)
# ppt week & ppt month too strongly correlated

beta.fdom.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "fDOM") %>%
                lmer(ln_beta ~ precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.fdom.cari.lmer)
qqnorm(resid(beta.fdom.cari.lmer,  type = "pearson"))
qqline(resid(beta.fdom.cari.lmer,  type = "pearson"))
plot(beta.fdom.cari.lmer)
summary(beta.fdom.cari.lmer)
confint(beta.fdom.cari.lmer)
r.squaredGLMM(beta.fdom.cari.lmer)

# POKE #
pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_fDOM_POKE_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.fdom.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "fDOM") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.fdom.poke.lmer)
qqnorm(resid(beta.fdom.poke.lmer,  type = "pearson"))
qqline(resid(beta.fdom.poke.lmer,  type = "pearson"))
plot(beta.fdom.poke.lmer)
summary(beta.fdom.poke.lmer)
confint(beta.fdom.poke.lmer)
r.squaredGLMM(beta.fdom.poke.lmer)

# STRT #
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_fDOM_STRT_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.fdom.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "fDOM") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.fdom.strt.lmer)
qqnorm(resid(beta.fdom.strt.lmer,  type = "pearson"))
qqline(resid(beta.fdom.strt.lmer,  type = "pearson"))
plot(beta.fdom.strt.lmer)
summary(beta.fdom.strt.lmer)
confint(beta.fdom.strt.lmer)
r.squaredGLMM(beta.fdom.strt.lmer)

# VAUL #
pairs <- AMC %>% filter(site.ID == "VAUL" & response_var == "fDOM") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_fDOM_VAUL_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

fdom_VAUL <- AMC %>% filter(response_var == "fDOM") %>% filter(site.ID == "VAUL")

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena + ln_beta, data = fdom_VAUL, col = as.factor(fdom_VAUL$year))

beta.fdom.vaul.lmer <- AMC %>% filter(site.ID == "VAUL" & response_var == "fDOM") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.fdom.vaul.lmer)
qqnorm(resid(beta.fdom.vaul.lmer,  type = "pearson"))
qqline(resid(beta.fdom.vaul.lmer,  type = "pearson"))
plot(beta.fdom.vaul.lmer)
summary(beta.fdom.vaul.lmer)
confint(beta.fdom.vaul.lmer)
r.squaredGLMM(beta.fdom.vaul.lmer)


```

```{r}
## SpCond ##

# MOOS #
pairs <- AMC %>% filter(site.ID == "MOOS" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_SPC_MOOS_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.spc.moos.lmer <- AMC %>% filter(site.ID == "MOOS" & response_var == "SPC") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.spc.moos.lmer)
qqnorm(resid(beta.spc.moos.lmer,  type = "pearson"))
qqline(resid(beta.spc.moos.lmer,  type = "pearson"))
plot(beta.spc.moos.lmer)
# not great
summary(beta.spc.moos.lmer)
confint(beta.spc.moos.lmer)
r.squaredGLMM(beta.spc.moos.lmer)

# FRCH #
pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
# two large positive ouliers, both from 2020- removing
pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "SPC" & ln_beta < 2) %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))

ggsave(pairs, file = "beta_SPC_FRCH_pairs_rem2out.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.spc.frch.lmer <- AMC %>% filter(site.ID == "FRCH" & response_var == "SPC" & ln_beta < 2) %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.spc.frch.lmer)
qqnorm(resid(beta.spc.frch.lmer,  type = "pearson"))
qqline(resid(beta.spc.frch.lmer,  type = "pearson"))
plot(beta.spc.frch.lmer)
summary(beta.spc.frch.lmer)
confint(beta.spc.frch.lmer)
r.squaredGLMM(beta.spc.frch.lmer)

# POKE #
pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_SPC_POKE_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.spc.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "SPC") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.spc.poke.lmer)
qqnorm(resid(beta.spc.poke.lmer,  type = "pearson"))
qqline(resid(beta.spc.poke.lmer,  type = "pearson"))
plot(beta.spc.poke.lmer)
summary(beta.spc.poke.lmer)
confint(beta.spc.poke.lmer)
r.squaredGLMM(beta.spc.poke.lmer)

# CARI #
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
      
ggsave(pairs, file = "beta_SPC_CARI_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

# negative outlier- remove
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "SPC" & ln_beta > 0) %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))

ggsave(pairs, file = "HI_SPC_CARI_pairs_out.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.spc.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "SPC" & ln_beta > 0) %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.spc.cari.lmer)
# ppt_week & ppt_month too correlated

beta.spc.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "SPC" & ln_beta > 0) %>%
                lmer(ln_beta ~ precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.spc.cari.lmer)
qqnorm(resid(beta.spc.cari.lmer,  type = "pearson"))
qqline(resid(beta.spc.cari.lmer,  type = "pearson"))
plot(beta.spc.cari.lmer)
summary(beta.spc.cari.lmer)
confint(beta.spc.cari.lmer)
r.squaredGLMM(beta.spc.cari.lmer)

# STRT #
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_SPC_STRT_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

# positive outlier- remove
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "SPC" & ln_beta < 2) %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_SPC_STRT_pairs_out.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")


beta.fdom.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "SPC" & ln_beta < 2) %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.fdom.strt.lmer)
qqnorm(resid(beta.fdom.strt.lmer,  type = "pearson"))
qqline(resid(beta.fdom.strt.lmer,  type = "pearson"))
plot(beta.fdom.strt.lmer)
summary(beta.fdom.strt.lmer)
confint(beta.fdom.strt.lmer)
r.squaredGLMM(beta.fdom.strt.lmer)

# VAUL #
pairs <- AMC %>% filter(site.ID == "VAUL" & response_var == "SPC") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
spc_VAUL <- AMC %>% filter(response_var == "SPC") %>% filter(site.ID == "VAUL")

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena + ln_beta, data = spc_VAUL, col = as.factor(spc_VAUL$year))
# 1 large negative outlier- remove

spc_VAUL <- AMC %>% filter(response_var == "SPC") %>% filter(site.ID == "VAUL") %>% filter(ln_beta >= 1.6)

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena + ln_beta, data = spc_VAUL, col = as.factor(spc_VAUL$year))

beta.spc.vaul.lmer <- AMC %>% filter(site.ID == "VAUL" & response_var == "SPC" & ln_beta >= 1.6) %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.spc.vaul.lmer)
qqnorm(resid(beta.spc.vaul.lmer,  type = "pearson"))
qqline(resid(beta.spc.vaul.lmer,  type = "pearson"))
plot(beta.spc.vaul.lmer)
summary(beta.spc.vaul.lmer)
confint(beta.spc.vaul.lmer)
r.squaredGLMM(beta.spc.vaul.lmer)

```

```{r}
## Turb ##

# MOOS #
pairs <- AMC %>% filter(site.ID == "MOOS" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_turb_MOOS_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.turb.moos.lmer <- AMC %>% filter(site.ID == "MOOS" & response_var == "turb") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.turb.moos.lmer)
qqnorm(resid(beta.turb.moos.lmer,  type = "pearson"))
qqline(resid(beta.turb.moos.lmer,  type = "pearson"))
plot(beta.turb.moos.lmer)
summary(beta.turb.moos.lmer)
confint(beta.turb.moos.lmer)
r.squaredGLMM(beta.turb.moos.lmer)

# FRCH #
pairs <- AMC %>% filter(site.ID == "FRCH" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_turb_FRCH_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.turb.frch.lmer <- AMC %>% filter(site.ID == "FRCH" & response_var == "turb") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.turb.frch.lmer)
qqnorm(resid(beta.turb.frch.lmer,  type = "pearson"))
qqline(resid(beta.turb.frch.lmer,  type = "pearson"))
plot(beta.turb.frch.lmer)
summary(beta.turb.frch.lmer)
confint(beta.turb.frch.lmer)
r.squaredGLMM(beta.turb.frch.lmer)

# POKE #
pairs <- AMC %>% filter(site.ID == "POKE" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_turb_POKE_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.turb.poke.lmer <- AMC %>% filter(site.ID == "POKE" & response_var == "turb") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.turb.poke.lmer)
qqnorm(resid(beta.turb.poke.lmer,  type = "pearson"))
qqline(resid(beta.turb.poke.lmer,  type = "pearson"))
plot(beta.turb.poke.lmer)
summary(beta.turb.poke.lmer)
confint(beta.turb.poke.lmer)
r.squaredGLMM(beta.turb.poke.lmer)

# CARI #
pairs <- AMC %>% filter(site.ID == "CARI" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_turb_CARI_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.turb.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "turb") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.turb.cari.lmer)
# ppt_week & ppt_month too correlated

beta.turb.cari.lmer <- AMC %>% filter(site.ID == "CARI" & response_var == "turb") %>%
                lmer(ln_beta ~ precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.turb.cari.lmer)
qqnorm(resid(beta.turb.cari.lmer,  type = "pearson"))
qqline(resid(beta.turb.cari.lmer,  type = "pearson"))
plot(beta.turb.cari.lmer)
summary(beta.turb.cari.lmer)
confint(beta.turb.cari.lmer)
r.squaredGLMM(beta.turb.cari.lmer)

# STRT #
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
        
ggsave(pairs, file = "beta_turb_STRT_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

# remove low outlier
pairs <- AMC %>% filter(site.ID == "STRT" & response_var == "turb" & ln_beta > 1.9) %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))
   
ggsave(pairs, file = "beta_turb_STRT_pairs_out.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10, units = "in")

beta.turb.strt.lmer <- AMC %>% filter(site.ID == "STRT" & response_var == "turb") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.turb.strt.lmer)
qqnorm(resid(beta.turb.strt.lmer,  type = "pearson"))
qqline(resid(beta.turb.strt.lmer,  type = "pearson"))
# not great- lower tail
plot(beta.turb.strt.lmer)
summary(beta.turb.strt.lmer)
confint(beta.turb.strt.lmer)
r.squaredGLMM(beta.turb.strt.lmer)

# VAUL #
pairs <- AMC %>% filter(site.ID == "VAUL" & response_var == "turb") %>%
        ggpairs(columns = c("precip.week_z", "precip.month_z", "ThreeMonth_z", "Intensity_z", "TimeSinceChena", "ln_beta"), mapping = aes(color = as.factor(year)))

turb_VAUL <- AMC %>% filter(response_var == "turb") %>% filter(site.ID == "VAUL")

pairs(~precip.week + precip.month + ThreeMonth + Intensity + TimeSinceChena + ln_beta, data = turb_VAUL, col = as.factor(turb_VAUL$year))

beta.turb.vaul.lmer <- AMC %>% filter(site.ID == "VAUL" & response_var == "turb") %>%
                lmer(ln_beta ~ precip.week_z + precip.month_z + TimeSinceChena + Intensity_z + (1|year), data = .)

vif(beta.turb.vaul.lmer)
qqnorm(resid(beta.turb.vaul.lmer,  type = "pearson"))
qqline(resid(beta.turb.vaul.lmer,  type = "pearson"))
plot(beta.turb.vaul.lmer)
summary(beta.turb.vaul.lmer)
confint(beta.turb.vaul.lmer)
r.squaredGLMM(beta.turb.vaul.lmer)

```

```{r}
#############
### PLOTS ###
#############
## Effect sizes: Multiple models on one figure ##
## HI ##
# NO3 #
multi.coef <- dwplot(list(hi.no3.moos.lmer, hi.no3.frch.lmer, hi.no3.poke.lmer, hi.no3.cari.lmer, hi.no3.strt.lmer, hi.no3.vaul.lmer), 
                  effects="fixed",
                  dot_args = list(size = 6),
                  whisker_args = list(size = 2)) +
  scale_color_manual(labels = c(bquote(paste("MOOS ", R^{2} == .(format(r.squaredGLMM(hi.no3.moos.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.no3.moos.lmer)))), 
                                bquote(paste("FRCH ", R^{2} == .(format(r.squaredGLMM(hi.no3.frch.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.no3.frch.lmer)))),
                                bquote(paste("POKE ", R^{2} == .(format(r.squaredGLMM(hi.no3.poke.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.no3.poke.lmer)))),
                                bquote(paste("CARI ", R^{2} == .(format(r.squaredGLMM(hi.no3.cari.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.no3.cari.lmer)))),
                                bquote(paste("STRT ", R^{2} == .(format(r.squaredGLMM(hi.no3.strt.lmer)[[1]][1], digits = 2)), " n" == .(nobs(hi.no3.strt.lmer)))),
                     bquote(paste("VAUL ", R^{2} == .(format(r.squaredGLMM(hi.no3.vaul.lmer)[[1]][1], digits = 2)),  " n" == .(nobs(hi.no3.vaul.lmer))))),
                     values = c("#A6761D", "#FF7F00","#3288BD", "#6A3D9A", "#E7298A", "#66C2A5")) +
  geom_vline(xintercept=0, lty=2) + 
  xlab("effect size") +
  xlim(-0.4, 0.5) +
  scale_y_discrete(labels=c(precip.week_z = "ppt 1 week", precip.month_z = "ppt 1 month", Intensity_z = "ppt event intensity", TimeSinceChena = "days since snowmelt")) +
  theme_bw() +
  theme(legend.position = c(0.72, 0.87),
        legend.title = element_blank(),
        legend.text = element_text(size = 18),
        legend.background = element_blank(),
        legend.box.background = element_rect(color = "black", size = 1),
        plot.title = element_text(face = "bold", hjust = 0.5, size =22),
        panel.grid = element_blank(),
        panel.border = element_rect(color = "black", size = 2),
        axis.text = element_text(size = 22),
        axis.title.x = element_text(size = 22),
        plot.margin = margin(0.5,1.5,0.5,0.5, "cm"))

ggsave(multi.coef, path = "plots", file = "FigX_HI_NO3_coef.pdf", width = 11.5, height = 10, units = "in")
```

Plot_no3 <- plot_summs(CARI.no3.model, FRCH.no3.model,
           MOOS.no3.model, POKE.no3.model, STRT.no3.model, 
           VAUL.no3.model, scale = TRUE,
           model.names = c("CARI", "FRCH", "MOOS", "POKE", "STRT", "VAUL"),
           colors = c("#A6761D", "#FF7F00","#3288BD", "#6A3D9A", "#E7298A", "#66C2A5")) #+ 
  #xlim(-0.5, 0.75)

vn = expression(paste(HI*-N*O[3]^"-"))
no3_hi <- Plot_no3 + 
  xlab("") + ylab("") +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 1) +
scale_y_discrete(labels= c("Seasonality", 
                             "Antecedent precipitation\n(1 month)", 
                             "Storm precipitation")) +
  geom_text(data = no3hireg, aes(x = -0.35, y = c(1.7, 1.5, 1.3, 1.1, 0.9, 0.7), color = site.ID, hjust = 0,
           label = paste("R[adj]^2", "==", round(adj.r.squared, 2))), size = 5, 
            show.legend = FALSE,
            parse = TRUE) +
  xlim(-0.375, 0.3) +
  theme_bw() +
  ggtitle(vn) +
  theme(axis.text.x = element_blank(), 
        axis.text.y = element_text(size = 15),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 20),
        legend.position = "none",
        plot.title = element_text(size=20))

ggsave("HI_NO3_ant.pdf",
       path = here("plots", "Publication"),
       width = 6, height = 5)


# ggsave("HI_NO3.pdf",
#        path = here("plots", "Coefficient_Plots", "HI"),
#        width = 7, height = 7)
```

### fDOM ###
``` {r}
# correlation 
fDOM_data <- HI_FI_fDOM[,c("Hyst_index", "site.ID", "StormPrecip", "PrecipWeek", "PrecipMonth", "ThreeMonth", "Intensity", "TimeSinceChena", "pf", "burn", "year")]
#fDOM_data <- na.omit(fDOM_data) # 273 to 273 rows 

HI_FI_fDOM$logHI <- log(abs(HI_FI_fDOM$Hyst_index))

ggpairs(fDOM_data,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A"))
        
ggsave("fDOM_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)
```

```{r}
HI_FI_fDOM_MOOS <- subset(HI_FI_fDOM, site.ID == "MOOS")
HI_FI_fDOM_FRCH <- subset(HI_FI_fDOM, site.ID == "FRCH")
HI_FI_fDOM_CARI <- subset(HI_FI_fDOM, site.ID == "CARI")
HI_FI_fDOM_POKE <- subset(HI_FI_fDOM, site.ID == "POKE")
HI_FI_fDOM_VAUL <- subset(HI_FI_fDOM, site.ID == "VAUL")
HI_FI_fDOM_STRT <- subset(HI_FI_fDOM, site.ID == "STRT")
```

```{r}
ggpairs(HI_FI_fDOM_MOOS,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#A6761D"))
        
ggsave("fDOM_pairs_MOOS.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


MOOS.fdom.model <- lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_fDOM_MOOS)

vif(MOOS.model)
plot(MOOS.model)
summary(MOOS.model)
```

```{r}
ggpairs(HI_FI_fDOM_FRCH,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#FF7F00"))
        
ggsave("fDOM_pairs_FRCH.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


FRCH.fdom.model <- lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_fDOM_FRCH)

vif(FRCH.model)
plot(FRCH.model)
summary(FRCH.model)
```
what does a log transform look like 
###***TKH: this is fine
```{r}
FRCH.model.log <- lm(logHI ~ StormPrecip + PrecipWeek + PrecipMonth + TimeSinceChena, data = HI_FI_fDOM_FRCH)

vif(FRCH.model.log)
plot(FRCH.model.log)

```
THis looks worse, lets stick with the original

```{r}
ggpairs(HI_FI_fDOM_CARI,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#3288BD"))
        
ggsave("fDOM_pairs_CARI.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


CARI.fdom.model <- lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_fDOM_CARI)

vif(CARI.model)
plot(CARI.model)
summary(CARI.model)
```
lets log transform
###***TKH: this is fine
```{r}
CARI.model.log <- lm(logHI ~ StormPrecip + PrecipWeek + PrecipMonth + TimeSinceChena, data = HI_FI_fDOM_CARI)

vif(CARI.model.log)
plot(CARI.model.log)

```
maybe further transform?
```{r}
ggpairs(HI_FI_fDOM_POKE,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#6A3D9A"))
        
ggsave("fDOM_pairs_POKE.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


POKE.fdom.model <- lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_fDOM_POKE)

vif(POKE.model)
plot(POKE.model)
summary(POKE.model)
```

```{r}
ggpairs(HI_FI_fDOM_VAUL,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#66C2A5"))
        
ggsave("fDOM_pairs_VAUL.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


VAUL.fdom.model <- lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_fDOM_VAUL)

vif(VAUL.model)
plot(VAUL.model)
summary(VAUL.model)
```
Vifs may be a little high for precipweek 
###***TKH: 2 is a good rule of thumb
```{r}
ggpairs(HI_FI_fDOM_STRT,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#E7298A"))
        
ggsave("fDOM_pairs_VAUL.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


STRT.fdom.model <- lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_fDOM_STRT)

vif(STRT.model)
plot(STRT.model)
summary(STRT.model)
```
###***TKH: ppt week &  month too strongly correlated
```{r}
fdomhireg <- AMC %>% filter(response_var == "fDOM") %>%
                      group_by(site.ID) %>%
                      do(glance(lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, .)))

Plot_fDOM <- plot_summs(CARI.fdom.model, FRCH.fdom.model, MOOS.fdom.model, 
           POKE.fdom.model, STRT.fdom.model, 
           VAUL.fdom.model, scale = TRUE,
           model.names = c("CARI", "FRCH", "MOOS", "POKE", "STRT", "VAUL"),
           colors = c("#A6761D", "#FF7F00","#3288BD", "#6A3D9A", "#E7298A", "#66C2A5")) +
  theme(aspect.ratio = 1) #+ 
  #xlim(-0.3, 0.6)
  
fDOM_hi <- Plot_fDOM + 
  xlab("") + ylab("") +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 1) +
scale_y_discrete(labels= c("Seasonality", 
                             "Antecedent precipitation\n(1 month)", 
                             "Storm precipitation")) +
  geom_text(data = fdomhireg, aes(x = -0.35, y = c(3.25, 3.05, 2.85, 2.65, 2.45, 2.25), color = site.ID, hjust = 0,
           label = paste("R[adj]^2", "==", round(adj.r.squared, 2))), size = 5, 
            show.legend = FALSE,
            parse = TRUE) +
  xlim(-0.375, 0.3) +
  xlab("coefficient") +
  theme_bw() +
  ggtitle("HI-fDOM") +
  theme(axis.text.x=element_text(size=15), 
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.position = "none",
        plot.title = element_text(size=20))

ggsave("HI_fDOM_ant.pdf",
       path = here("plots", "Publication"),
       width = 6, height = 5)


```

### SPC ###
``` {r}
# correlation 
SPC_data <- HI_FI_SPC[,c("Hyst_index", "site.ID", "StormPrecip", "PrecipWeek", "PrecipMonth", "ThreeMonth", "Intensity", "TimeSinceChena", "pf", "burn", "year")]
SPC_data <- na.omit(SPC_data) # 271 to 268 rows 

HI_FI_SPC$logHI <- log(abs(HI_FI_SPC$Hyst_index))

ggpairs(SPC_data,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A"))
        
ggsave("SPC_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)
```

```{r}
HI_FI_SPC_MOOS <- subset(HI_FI_SPC, site.ID == "MOOS")
HI_FI_SPC_FRCH <- subset(HI_FI_SPC, site.ID == "FRCH")
HI_FI_SPC_CARI <- subset(HI_FI_SPC, site.ID == "CARI")
HI_FI_SPC_POKE <- subset(HI_FI_SPC, site.ID == "POKE")
HI_FI_SPC_VAUL <- subset(HI_FI_SPC, site.ID == "VAUL")
HI_FI_SPC_STRT <- subset(HI_FI_SPC, site.ID == "STRT")
```

```{r}
ggpairs(HI_FI_SPC_MOOS,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#A6761D"))
        
ggsave("SPC_pairs_MOOS.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


MOOS.spc.model <- lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_SPC_MOOS)

vif(MOOS.model)
plot(MOOS.model)
summary(MOOS.model)
```

```{r}
ggpairs(HI_FI_SPC_FRCH,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#FF7F00"))
        
ggsave("SPC_pairs_FRCH.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


FRCH.spc.model <- lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_SPC_FRCH)

vif(FRCH.model)
plot(FRCH.model)
summary(FRCH.model)
```

```{r}
ggpairs(HI_FI_SPC_CARI,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#3288BD"))
        
ggsave("SPC_pairs_CARI.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


CARI.spc.model <- lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_SPC_CARI)

vif(CARI.model)
plot(CARI.model)
summary(CARI.model)
```

```{r}
ggpairs(HI_FI_SPC_POKE,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#6A3D9A"))
        
ggsave("SPC_pairs_POKE.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


POKE.spc.model <- lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_SPC_POKE)

vif(POKE.model)
plot(POKE.model)
summary(POKE.model)
```
lets log transform 

```{r}
POKE.model.log <- lm(logHI ~ StormPrecip + PrecipWeek + PrecipMonth + TimeSinceChena, data = HI_FI_SPC_POKE)

vif(POKE.model.log)
plot(POKE.model.log)

```
mostly works except one point 

```{r}
ggpairs(HI_FI_SPC_VAUL,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#E7298A"))
        
ggsave("SPC_pairs_VAUL.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


VAUL.spc.model <- lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_SPC_VAUL)

vif(VAUL.model)
plot(VAUL.model)
summary(VAUL.model)

```
Lets log transform 

```{r}
VAUL.model.log <- lm(logHI ~ StormPrecip + PrecipWeek + PrecipMonth + TimeSinceChena, data = HI_FI_SPC_VAUL)

vif(VAUL.model.log)
plot(VAUL.model.log)


```

```{r}
ggpairs(HI_FI_SPC_STRT,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#66C2A5"))
        
ggsave("SPC_pairs_VAUL.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


STRT.spc.model <- lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_SPC_STRT)

vif(STRT.model)
plot(STRT.model)
summary(STRT.model)

```

```{r}
spchireg <- AMC %>% filter(response_var == "SPC") %>%
                      group_by(site.ID) %>%
                      do(glance(lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, .)))

Plot_spc <- plot_summs(CARI.spc.model, FRCH.spc.model, MOOS.spc.model, 
           POKE.spc.model, STRT.spc.model, 
           VAUL.spc.model, scale = TRUE,
           model.names = c("CARI", "FRCH", "MOOS", "POKE", "STRT", "VAUL"),
           colors = c("#A6761D", "#FF7F00","#3288BD", "#6A3D9A", "#E7298A", "#66C2A5"))+
  theme(aspect.ratio = 1) #+
 # xlim(-0.45, 0.7)

SPC_hi <- Plot_spc + 
  xlab("Coefficient estimate") + ylab("") +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 1) +
  scale_y_discrete(labels= c("Seasonality", 
                             "Antecedent precipitation\n(1 month)", 
                             "Storm precipitation")) +
  geom_text(data = spchireg, aes(x = -0.35, y = c(1.7, 1.5, 1.3, 1.1, 0.9, 0.7), color = site.ID, hjust = 0,
            label = paste("R[adj]^2", "==", round(adj.r.squared, 2))), 
            size = 5, 
            show.legend = FALSE,
            parse = TRUE) +
  xlim(-0.375, 0.3) +
  theme_bw() +
  ggtitle("HI-SPC") +
  theme(axis.text.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = c(0.15, 0.85),
        legend.background = element_rect(fill = NA, color = NA),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        plot.title = element_text(size = 20))
  
ggsave("HI_SPC_ant.pdf",
       path = here("plots", "Publication"),
       width = 6, height = 5)

#ggsave("HI_SPC.pdf",
#       path = here("plots", "Coefficient_Plots", "HI"),
#       width = 7, height = 7)
```

### turb ###
``` {r}
# correlation 
turb_data <- HI_FI_turb[,c("Hyst_index", "site.ID", "StormPrecip", "PrecipWeek", "PrecipMonth", "ThreeMonth", "Intensity", "TimeSinceChena", "pf", "burn", "year")]
turb_data <- na.omit(turb_data) # 276 to 273 rows 

HI_FI_turb$logHI <- log(abs(HI_FI_turb$Hyst_index))

ggpairs(turb_data,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A"))
        
ggsave("turb_pairs.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)
```

```{r}
HI_FI_turb_MOOS <- subset(HI_FI_turb, site.ID == "MOOS")
HI_FI_turb_FRCH <- subset(HI_FI_turb, site.ID == "FRCH")
HI_FI_turb_CARI <- subset(HI_FI_turb, site.ID == "CARI")
HI_FI_turb_POKE <- subset(HI_FI_turb, site.ID == "POKE")
HI_FI_turb_VAUL <- subset(HI_FI_turb, site.ID == "VAUL")
HI_FI_turb_STRT <- subset(HI_FI_turb, site.ID == "STRT")
```

```{r}
ggpairs(HI_FI_turb_MOOS,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#A6761D"))
        
ggsave("turb_pairs_MOOS.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


MOOS.turb.model <- lm(Hyst_index ~ StormPrecip + PrecipMonth +  TimeSinceChena, data = HI_FI_turb_MOOS)

vif(MOOS.model)
plot(MOOS.model)
summary(MOOS.model)
```
lets log transform 

```{r}
MOOS.model.log <- lm(logHI ~ StormPrecip + PrecipWeek + PrecipMonth + TimeSinceChena, data = HI_FI_turb_MOOS)

vif(MOOS.model.log)
plot(MOOS.model.log)
summary(MOOS.model.log)
```


```{r}
ggpairs(HI_FI_turb_FRCH,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#FF7F00"))
        
ggsave("turb_pairs_FRCH.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


FRCH.turb.model <- lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_turb_FRCH)

vif(FRCH.model)
plot(FRCH.model)
summary(FRCH.model)
```

```{r}
ggpairs(HI_FI_turb_CARI,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#3288BD"))
        
ggsave("turb_pairs_CARI.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


CARI.turb.model <- lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_turb_CARI)

vif(CARI.model)
plot(CARI.model)
summary(CARI.model)
```

```{r}
ggpairs(HI_FI_turb_POKE,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#6A3D9A"))
        
ggsave("turb_pairs_POKE.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


POKE.turb.model <- lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_turb_POKE)

vif(POKE.model)
plot(POKE.model)
summary(POKE.model)
```

```{r}
ggpairs(HI_FI_turb_VAUL,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#E7298A"))
        
ggsave("turb_pairs_VAUL.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


VAUL.turb.model <- lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_turb_VAUL)

vif(VAUL.model)
plot(VAUL.model)
summary(VAUL.model)
```

```{r}
ggpairs(HI_FI_turb_STRT,
        columns = c("Hyst_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#66C2A5"))
        
ggsave("turb_pairs_VAUL.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


STRT.turb.model <- lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_turb_STRT)

vif(STRT.model)
plot(STRT.model)
summary(STRT.model)
```
lets log transform 
###***TKH: this is fine
```{r}
STRT.model.log <- lm(logHI ~ StormPrecip + PrecipWeek + PrecipMonth + TimeSinceChena, data = HI_FI_turb_STRT)

vif(STRT.model.log)
plot(STRT.model.log)

```
may need further transformation 


```{r}
turbhireg <- AMC %>% filter(response_var == "turb") %>%
                      group_by(site.ID) %>%
                      do(glance(lm(Hyst_index ~ StormPrecip + PrecipMonth + TimeSinceChena, .)))

Plot_turb <- plot_summs(CARI.turb.model, FRCH.turb.model, MOOS.turb.model, 
           POKE.turb.model, STRT.turb.model, 
           VAUL.turb.model, scale = TRUE,
           model.names = c("CARI", "FRCH", "MOOS", "POKE", "STRT", "VAUL"),
           colors = c("#A6761D", "#FF7F00","#3288BD", "#6A3D9A", "#E7298A", "#66C2A5")) +
  theme(aspect.ratio = 1) #+
  #xlim(-0.15, 0.3)

turb_hi <- Plot_turb + 
           geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 1) +
  xlab("Coefficient estimate") + ylab("") +
  scale_y_discrete(labels= c("Seasonality", 
                             "Antecedent precipitation\n(1 month)", 
                             "Storm precipitation")) +
  geom_text(data = turbhireg, aes(x = -0.35, y = c(3.25, 3.05, 2.85, 2.65, 2.45, 2.25), color = site.ID, hjust = 0,
           label = paste("R[adj]^2", "==", round(adj.r.squared, 2))), size = 5, 
            show.legend = FALSE,
            parse = TRUE) +
  xlim(-0.375, 0.3) +
  xlab("coefficient") +
  theme_bw() +
  ggtitle("HI-turbidity") +
  theme(axis.text.x=element_text(size=15), 
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.position = "none",
        plot.title = element_text(size = 20))
  

ggsave("HI_turb_ant.pdf",
       path = here("plots", "Publication"),
       width = 6, height = 5)

# ggsave("HI_turb.pdf",
#        path = here("plots", "Coefficient_Plots", "HI"),
#        width = 7, height = 7)
```

```{r}
### HI plots to single fig
gA <- ggplotGrob(no3_hi)
gB <- ggplotGrob(fDOM_hi)
gC <- ggplotGrob(SPC_hi)
gD <- ggplotGrob(turb_hi)

grid::grid.newpage()
grid.draw(cbind(rbind(gA, gB), rbind(gC, gD), size="first"))
fig <- arrangeGrob(cbind(rbind(gA, gB), rbind(gC, gD), size="first"))
ggsave(path = here("plots", "Publication"), file = "HI_ant.pdf", fig, width = 10, height = 11, units = "in")


```
### BETA ###
# NO3 
``` {r}
#### Correlation 
NO3_data <- HI_FI_NO3[,c("Beta_index", "site.ID", "StormPrecip", "PrecipWeek", "PrecipMonth", "ThreeMonth", "Intensity", "TimeSinceChena", "pf", "burn", "year")]
NO3_data <- na.omit(NO3_data) # 267 to 247 rows 

HI_FI_NO3$logBETA <- log(abs(HI_FI_NO3$Beta_index))

ggpairs(NO3_data,
        columns = c("Beta_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A"))
        
ggsave("NO3_pairs_BETA.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)
```

1) StormTemp is heavily correlated with TempWeek leading up to a storm (0.778) but TempWeek is slightly more correlated with HI (-.05 to -.03)

2) StormTemp is also correlated with time since chena (-0.735) but time since chena is more correlated with HI (0.251 vs. -0.173) so this makes me want to keep Time since Chena and temperature a week before considering that is a more marginal comparison with HI and the temperature predictors. 

3)Precip week is correlated with precip month (0.511) but precip week is more correlated with HI than precip month (-0.242 vs. 0.048)

4)Precip month is correlated with three month precip (0.591) but three month precip is more correlated with HI (0.220 vs. 0.048)

5) Three month is correlated with Time since Chena (0.619) but time since chena is more correlated with HI (0.251 vs. 0.220)

* to sum up this makes me want to drop storm temperature and three month precipitation.....but lets run the model with all of the candidate predictors first and go from there 


```{r}
HI_FI_NO3_MOOS <- subset(HI_FI_NO3, site.ID == "MOOS")
HI_FI_NO3_FRCH <- subset(HI_FI_NO3, site.ID == "FRCH")
HI_FI_NO3_CARI <- subset(HI_FI_NO3, site.ID == "CARI")
HI_FI_NO3_POKE <- subset(HI_FI_NO3, site.ID == "POKE")
HI_FI_NO3_VAUL <- subset(HI_FI_NO3, site.ID == "VAUL")
HI_FI_NO3_STRT <- subset(HI_FI_NO3, site.ID == "STRT")
```

```{r}
ggpairs(HI_FI_NO3_MOOS,
        columns = c("Beta_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#A6761D"))
        
ggsave("NO3_pairs_BETA_MOOS.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


MOOS.model <- lm(Beta_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_NO3_MOOS)

vif(MOOS.model)
plot(MOOS.model)
summary(MOOS.model)
```

```{r}
ggpairs(HI_FI_NO3_FRCH,
        columns = c("Beta_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#FF7F00"))
        
ggsave("NO3_pairs_BETA_FRCH.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)

FRCH.model <- lm(Beta_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_NO3_FRCH)

vif(FRCH.model)
plot(FRCH.model)
summary(FRCH.model)
```

```{r}
ggpairs(HI_FI_NO3_CARI,
        columns = c("Beta_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#3288BD"))
        
ggsave("NO3_pairs_BETA_CARI.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)

CARI.model <- lm(Beta_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_NO3_CARI)

vif(CARI.model)
plot(CARI.model)
summary(CARI.model)

```

```{r}
ggpairs(HI_FI_NO3_POKE,
        columns = c("Beta_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#6A3D9A"))
        
ggsave("NO3_pairs_BETA_POKE.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)

POKE.model <- lm(Beta_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_NO3_POKE)

vif(POKE.model)
plot(POKE.model)
summary(POKE.model)
```

```{r}
ggpairs(HI_FI_NO3_VAUL,
        columns = c("Beta_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#66C2A5"))
        
ggsave("NO3_pairs_BETA_VAUL.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


VAUL.model <- lm(Beta_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_NO3_VAUL)

vif(VAUL.model)
plot(VAUL.model)
summary(VAUL.model)

```

```{r}
ggpairs(HI_FI_NO3_STRT,
        columns = c("Beta_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#E7298A"))
        
ggsave("NO3_pairs_BETA_VAUL.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


STRT.model <- lm(Beta_index ~ StormPrecip + PrecipMonth + TimeSinceChena, data = HI_FI_NO3_STRT)

vif(STRT.model)
plot(STRT.model)
summary(STRT.model)

```
let me log transform

```{r}
STRT.model.log <- lm(logBETA ~ StormPrecip + PrecipWeek + PrecipMonth + TimeSinceChena, data = HI_FI_NO3_STRT)

vif(STRT.model.log)
plot(STRT.model.log)

```



```{r}
Plot_1 <- plot_summs(MOOS.model, FRCH.model, 
           CARI.model, POKE.model, 
           VAUL.model, STRT.model, 
           scale = TRUE,
           model.names = c("MOOS", "FRCH", "CARI", "POKE", "VAUL", "STRT"),
           colors = c("#A6761D", "#FF7F00","#3288BD", "#6A3D9A", "#E7298A", "#66C2A5")) 

vn = expression(paste(ß*-N*O[3]^"-"))
no3_beta <- Plot_1 + 
  xlab("") + ylab("") +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 1) +
scale_y_discrete(labels= c("Seasonality", 
                             "Precipitation Month", 
                             "Precipitation Week",
                             "Storm Precipitation")) +
  theme_bw() +
   ggtitle(vn) +
theme(axis.text.x=element_text(size=15), 
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.position = "none",
        plot.title = element_text(size = 20))
 
ggsave("BETA_NO3_AMC.pdf",
       path = here("plots", "Publication"),
       width = 7, height = 7)

# ggsave("BETA_NO3.pdf",
#        path = here("plots", "Coefficient_Plots", "HI"),
#        width = 7, height = 7)


```

### fDOM ###
``` {r}
# correlation 
fDOM_data <- HI_FI_fDOM[,c("Beta_index", "site.ID", "StormPrecip", "PrecipWeek", "PrecipMonth", "ThreeMonth", "Intensity", "TimeSinceChena", "pf", "burn", "year")]
fDOM_data <- na.omit(fDOM_data) # 273 to 264 rows 

HI_FI_fDOM$logBETA <- log(abs(HI_FI_fDOM$Beta_index))

ggpairs(fDOM_data,
        columns = c("Beta_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A"))
        
ggsave("fDOM_pairs_BETA.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)
```

```{r}
HI_FI_fDOM_MOOS <- subset(HI_FI_fDOM, site.ID == "MOOS")
HI_FI_fDOM_FRCH <- subset(HI_FI_fDOM, site.ID == "FRCH")
HI_FI_fDOM_CARI <- subset(HI_FI_fDOM, site.ID == "CARI")
HI_FI_fDOM_POKE <- subset(HI_FI_fDOM, site.ID == "POKE")
HI_FI_fDOM_VAUL <- subset(HI_FI_fDOM, site.ID == "VAUL")
HI_FI_fDOM_STRT <- subset(HI_FI_fDOM, site.ID == "STRT")
```

```{r}
ggpairs(HI_FI_fDOM_MOOS,
        columns = c("Beta_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#A6761D"))
        
ggsave("fDOM_pairs_BETA_MOOS.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


MOOS.model <- lm(Beta_index ~ StormPrecip + PrecipWeek + PrecipMonth + TimeSinceChena, data = HI_FI_fDOM_MOOS)

vif(MOOS.model)
plot(MOOS.model)
summary(MOOS.model)
```

```{r}
ggpairs(HI_FI_fDOM_FRCH,
        columns = c("Beta_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#FF7F00"))
        
ggsave("fDOM_pairs_BETA_FRCH.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)

HI_FI_fDOM_FRCH <- HI_FI_fDOM_FRCH[-c(25,30), ]

FRCH.model <- lm(Beta_index ~ StormPrecip + PrecipWeek + PrecipMonth + TimeSinceChena, data = HI_FI_fDOM_FRCH)

vif(FRCH.model)
plot(FRCH.model)
summary(FRCH.model)
```

```{r}
ggpairs(HI_FI_fDOM_CARI,
        columns = c("Beta_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#3288BD"))
        
ggsave("fDOM_pairs_BETA_CARI.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


CARI.model <- lm(Beta_index ~ StormPrecip + PrecipWeek + PrecipMonth + TimeSinceChena, data = HI_FI_fDOM_CARI)

vif(CARI.model)
plot(CARI.model)
summary(CARI.model)
```

```{r}
ggpairs(HI_FI_fDOM_POKE,
        columns = c("Beta_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#6A3D9A"))
        
ggsave("fDOM_pairs_BETA_POKE.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)

HI_FI_fDOM_POKE <- HI_FI_fDOM_POKE[-c(12,32),]

POKE.model <- lm(Beta_index ~ StormPrecip + PrecipWeek + PrecipMonth + TimeSinceChena, data = HI_FI_fDOM_POKE)

vif(POKE.model)
plot(POKE.model)
summary(POKE.model)
```

```{r}
ggpairs(HI_FI_fDOM_VAUL,
        columns = c("Beta_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#66C2A5"))
        
ggsave("fDOM_pairs_BETA_VAUL.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)

HI_FI_fDOM_VAUL <- HI_FI_fDOM_VAUL[-c(4),]


VAUL.model <- lm(Beta_index ~ StormPrecip + PrecipWeek + PrecipMonth + TimeSinceChena, data = HI_FI_fDOM_VAUL)

vif(VAUL.model)
plot(VAUL.model)
summary(VAUL.model)
```

```{r}
ggpairs(HI_FI_fDOM_STRT,
        columns = c("Beta_index", "StormPrecip", "PrecipWeek", "PrecipMonth","ThreeMonth", "Intensity", "TimeSinceChena"),
        ggplot2::aes(color = site.ID))+
  scale_color_manual(values = c("#E7298A"))
        
ggsave("fDOM_pairs_BETA_VAUL.pdf",
       path = here("Output_from_analysis", "09_Antecedent_Conditions_models", "plots"),
       width = 10, height = 10)


STRT.model <- lm(Beta_index ~ StormPrecip + PrecipWeek + PrecipMonth + TimeSinceChena, data = HI_FI_fDOM_STRT)

vif(STRT.model)
plot(STRT.model)
summary(STRT.model)
```

```{r}
Plot_1 <- plot_summs(MOOS.model, FRCH.model, 
           CARI.model, POKE.model, 
           VAUL.model, STRT.model, scale = TRUE,
           model.names = c("MOOS", "FRCH", "CARI", "POKE", "VAUL", "STRT"),
           colors = c("#A6761D", "#FF7F00","#3288BD", "#6A3D9A", "#E7298A", "#66C2A5")) 

fDOM_beta <- Plot_1 + 
  xlab("") + ylab("") +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 1) +
  theme_bw() +
   ggtitle("ß-fDOM") +
theme(axis.text.x=element_text(size=15), 
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.position = "none",
      plot.title = element_text(size = 20)) 

ggsave("BETA_fDOM_AMC.pdf",
       path = here("plots", "Publication"),
       width = 7, height = 7)
 

# ggsave("BETA_fDOM.pdf",
#        path = here("plots", "Coefficient_Plots", "HI"),
#        width = 7, height = 7)
```





```{r}
Plot_1 <- plot_summs(MOOS.model, FRCH.model, 
           CARI.model, POKE.model, 
           VAUL.model, STRT.model, scale = TRUE,
           model.names = c("MOOS", "FRCH", "CARI", "POKE", "VAUL", "STRT"),
           colors = c("#A6761D", "#FF7F00","#3288BD", "#6A3D9A", "#E7298A", "#66C2A5")) 

turb_beta <- Plot_1 + 
  xlab("Coefficient estimate") + ylab("") +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 1) +
  theme_bw() +
  ggtitle("ß-turbidity") +
  theme(axis.text.x=element_text(size=15), 
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.position = "none", 
        plot.title = element_text(size = 20))

ggsave("BETA_turb_AMC.pdf",
       path = here("plots", "Publication"),
       width = 7, height = 7)
  

# ggsave("BETA_turb.pdf",
#        path = here("plots", "Coefficient_Plots", "HI"),
#        width = 7, height = 7)
```


# plots for thesis # 
```{r}
library(ggpubr)
ggarrange(fDOM_hi,no3_hi,
          SPC_hi, turb_hi,
          ncol = 2, nrow = 2,
          common.legend = TRUE,
          labels = c("A)", "B)",
                     "C)", "D)"),
          legend = "bottom",
          align = "hv")


ggsave("HIs_AMC.pdf",
       path = here("plots", "Publication"),
       width = 12, height = 12)

ggarrange(fDOM_beta, no3_beta, 
          SPC_beta, turb_beta,
          ncol = 2, nrow = 2,
          common.legend = TRUE,
          labels = c("A)", "B)",
                     "C)", "D)"),
          legend = "bottom",
          align = "hv")

ggsave("BETAs_AMC.pdf",
       path = here("plots", "Publication"),
       width = 12, height = 12)
# 
# ggsave("NO3_fDOM.pdf",
#        path = here("plots", "Coefficient_Plots"),
#        width = 10, height = 10)
# 
# ggarrange(spc_hi, turb_hi,
#           spc_beta, turb_beta,
#           ncol = 2, nrow = 2,
#           common.legend = TRUE,
#           labels = c("A)", "B)",
#                      "C)", "D)"),
#           legend = "bottom")
# 
# ggsave("SPC_turb.pdf",
#        path = here("plots", "Coefficient_Plots"),
#        width = 10, height = 10)
# 
# # annotate_figure(a, 
# #                 top =                         "Column 1 Title,                                                                            Column 2 Title")

```



