---
title: "11_HI_anova_models"
author: "Jake Cavaiani"
date: "9/13/2022"
output:
  word_document: default
  html_document: default
---
The purpose of this script is to compare if HI/BETA for each constituent varied between sites using linear mixed effects models

Input: Antecedent moisture conditions with HI_FI_BETA and catchment characteristics!

Step 1) import full file 
Step 2) Model for each constituent:

mod <- lmer(meanHI ~ site.ID + (1|year), data = HI_FI_NO3)

Step 3) Check model assumptions 
Step 4) Post-hoc analysis - pairwise comparison if there is significance among site
Step 5) Plot!

Output: boxplots with letters signifying difference 

#load libraries 
```{r}
library(here)
library(tidyverse)
library(nlme)
library(forecast)
library(stats)
library(readr)
library(ggplot2)
library(plotly)
library(GGally)
library(ggpmisc)
library(ggpubr)
library(ggExtra)
library(lubridate)
library(lme4)
# library(MuMIn)
library(multcomp)
library(ggpattern)
library(emmeans)
library(multcompView)

```

# load in the data 
```{r}
AMC <- read.csv(here("Output_from_analysis", "07_Combine_HI_BETA_FI", "antecedent_HI_FI_AllYears.csv"))

AMC <- AMC[c("Hyst_index","site.ID", "storm.ID", "response_var", "Flush_index", "month.y", "day.y", "year", "Beta_index", "doy", "burn", "pf", "date")] # selecting the columns that I want

colNames <- c("Hyst_index", "site.ID", "storm.ID", "response_var", "Flush_index", "month", "day", "year", "Beta_index", "doy", "burn", "pf", "date")

names(AMC)<- colNames # renaming columns 

AMC <- AMC %>% 
  group_by(site.ID, response_var, year) %>% 
  dplyr::summarise(meanHI = mean(Hyst_index, na.rm = TRUE),
                   meanBETA = mean(Beta_index, na.rm = TRUE),
                   sdHI = sd(Hyst_index, na.rm = TRUE),
                   sdBETA = sd(Beta_index, na.rm = TRUE),
                   CVhi = sdHI/meanHI,
                   CVbeta = sdBETA/meanBETA,
                   response_var = paste(response_var),
                   Date = as.Date(date),
                   DOY = as.numeric(doy),
                   burn = paste(burn),
                   PF = paste(pf))

AMC <- AMC[!duplicated(AMC$meanHI), ] # removing duplicated rows 

AMC$year <- as.character(AMC$year)


AMC <- AMC %>% 
  mutate(across(c(burn),
                ~ifelse(site.ID == "CARI" | site.ID == "FRCH" | site.ID == "VAUL", "unburned", "burned")))

AMC <- AMC %>% 
  mutate(across(c(PF),
                ~ifelse(site.ID == "VAUL" | site.ID == "STRT", "High", "Moderate")))


##subsetting by solute 
# NO3 #
HI_FI_NO3 = subset(AMC, response_var == "NO3")
# fDOM #
HI_FI_fDOM = subset(AMC, response_var == "fDOM")
# SPC #
HI_FI_SPC = subset(AMC, response_var == "SPC")
# turb #
HI_FI_turb = subset(AMC, response_var == "turb")


```


# plot 
```{r}
AMC_new <- AMC # reordering the sites to group by burn categorization 
AMC_new$site.ID <- factor(AMC_new$site.ID,     # Reorder factor levels
                         c("CARI", "FRCH", "VAUL", "MOOS", "POKE", "STRT"))

vn = expression(paste(N*O[3]^"-"))

supp.labs <- c("fDOM","NO3-", "SPC", "Turbidity")
names(supp.labs) <- c("fDOM", "NO3", "SPC", "turb")

AMC_new <- AMC_new %>% 
  filter(response_var != "abs")# removing absorbance for now

AMC_new$facets = factor(AMC_new$response_var, labels = c(
    "fDOM",
    "NO3~^{-})",
    "SPC", 
    "Turbidity"))

my_labeller <- as_labeller(c(fDOM="fDOM", NO3="NO[3]", SPC="SPC", turb = "Turbidity"),
                           default = label_parsed)

ggplot(AMC_new, aes(x = site.ID, y = meanHI, pattern = PF, fill = site.ID)) +
  geom_hline(yintercept= 0, linetype="dashed", color = "red")+
  geom_boxplot() +
  geom_boxplot_pattern(position = position_dodge(preserve = "single"), color = "black", pattern_fill = "white", pattern_angle = 45, pattern_density = 0.1, pattern_spacing = 0.025, pattern_key_scale_factor = 0.6) +
  scale_pattern_manual(values = c(High = "stripe", Moderate = "none"), "Permafrost") +
  scale_fill_manual(values=c("#3288BD","#FF7F00", "#E7298A", "#A6761D", "#6A3D9A", "#66C2A5")) +
  xlab("") +
  ylab("Mean HI") +
  theme_classic() +
  facet_wrap(~response_var, labeller = my_labeller) +
  theme(axis.text.x=element_text(size=20, angle = 90, vjust = 0.5, hjust = 1), 
        axis.text.y = element_text(size = 20),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.position = "none",
        strip.text = element_text(size = 20)) 


ggsave("HI_all_solutes.line.pdf",
       path = here("plots", "Storm_metrics_sites"),
       width = 10, height = 10)
```


### HI ###
# HI - NO3
```{r}
# NO3 #
ggplot(HI_FI_NO3, aes(site.ID, meanHI, fill = site.ID)) +
  geom_boxplot() +
  scale_fill_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A")) +
  theme_classic()

ggsave("HI_NO3.pdf",
       path = here("plots", "Storm_metrics_sites"),
       width = 10, height = 10)

NO3.CV.HI.mod <- lmer(meanHI ~ site.ID + (1|year), data = HI_FI_NO3)

plot(NO3.CV.HI.mod)
qqnorm(resid(NO3.CV.HI.mod))
summary(NO3.CV.HI.mod)
anova(NO3.CV.HI.mod)

emmeans(NO3.CV.HI.mod, list(pairwise ~ site.ID), adjust = "tukey")
# add post hoc pairwise comparisons
```

```{r}
# getting the letter designation for significance 
anova <- aov(meanHI ~ site.ID, data = HI_FI_NO3)
summary(anova)

#tukeys test
tukey <- TukeyHSD(anova)
print(tukey)

#cld
cld <- multcompLetters4(anova, tukey)
print(cld)
```
# For HI-NO3, no sig difference between sites (all letters are the same)
 
# HI - fDOM 

```{r fDOM}
#fDOM #
ggplot(HI_FI_fDOM, aes(site.ID, meanHI, fill = site.ID)) +
  geom_boxplot() +
  scale_fill_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A")) +
  theme_classic()

ggsave("HI_fDOM.pdf",
       path = here("plots", "Storm_metrics_sites"),
       width = 10, height = 10)

fDOM.CV.HI.mod <- lmer(meanHI ~ site.ID + (1|year), data = HI_FI_fDOM)

plot(fDOM.CV.HI.mod)
qqnorm(resid(fDOM.CV.HI.mod))
summary(fDOM.CV.HI.mod)

emmeans(fDOM.CV.HI.mod, list(pairwise ~ site.ID), adjust = "tukey")
# add post hoc pairwise comparisons

```



normality looks good 
<!-- CARI:FRCH -->
CARI:VAUL
<!-- FRCH:MOOS -->
FRCH:VAUL
<!-- MOOS:POKE -->
POKE:VAUL
<!-- STRT:VAUL -->

```{r}
# getting the letter designation for significance 
anova <- aov(meanHI ~ site.ID, data = HI_FI_fDOM)
summary(anova)

#tukeys test
tukey <- TukeyHSD(anova)
print(tukey)

#cld
cld <- multcompLetters4(anova, tukey)
print(cld)
```
# For HI-fDOM: VAUL:a, MOOS:ab, STRT:ab, CARI:b, POKE:b, FRCH:b

### ***TKH: naming an object anova is not a good practice, because anova is a defined function in base R. The emmeans approach above at line 192 is the currently accepted way to complete post-hoc comparisons on lmer objects. For this model the letters listed from the cld output are the same result as emmeans because year is not explaining any variation (hence the singluar fit from lmer).

# HI - SPC
```{r}
#SPC #
ggplot(HI_FI_SPC, aes(site.ID, meanHI, fill = site.ID)) +
  geom_boxplot() +
  scale_fill_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A")) +
  theme_classic()

ggsave("HI_SPC.pdf",
       path = here("plots", "Storm_metrics_sites"),
       width = 10, height = 10)

SPC.CV.HI.mod <- lmer(meanHI ~ site.ID + (1|year), data = HI_FI_SPC)

plot(SPC.CV.HI.mod)
qqnorm(resid(SPC.CV.HI.mod))
summary(SPC.CV.HI.mod)
anova(SPC.CV.HI.mod)

emmeans(SPC.CV.HI.mod, list(pairwise ~ site.ID), adjust = "tukey")
# add post hoc pairwise comparisons
```
### ***TKH: model name is CV but response is mean
### ***no post-hoc test needed because the omnibus test isn't significant (F-value < 2)

# For HI-SPC, no sig difference between sites (all letters are the same)
POKE:a
MOOS:a
FRCH:a
VAUL:a
STRT:a
CARI:a


# HI - Turb
```{r}
#turb #
ggplot(HI_FI_turb, aes(site.ID, meanHI, fill = site.ID)) +
  geom_boxplot() +
  scale_fill_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A")) +
  theme_classic()

ggsave("HI_turb.pdf",
       path = here("plots", "Storm_metrics_sites"),
       width = 10, height = 10)

turb.CV.HI.mod <- lmer(meanHI ~ site.ID + (1|year), data = HI_FI_turb)

plot(turb.CV.HI.mod)
qqnorm(resid(turb.CV.HI.mod))
summary(turb.CV.HI.mod)
anova(turb.CV.HI.mod)

emmeans(turb.CV.HI.mod, list(pairwise ~ site.ID), adjust = "tukey")
# add post hoc pairwise comparisons

```

```{r}
# getting the letter designation for significance 
anova <- aov(meanHI ~ site.ID, data = HI_FI_turb)
summary(anova)

#tukeys test
tukey <- TukeyHSD(anova)
print(tukey)

#cld
cld <- multcompLetters4(anova, tukey)
print(cld)
```
# For HI-turb: VAUL:a, MOOS:b, STRT:ab, CARI:ab, POKE:ab, FRCH:ab
VAUL:a
POKE:ab
CARI:ab
STRT:ab
FRCH:ab
MOOS:b

# 12/23/2025 - FIGURE 4 - HI across all storms for fDOM (A), NO3 (B), SPC (C), turbidity (D)
```{r}
# FIGURE 4 TEST ###
# PF extent
# POKE - 25%
# CARI - 29%
# STRT - 30%
# FRCH - 33%
# MOOS - 38%
# VAUL - 58%
desired_order <- c("POKE", "CARI", "STRT", "FRCH", "MOOS", "VAUL")

my_labeller <- as_labeller(c(fDOM="fDOM", NO3="NO[3]", SPC="SPC", turb = "Turbidity"),
                           default = label_parsed)

my_labeller <- as_labeller(c(
  fDOM = "fDOM", 
  NO3 = "Nitrate",  # Subscript 3 and superscript as a minus sign
  SPC = "SPC", 
  turb = "Turbidity"             # Change turb to Turbidity
), default = label_parsed)



annotations <- data.frame(
  response_var = c("fDOM", "fDOM", "fDOM", "fDOM", "fDOM", "fDOM",    
                   "turb", "turb", "turb", "turb", "turb", "turb",
                   "SPC", "SPC"),   
  site.ID = c("VAUL", "MOOS", "STRT", "CARI", "POKE", "FRCH",         
              "VAUL", "MOOS", "STRT", "CARI", "POKE", "FRCH",
              NA, NA),        
  Label = c("a", "ab", "ab", "b", "b", "b",                           
            "a", "b", "ab", "ab", "ab", "ab",
            "Clockwise", "Counterclockwise"),                       
  x_position = c(6, 5, 3, 2, 4, 1,                                   
                 6, 5, 3, 2, 4, 1,
                 1.5,2),                                  
  y_position = c(0.35, 0.35, 0.35, 0.35, 0.35, 0.35,                
                 0.45, 0.45, 0.45, 0.45, 0.45, 0.45,
                 0.1, -0.1)                
)

hi <- ggplot(AMC_new, aes(x = site.ID, y = meanHI, pattern = burn, fill = site.ID)) +
  geom_hline(yintercept= 0, linetype="dashed", color = "red") +
  geom_boxplot(width = .25,
                 outlier.colour = NA,
                 alpha = 0.5) +
   geom_boxplot_pattern(position = position_dodge(preserve = "single"), 
                        width = .5,
                        color = "black", 
                        pattern_fill = "white", 
                        pattern_angle = 45, 
                        pattern_density = 0.1, 
                        pattern_spacing = 0.025, 
                        pattern_key_scale_factor = 0.6) +
  scale_pattern_manual(values = c(burned = "stripe", unburned = "none")) +
  scale_x_discrete(limits = desired_order,
                   labels = c("POKE" = "POKE\n(25%)",
                              "CARI" = "CARI\n(29%)",
                              "STRT" = "STRT\n(30%)",
                              "FRCH" = "FRCH\n(33%)",
                              "MOOS" = "MOOS\n(38%)",
                              "VAUL" = "VAUL\n(58%)")) +
  coord_cartesian(xlim = c(1, 6.05)) + 
  scale_fill_manual(values=c("#3288BD","#FF7F00", "#E7298A", "#A6761D", "#6A3D9A", "#66C2A5"), guide = "none") +
  facet_wrap(~response_var, labeller = my_labeller) +
  geom_text(data = annotations, aes(x = x_position, y = y_position, label = Label), 
            inherit.aes = FALSE, size = 7) + 
  xlab("") +
  ylab("HI") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(size = 16),
        axis.title.y = element_text(size = 25),
        axis.text.y = element_text(size = 20),
        strip.text = element_text(size = 20), 
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 20))
  
ggsave(hi, path = here("plots", "Storm_metrics_sites"),
       file = paste0("Fig4_meanHI_all_annotated_", Sys.Date(), ".pdf"),
       width = 10, height = 8, units = "in")

ggsave(hi, path = here("plots", "Storm_metrics_sites"),
       file = paste0("Fig4_meanHI_all_annotated_", Sys.Date(), ".jpg"),
       width = 10, height = 8, units = "in")

```

### BETA ###

```{r}
ggplot(AMC_new, aes(x = site.ID, y = meanBETA, pattern = PF, fill = site.ID)) +
  geom_hline(yintercept= 0, linetype="dashed", color = "red")+
  geom_boxplot() +
  geom_boxplot_pattern(position = position_dodge(preserve = "single"), color = "black", pattern_fill = "white", pattern_angle = 45, pattern_density = 0.1, pattern_spacing = 0.025, pattern_key_scale_factor = 0.6) +
  scale_pattern_manual(values = c(High = "stripe", Moderate = "none")) +
  scale_fill_manual(values=c("#3288BD","#FF7F00", "#E7298A", "#A6761D", "#6A3D9A", "#66C2A5")) +
  xlab("") +
  ylab("Mean ß") +
  ylim(-1.5,2) +
  theme_classic() +
  facet_wrap(~response_var, labeller = my_labeller) +
  theme(axis.text.x=element_text(size=20, angle = 90, vjust = 0.5, hjust = 1), 
        axis.text.y = element_text(size = 20),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.position = "none",
        strip.text = element_text(size = 20)) 

ggsave("BETA_all_solutes.pdf",
       path = here("plots", "Storm_metrics_sites"),
       width = 10, height = 10)

```

# BETA - NO3
```{r}
#NO3
ggplot(HI_FI_NO3, aes(site.ID, meanBETA, fill = site.ID)) +
  geom_boxplot() +
  facet_wrap(~response_var, scales = "free") +
  scale_fill_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A")) +
  theme_classic()

ggsave("BETA_NO3.pdf",
       path = here("plots", "Storm_metrics_sites"),
       width = 10, height = 10)

NO3.BETA.mod <- lmer(meanBETA ~ site.ID + (1|year), data = HI_FI_NO3)

plot(NO3.BETA.mod)
qqnorm(resid(NO3.BETA.mod))
summary(NO3.BETA.mod)
anova(NO3.BETA.mod)

emmeans(NO3.BETA.mod, list(pairwise ~ site.ID), adjust = "tukey")
# add post hoc pairwise comparisons
```
### ***TKH: note year explains no variance so fit is singular. Nothing significant anyway.

```{r}
summary(NO3.CV.BETA.mod) # nothing is significant 
summary.lm(NO3.CV.BETA.mod)

```
# For BETA-NO3, no sig difference between sites (all letters are the same)


#BETA - fDOM
```{r}
ggplot(HI_FI_fDOM, aes(site.ID, meanBETA, fill = site.ID)) +
  geom_boxplot() +
  scale_fill_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A")) +
  theme_classic()

ggsave("BETA_fDOM.pdf",
       path = here("plots", "Storm_metrics_sites"),
       width = 10, height = 10)

fDOM.BETA.mod <- lmer(meanBETA ~ site.ID + (1|year), data = HI_FI_fDOM)

plot(fDOM.BETA.mod)
qqnorm(resid(fDOM.BETA.mod))
summary(fDOM.BETA.mod)

emmeans(fDOM.BETA.mod, list(pairwise ~ site.ID), adjust = "tukey")
# add post hoc pairwise comparisons

```

```{r}
# getting the letter designation for significance 
anova <- aov(meanBETA ~ site.ID, data = HI_FI_fDOM)
summary(anova)

#tukeys test
tukey <- TukeyHSD(anova)
print(tukey)

#cld
cld <- multcompLetters4(anova, tukey)
print(cld)
```
# For BETA-fDOM: VAUL:b, MOOS:ab, STRT:a, CARI:a, POKE:a, FRCH:a

# BETA - SPC
```{r}
#SPC
ggplot(HI_FI_SPC, aes(site.ID, meanBETA, color = site.ID, shape = as.character(year))) +
  geom_point() +
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A")) +
  theme_classic()

ggsave("BETA_SPC_year.pdf",
       path = here("plots", "Storm_metrics_sites"),
       width = 10, height = 10)

SPC.BETA.mod <- lmer(meanBETA ~ site.ID + (1|year), data = HI_FI_SPC)

plot(SPC.BETA.mod)
qqnorm(resid(SPC.BETA.mod))
summary(SPC.BETA.mod)
anova(SPC.BETA.mod)

emmeans(SPC.BETA.mod, list(pairwise ~ site.ID), adjust = "tukey")
# add post hoc pairwise comparisons

```

```{r}
# getting the letter designation for significance 
anova <- aov(meanBETA ~ site.ID, data = HI_FI_SPC)
summary(anova)

#tukeys test
tukey <- TukeyHSD(anova)
print(tukey)

#cld
cld <- multcompLetters4(anova, tukey)
print(cld)
```
# For BETA-SPC, no sig difference between sites (all letters are the same)

FRCH:a
MOOS:a
STRT:a
POKE:a
CARI:a
VAUL:a

# BETA - TURB 
```{r}
#turb
ggplot(HI_FI_turb, aes(site.ID, meanBETA, fill = site.ID)) +
  geom_boxplot() +
  scale_fill_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A")) +
  theme_classic()

ggsave("BETA_turb.pdf",
       path = here("plots", "Storm_metrics_sites"),
       width = 10, height = 10)

turb.BETA.mod <- lmer(meanBETA ~ site.ID + (1|year), data = HI_FI_turb)

plot(turb.BETA.mod)
qqnorm(resid(turb.BETA.mod))
summary(turb.BETA.mod)
anova(turb.BETA.mod)

emmeans(turb.BETA.mod, list(pairwise ~ site.ID), adjust = "tukey")
```
### ***TKH: note emmeans result differs from the cld below. Use emmeans
# For BETA-turb, CARI: a, VAUL: b, MOOS: b, STRT: b, POKE: a, FRCH: a

CARI:a
VAUL:b
MOOS:b
STRT:b
POKE:a
FRCH:a

# 12/23/2025 - FIGURE 5 - BETA across all storms for fDOM (A), NO3 (B), SPC (C), turbidity (D)
```{r}
# FIGURE 4 TEST ###
# PF extent
# POKE - 25%
# CARI - 29%
# STRT - 30%
# FRCH - 33%
# MOOS - 38%
# VAUL - 58%
desired_order <- c("POKE", "CARI", "STRT", "FRCH", "MOOS", "VAUL")

my_labeller <- as_labeller(c(fDOM="fDOM", NO3="NO[3]", SPC="SPC", turb = "Turbidity"),
                           default = label_parsed)

my_labeller <- as_labeller(c(
  fDOM = "fDOM", 
  NO3 = "Nitrate",  # Subscript 3 and superscript as a minus sign
  SPC = "SPC", 
  turb = "Turbidity"             # Change turb to Turbidity
), default = label_parsed)



annotations <- data.frame(
  response_var = c("fDOM", "fDOM", "fDOM", "fDOM", "fDOM", "fDOM",    
                   "turb", "turb", "turb", "turb", "turb", "turb",
                   "SPC", "SPC"),   
  site.ID = c("VAUL", "MOOS", "STRT", "CARI", "POKE", "FRCH",         
              "VAUL", "MOOS", "STRT", "CARI", "POKE", "FRCH",
              NA, NA),        
  Label = c("b", "ab", "a", "a", "a", "a",                           
            "b", "b", "b", "a", "a", "a",
            "Flushing", "Dilution"),                       
  x_position = c(6, 5, 3, 2, 4, 1,                                   
                 6, 5, 3, 2, 4, 1,
                 1.2,1.2),                                  
  y_position = c(0.2, 0.8, 1.4, 1.4, 1.4, 1.4,                
                 1.2, 1.2, 1.2, 1.2, 1.2, 1.2,
                 0.3, -1.0)                
)

beta <- ggplot(AMC_new, aes(x = site.ID, y = meanBETA, pattern = burn, fill = site.ID)) +
  geom_hline(yintercept= 0, linetype="dashed", color = "red") +
  geom_boxplot(width = .25,
                 outlier.colour = NA,
                 alpha = 0.5) +
   geom_boxplot_pattern(position = position_dodge(preserve = "single"), 
                        width = .5,
                        color = "black", 
                        pattern_fill = "white", 
                        pattern_angle = 45, 
                        pattern_density = 0.1, 
                        pattern_spacing = 0.025, 
                        pattern_key_scale_factor = 0.6) +
  scale_pattern_manual(values = c(burned = "stripe", unburned = "none")) +
  scale_x_discrete(limits = desired_order,
                   labels = c("POKE" = "POKE\n(25%)",
                              "CARI" = "CARI\n(29%)",
                              "STRT" = "STRT\n(30%)",
                              "FRCH" = "FRCH\n(33%)",
                              "MOOS" = "MOOS\n(38%)",
                              "VAUL" = "VAUL\n(58%)")) +
  coord_cartesian(xlim = c(1, 6.05)) + 
  scale_fill_manual(values=c("#3288BD","#FF7F00", "#E7298A", "#A6761D", "#6A3D9A", "#66C2A5"), guide = "none") +
  facet_wrap(~response_var, labeller = my_labeller) +
  geom_text(data = annotations, aes(x = x_position, y = y_position, label = Label), 
            inherit.aes = FALSE, size = 7) + 
  xlab("") +
  ylab("ß") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(size = 16),
        axis.title.y = element_text(size = 25),
        axis.text.y = element_text(size = 20),
        strip.text = element_text(size = 20), 
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 20))
  
ggsave(beta, path = here("plots", "Storm_metrics_sites"),
       file = paste0("Fig5_meanBETA_all_annotated_", Sys.Date(), ".pdf"),
       width = 10, height = 8, units = "in")

ggsave(beta, path = here("plots", "Storm_metrics_sites"),
       file = paste0("Fig5_meanBETA_all_annotated_", Sys.Date(), ".jpg"),
       width = 10, height = 8, units = "in")

```

### SDs of storm metrics ###

```{r}
#plot 
ggplot(AMC_new, aes(x = site.ID, y = sdHI, pattern = PF, fill = site.ID)) +
  geom_boxplot() +
  geom_boxplot_pattern(position = position_dodge(preserve = "single"), color = "black", pattern_fill = "white", pattern_angle = 45, pattern_density = 0.1, pattern_spacing = 0.025, pattern_key_scale_factor = 0.6) +
  scale_pattern_manual(values = c(High = "stripe", Moderate = "none")) +
  scale_fill_manual(values=c("#3288BD","#FF7F00", "#E7298A", "#A6761D", "#6A3D9A", "#66C2A5")) +
  xlab("") +
  ylab("SD HI") +
  theme_classic() +
  facet_wrap(~response_var, labeller = my_labeller) +
  theme(axis.text.x=element_text(size=20, angle = 90, vjust = 0.5, hjust = 1), 
        axis.text.y = element_text(size = 20),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.position = "none",
        strip.text = element_text(size = 20))

ggsave("sdHI_all_solutes.pdf",
       path = here("plots", "Storm_metrics_sites"),
       width = 10, height = 10)


HI_FI_NO3$logSDhi <- log(abs(HI_FI_NO3$sdHI))
HI_FI_fDOM$logSDhi <- log(abs(HI_FI_fDOM$sdHI))
HI_FI_SPC$logSDhi <- log(abs(HI_FI_SPC$sdHI))
HI_FI_turb$logSDhi <- log(abs(HI_FI_turb$sdHI))

HI_FI_NO3$logSDbeta <- log(abs(HI_FI_NO3$sdBETA))
HI_FI_fDOM$logSDbeta <- log(abs(HI_FI_fDOM$sdBETA))
HI_FI_SPC$logSDbeta <- log(abs(HI_FI_SPC$sdBETA))
HI_FI_turb$logSDbeta <- log(abs(HI_FI_turb$sdBETA))

```

# SD HI - NO3 
```{r}
ggplot(HI_FI_NO3, aes(site.ID, sdHI, fill = site.ID)) +
  geom_boxplot() +
  scale_fill_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A")) +
  theme_classic()

ggsave("sdHI_NO3.pdf",
       path = here("plots", "Storm_metrics_sites"),
       width = 10, height = 10)

NO3.sdHI.mod <- lmer(sdHI ~ site.ID + (1|year), data = HI_FI_NO3)

plot(NO3.sdHI.mod)
qqnorm(resid(NO3.sdHI.mod))
summary(NO3.sdHI.mod)
anova(NO3.sdHI.mod)

emmeans(NO3.sdHI.mod, list(pairwise ~ site.ID), adjust = "tukey")
```

```{r}
# getting the letter designation for significance 
anova <- aov(sdHI ~ site.ID, data = HI_FI_NO3)
summary(anova)

#tukeys test
tukey <- TukeyHSD(anova)
print(tukey)

#cld
cld <- multcompLetters4(anova, tukey)
print(cld)
```
# For sdHI-NO3, no sig difference between sites (all letters are the same)

STRT:a
CARI:a
VAUL:a
POKE:a
FRCH:a
MOOS:a

# SD HI - fDOM 
```{r}
ggplot(HI_FI_fDOM, aes(site.ID, sdHI, fill = site.ID)) +
  geom_boxplot() +
  scale_fill_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A")) +
  theme_classic()

ggsave("sdHI_fDOM.pdf",
       path = here("plots", "Storm_metrics_sites"),
       width = 10, height = 10)

fDOM.sdHI.mod <- lmer(sdHI ~ site.ID + (1|year), data = HI_FI_fDOM)

plot(fDOM.sdHI.mod)
qqnorm(resid(fDOM.sdHI.mod))
summary(fDOM.sdHI.mod)
anova(fDOM.sdHI.mod)

emmeans(fDOM.sdHI.mod, list(pairwise ~ site.ID), adjust = "tukey")
```

```{r}
# getting the letter designation for significance 
anova <- aov(sdHI ~ site.ID, data = HI_FI_fDOM)
summary(anova)

#tukeys test
tukey <- TukeyHSD(anova)
print(tukey)

#cld
cld <- multcompLetters4(anova, tukey)
print(cld)
```
# For sdHI-fDOM, MOOS: a, STRT: ab, VAUL: ab, FRCH: ab, POKE: ab, CARI: b

MOOS:a
STRT:ab
VAUL:ab
FRCH:ab
POKE:ab
CARI:b

# SD HI - SPC 
```{r}
ggplot(HI_FI_SPC, aes(site.ID, sdHI, fill = site.ID)) +
  geom_boxplot() +
  scale_fill_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A")) +
  theme_classic()

ggsave("sdHI_SPC.pdf",
       path = here("plots", "Storm_metrics_sites"),
       width = 10, height = 10)

SPC.sdHI.mod <- lmer(sdHI ~ site.ID + (1|year), data = HI_FI_SPC)

plot(SPC.sdHI.mod)
qqnorm(resid(SPC.sdHI.mod))
summary(SPC.sdHI.mod)

emmeans(SPC.sdHI.mod, list(pairwise ~ site.ID), adjust = "tukey")
```

```{r}
# getting the letter designation for significance 
anova <- aov(sdHI ~ site.ID, data = HI_FI_SPC)
summary(anova)

#tukeys test
tukey <- TukeyHSD(anova)
print(tukey)

#cld
cld <- multcompLetters4(anova, tukey)
print(cld)
```
# For sdHI-SPC, no sig difference between sites (all letters are the same)

VAUL:a
FRCH:a
MOOS:a
STRT:a
CARI:a
POKE:a

# SD HI - TURB
```{r}
ggplot(HI_FI_turb, aes(site.ID, sdHI, fill = site.ID)) +
  geom_boxplot() +
  scale_fill_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A")) +
  theme_classic()

ggsave("sdHI_Turb.pdf",
       path = here("plots", "Storm_metrics_sites"),
       width = 10, height = 10)

ggplot(HI_FI_turb, aes(site.ID, sdHI, color = site.ID, shape = as.character(year))) +
  geom_point() +
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A")) +
  theme_classic()

ggsave("sdHI_Turb_year.pdf",
       path = here("plots", "Storm_metrics_sites"),
       width = 10, height = 10)

turb.sdHI.mod <- lmer(sdHI ~ site.ID + (1|year), data = HI_FI_turb)

plot(turb.sdHI.mod)
qqnorm(resid(turb.sdHI.mod))
summary(turb.sdHI.mod)
anova(turb.sdHI.mod)

emmeans(turb.sdHI.mod, list(pairwise ~ site.ID), adjust = "tukey")

```

```{r}
# getting the letter designation for significance 
anova <- aov(sdHI ~ site.ID, data = HI_FI_turb)
summary(anova)

#tukeys test
tukey <- TukeyHSD(anova)
print(tukey)

#cld
cld <- multcompLetters4(anova, tukey)
print(cld)
```
# For sdHI-TURB, no sig difference between sites (all letters are the same)

CARI:a
POKE:a
FRCH:a
VAUL:a
MOOS:a
STRT:a

# 12/23/2025 - FIGURE 6 - sdHI across all storms for fDOM (A), NO3 (B), SPC (C), turbidity (D)
```{r}
# FIGURE 4 TEST ###
# PF extent
# POKE - 25%
# CARI - 29%
# STRT - 30%
# FRCH - 33%
# MOOS - 38%
# VAUL - 58%
desired_order <- c("POKE", "CARI", "STRT", "FRCH", "MOOS", "VAUL")

my_labeller <- as_labeller(c(fDOM="fDOM", NO3="NO[3]", SPC="SPC", turb = "Turbidity"),
                           default = label_parsed)

my_labeller <- as_labeller(c(
  fDOM = "fDOM", 
  NO3 = "Nitrate",  # Subscript 3 and superscript as a minus sign
  SPC = "SPC", 
  turb = "Turbidity"             # Change turb to Turbidity
), default = label_parsed)



annotations <- data.frame(
  response_var = c("fDOM", "fDOM", "fDOM", "fDOM", "fDOM", "fDOM"),   
  site.ID = c("VAUL", "MOOS", "STRT", "CARI", "POKE", "FRCH"),        
  Label = c("ab", "a", "ab", "b", "ab", "ab"),                       
  x_position = c(6, 5, 3, 2, 4, 1),                                  
  y_position = c(0.4, 0.5, 0.6, 0.25, 0.5, 0.35)                
)

sdHI <- ggplot(AMC_new, aes(x = site.ID, y = sdHI, pattern = burn, fill = site.ID)) +
  geom_boxplot(width = .25,
                 outlier.colour = NA,
                 alpha = 0.5) +
   geom_boxplot_pattern(position = position_dodge(preserve = "single"), 
                        width = .5,
                        color = "black", 
                        pattern_fill = "white", 
                        pattern_angle = 45, 
                        pattern_density = 0.1, 
                        pattern_spacing = 0.025, 
                        pattern_key_scale_factor = 0.6) +
  scale_pattern_manual(values = c(burned = "stripe", unburned = "none")) +
  scale_x_discrete(limits = desired_order,
                   labels = c("POKE" = "POKE\n(25%)",
                              "CARI" = "CARI\n(29%)",
                              "STRT" = "STRT\n(30%)",
                              "FRCH" = "FRCH\n(33%)",
                              "MOOS" = "MOOS\n(38%)",
                              "VAUL" = "VAUL\n(58%)")) +
  coord_cartesian(xlim = c(1, 6.05)) + 
  scale_fill_manual(values=c("#3288BD","#FF7F00", "#E7298A", "#A6761D", "#6A3D9A", "#66C2A5"), guide = "none") +
  facet_wrap(~response_var, labeller = my_labeller) +
  geom_text(data = annotations, aes(x = x_position, y = y_position, label = Label), 
            inherit.aes = FALSE, size = 7) + 
  xlab("") +
  ylab("SD-HI") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(size = 16),
        axis.title.y = element_text(size = 25),
        axis.text.y = element_text(size = 20),
        strip.text = element_text(size = 20), 
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 20))
  
ggsave(sdHI, path = here("plots", "Storm_metrics_sites"),
       file = paste0("Fig6_sdHI_all_annotated_", Sys.Date(), ".pdf"),
       width = 10, height = 8, units = "in")

ggsave(sdHI, path = here("plots", "Storm_metrics_sites"),
       file = paste0("Fig6_sdHI_all_annotated_", Sys.Date(), ".jpg"),
       width = 10, height = 8, units = "in")

```

# SD - BETA ### 
```{r}
#plot 
ggplot(AMC_new, aes(x = site.ID, y = sdBETA, pattern = PF, fill = site.ID)) +
  geom_boxplot() +
  geom_boxplot_pattern(position = position_dodge(preserve = "single"), color = "black", pattern_fill = "white", pattern_angle = 45, pattern_density = 0.1, pattern_spacing = 0.025, pattern_key_scale_factor = 0.6) +
  scale_pattern_manual(values = c(High = "stripe", Moderate = "none")) +
  scale_fill_manual(values=c("#3288BD","#FF7F00", "#E7298A", "#A6761D", "#6A3D9A", "#66C2A5")) +
  scale_y_log10() +
  xlab("") +
  ylab("SD ß") +
  theme_classic() +
  facet_wrap(~response_var, labeller = my_labeller) +
  theme(axis.text.x=element_text(size=20, angle = 90, vjust = 0.5, hjust = 1), 
        axis.text.y = element_text(size = 20),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.position = "none",
        strip.text = element_text(size = 20))


ggsave("sdBETA_all_solutes.pdf",
       path = here("plots", "Storm_metrics_sites"),
       width = 10, height = 10)


```

# SD BETA - NO3
```{r}
NO3.sdBETA.mod <- lmer(sdBETA ~ site.ID + (1|year), data = HI_FI_NO3)

plot(NO3.sdBETA.mod)
# variance increases with mean

NO3.logsdBETA.mod <- lmer(log(sdBETA) ~ site.ID + (1|year), data = HI_FI_NO3)

plot(NO3.logsdBETA.mod)
# fixed
qqnorm(resid(NO3.logsdBETA.mod))
summary(NO3.logsdBETA.mod)

emmeans(NO3.sdBETA.mod, list(pairwise ~ site.ID), adjust = "tukey")
```

```{r}
# getting the letter designation for significance 
anova <- aov(sdBETA ~ site.ID, data = HI_FI_NO3)
summary(anova)

#tukeys test
tukey <- TukeyHSD(anova)
print(tukey)

#cld
cld <- multcompLetters4(anova, tukey)
print(cld)
```
# For sdBETA-NO3, no sig difference between sites (all letters are the same)

CARI:a
STRT:a
POKE:a
VAUL:a
FRCH:a
MOOS:a

# SD BETA - fDOM
```{r}
fDOM.sdBETA.mod <- lmer(sdBETA ~ site.ID + (1|year), data = HI_FI_fDOM)

plot(fDOM.sdBETA.mod)
qqnorm(resid(fDOM.sdBETA.mod))
summary(fDOM.sdBETA.mod)

emmeans(fDOM.sdBETA.mod, list(pairwise ~ site.ID), adjust = "tukey")
```

```{r}
# getting the letter designation for significance 
anova <- aov(sdBETA ~ site.ID, data = HI_FI_fDOM)
summary(anova)

#tukeys test
tukey <- TukeyHSD(anova)
print(tukey)

#cld
cld <- multcompLetters4(anova, tukey)
print(cld)
```
# For sdBETA-fDOM, no sig difference between sites (all letters are the same)

MOOS:a
POKE:a
FRCH:a
STRT:a
CARI:a
VAUL:a

# SD BETA - SPC
```{r}
SPC.sdBETA.mod <- lmer(sdBETA ~ site.ID + (1|year), data = HI_FI_SPC)

plot(SPC.sdBETA.mod)
qqnorm(resid(SPC.sdBETA.mod))
summary(SPC.sdBETA.mod)
anova(SPC.sdBETA.mod)

emmeans(SPC.sdBETA.mod, list(pairwise ~ site.ID), adjust = "tukey")
```

```{r}
# getting the letter designation for significance 
anova <- aov(sdBETA ~ site.ID, data = HI_FI_SPC)
summary(anova)

#tukeys test
tukey <- TukeyHSD(anova)
print(tukey)

#cld
cld <- multcompLetters4(anova, tukey)
print(cld)
```
# For sdBETA-SPC, no sig difference between sites (all letters are the same)

VAUL:a
CARI:a
POKE:a
MOOS:a
FRCH:a
STRT:a

# SD BETA - TURB 
```{r}
turb.sdBETA.mod <- lmer(sdBETA ~ site.ID + (1|year), data = HI_FI_turb)

plot(turb.sdBETA.mod)
qqnorm(resid(turb.sdBETA.mod))
summary(turb.sdBETA.mod)
anova(turb.sdBETA.mod)

emmeans(turb.sdBETA.mod, list(pairwise ~ site.ID), adjust = "tukey")
```
### ***TKH: emmeans result differs from cld
# For sdBETA - TURB: CARI: a, POKE: ab, VAUL: ab, STRT: ab, MOOS: ab, FRCH: b
CARI:a
POKE:ab
VAUL:ab
STRT:ab
MOOS:ab
FRCH:b

# 12/23/2025 - FIGURE 7 - sdBETA across all storms for fDOM (A), NO3 (B), SPC (C), turbidity (D)
```{r}
# FIGURE 4 TEST ###
# PF extent
# POKE - 25%
# CARI - 29%
# STRT - 30%
# FRCH - 33%
# MOOS - 38%
# VAUL - 58%
desired_order <- c("POKE", "CARI", "STRT", "FRCH", "MOOS", "VAUL")

my_labeller <- as_labeller(c(fDOM="fDOM", NO3="NO[3]", SPC="SPC", turb = "Turbidity"),
                           default = label_parsed)

my_labeller <- as_labeller(c(
  fDOM = "fDOM", 
  NO3 = "Nitrate",  # Subscript 3 and superscript as a minus sign
  SPC = "SPC", 
  turb = "Turbidity"             # Change turb to Turbidity
), default = label_parsed)



annotations <- data.frame(
  response_var = c("turb", "turb", "turb", "turb", "turb", "turb"),   
  site.ID = c("VAUL", "MOOS", "STRT", "CARI", "POKE", "FRCH"),        
  Label = c("ab", "ab", "ab", "a", "b", "ab"),                       
  x_position = c(6, 5, 3, 2, 4, 1),                                  
  y_position = c(0.25, 0.25, 0.2, 0.35, 0.25, 0.25)                
)

sdBETA <- ggplot(AMC_new, aes(x = site.ID, y = sdHI, pattern = burn, fill = site.ID)) +
  geom_boxplot(width = .25,
                 outlier.colour = NA,
                 alpha = 0.5) +
   geom_boxplot_pattern(position = position_dodge(preserve = "single"), 
                        width = .5,
                        color = "black", 
                        pattern_fill = "white", 
                        pattern_angle = 45, 
                        pattern_density = 0.1, 
                        pattern_spacing = 0.025, 
                        pattern_key_scale_factor = 0.6) +
  scale_pattern_manual(values = c(burned = "stripe", unburned = "none")) +
  scale_x_discrete(limits = desired_order,
                   labels = c("POKE" = "POKE\n(25%)",
                              "CARI" = "CARI\n(29%)",
                              "STRT" = "STRT\n(30%)",
                              "FRCH" = "FRCH\n(33%)",
                              "MOOS" = "MOOS\n(38%)",
                              "VAUL" = "VAUL\n(58%)")) +
  coord_cartesian(xlim = c(1, 6.05)) + 
  scale_fill_manual(values=c("#3288BD","#FF7F00", "#E7298A", "#A6761D", "#6A3D9A", "#66C2A5"), guide = "none") +
  facet_wrap(~response_var, labeller = my_labeller) +
  geom_text(data = annotations, aes(x = x_position, y = y_position, label = Label), 
            inherit.aes = FALSE, size = 7) + 
  xlab("") +
  ylab("SD-ß") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(size = 16),
        axis.title.y = element_text(size = 25),
        axis.text.y = element_text(size = 20),
        strip.text = element_text(size = 20), 
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 20))
  
ggsave(sdBETA, path = here("plots", "Storm_metrics_sites"),
       file = paste0("Fig7_sdBETA_all_annotated_", Sys.Date(), ".pdf"),
       width = 10, height = 8, units = "in")

ggsave(sdBETA, path = here("plots", "Storm_metrics_sites"),
       file = paste0("Fig7_sdBETA_all_annotated_", Sys.Date(), ".jpg"),
       width = 10, height = 8, units = "in")

```


