---
title: "14_Catchment_Characteristics_graveyard"
author: "Jake Cavaiani"
date: "9/26/2022"
output: html_document
---
# NO3
```{r}
HI.no3 <- gls(meanHI ~ Slope + pctburn_lg, 
             data = NO3_data)

vif(HI.no3)

```

#diagnostic plots 
```{r}
plot(HI.no3, resid(., type = "p") ~ fitted(.), abline = 0)

plot(HI.no3, meanHI ~ fitted(.) | site.ID, abline = c(0,1))

qqnorm(HI.no3, abline = c(0,1))

plot(predictorEffects(HI.no3, partial.residuals=TRUE),
partial.residual=list(pch=".", col="#FF00FF80"),
axes=list(x=list(rotate=45)),
rows=1, cols=2)

summary(HI.no3) # no significance/ t-value>2 for burn 
```

# BETA #
```{r}
BETA.no3 <- gls(meanBETA ~ Slope + pctburn_lg, 
             data = NO3_data)

vif(BETA.no3)

```
Vifs pass 
#diagnostic plots 
```{r}
plot(BETA.no3, resid(., type = "p") ~ fitted(.), abline = 0)

plot(BETA.no3, meanBETA ~ fitted(.) | site.ID, abline = c(0,1))

qqnorm(BETA.no3, abline = c(0,1))

plot(predictorEffects(BETA.no3, partial.residuals=TRUE),
partial.residual=list(pch=".", col="#FF00FF80"),
axes=list(x=list(rotate=45)),
rows=1, cols=2)

summary(BETA.no3) # no significance 

```

# SD HI #
```{r}
sdHI.no3 <- gls(sdHI ~ Slope + pctburn_lg, 
             data = NO3_data)

vif(sdHI.no3)

```

#diagnostic plots 
```{r}
plot(sdHI.no3, resid(., type = "p") ~ fitted(.), abline = 0)

plot(sdHI.no3, sdHI ~ fitted(.) | site.ID, abline = c(0,1))

qqnorm(sdHI.no3, abline = c(0,1))


plot(predictorEffects(sdHI.no3, partial.residuals=TRUE),
partial.residual=list(pch=".", col="#FF00FF80"),
axes=list(x=list(rotate=45)),
rows=1, cols=2)

summary(sdHI.no3) # no significance /t va;ue > 2 for slope 
```

# SD BETA #
```{r}
sdBETA.no3 <- gls(sdBETA ~ Slope + pctburn_lg, 
             data = NO3_data)

vif(sdBETA.no3)

```

#diagnostic plots 
```{r}
plot(sdBETA.no3, resid(., type = "p") ~ fitted(.), abline = 0)

plot(sdBETA.no3, sdBETA ~ fitted(.) | site.ID, abline = c(0,1))

qqnorm(sdBETA.no3, abline = c(0,1))

plot(predictorEffects(sdBETA.no3, partial.residuals=TRUE),
partial.residual=list(pch=".", col="#FF00FF80"),
axes=list(x=list(rotate=45)),
rows=1, cols=2)

summary(sdBETA.no3) # no significance 

```



# fDOM
```{r}
HI.fDOM <- gls(meanHI ~ Slope + pctburn_lg, 
             data = fDOM_data)

vif(HI.fDOM)

```

#diagnostic plots 
```{r}
plot(HI.fDOM, resid(., type = "p") ~ fitted(.), abline = 0)

plot(HI.fDOM, meanHI ~ fitted(.) | site.ID, abline = c(0,1))

qqnorm(HI.fDOM, abline = c(0,1))

plot(predictorEffects(HI.fDOM, partial.residuals=TRUE),
partial.residual=list(pch=".", col="#FF00FF80"),
axes=list(x=list(rotate=45)),
rows=1, cols=2)

summary(HI.fDOM) # no significance/ t -values > 2 for slope 

```

# BETA #
```{r}
BETA.fDOM <- gls(meanBETA ~ Slope + pctburn_lg, 
             data = fDOM_data)

vif(BETA.fDOM)

```

#diagnostic plots 
```{r}
plot(BETA.fDOM, resid(., type = "p") ~ fitted(.), abline = 0)

plot(BETA.fDOM, meanBETA ~ fitted(.) | site.ID, abline = c(0,1))

qqnorm(BETA.fDOM, abline = c(0,1))

plot(predictorEffects(BETA.fDOM, partial.residuals=TRUE),
partial.residual=list(pch=".", col="#FF00FF80"),
axes=list(x=list(rotate=45)),
rows=1, cols=2)

summary(BETA.fDOM) # no significance/ t-value > 2 for slope 
```

# SD HI #
```{r}
sdHI.fDOM <- gls(sdHI ~ Slope + pctburn_lg, 
             data = fDOM_data)

vif(sdHI.fDOM)

```

#diagnostic plots 
```{r}
plot(sdHI.fDOM, resid(., type = "p") ~ fitted(.), abline = 0)

plot(sdHI.fDOM, sdHI ~ fitted(.) | site.ID, abline = c(0,1))

qqnorm(sdHI.fDOM, abline = c(0,1))

plot(predictorEffects(sdHI.fDOM, partial.residuals=TRUE),
partial.residual=list(pch=".", col="#FF00FF80"),
axes=list(x=list(rotate=45)),
rows=1, cols=2)

summary(sdHI.fDOM) # no significance

```

# SD BETA #
```{r}
sdBETA.fDOM <- gls(sdBETA ~ Slope + pctburn_lg, 
             data = fDOM_data)

vif(sdBETA.fDOM)

```

#diagnostic plots 
```{r}
plot(sdBETA.fDOM, resid(., type = "p") ~ fitted(.), abline = 0)

plot(sdBETA.fDOM, sdBETA ~ fitted(.) | site.ID, abline = c(0,1))

qqnorm(sdBETA.fDOM, abline = c(0,1))

plot(predictorEffects(sdBETA.fDOM, partial.residuals=TRUE),
partial.residual=list(pch=".", col="#FF00FF80"),
axes=list(x=list(rotate=45)),
rows=1, cols=2)

summary(sdBETA.fDOM) # no significance 

```


# SPC
```{r}
HI.SPC <- gls(meanHI ~ Slope + pctburn_lg, 
             data = SPC_data)

vif(HI.SPC)

```

#diagnostic plots 
```{r}
plot(HI.SPC, resid(., type = "p") ~ fitted(.), abline = 0)

plot(HI.SPC, meanHI ~ fitted(.) | site.ID, abline = c(0,1))

qqnorm(HI.SPC, abline = c(0,1))

plot(predictorEffects(HI.SPC, partial.residuals=TRUE),
partial.residual=list(pch=".", col="#FF00FF80"),
axes=list(x=list(rotate=45)),
rows=1, cols=2)

summary(HI.SPC) # no significance/ t-value > 2 for slope 

```

# BETA #
```{r}
BETA.SPC <- gls(meanBETA ~ Slope + pctburn_lg, 
             data = SPC_data)

vif(BETA.SPC)

```

#diagnostic plots 
```{r}
plot(BETA.SPC, resid(., type = "p") ~ fitted(.), abline = 0)

plot(BETA.SPC, meanBETA ~ fitted(.) | site.ID, abline = c(0,1))

qqnorm(BETA.SPC, abline = c(0,1))

plot(predictorEffects(BETA.SPC, partial.residuals=TRUE),
partial.residual=list(pch=".", col="#FF00FF80"),
axes=list(x=list(rotate=45)),
rows=1, cols=2)

summary(BETA.SPC) # no significance 

```

# SD HI #
```{r}
sdHI.SPC <- gls(sdHI ~ Slope + pctburn_lg, 
             data = SPC_data)

vif(sdHI.SPC)

```

#diagnostic plots 
```{r}
plot(sdHI.SPC, resid(., type = "p") ~ fitted(.), abline = 0)

plot(sdHI.SPC, sdHI ~ fitted(.) | site.ID, abline = c(0,1))

qqnorm(sdHI.SPC, abline = c(0,1))

plot(predictorEffects(sdHI.SPC, partial.residuals=TRUE),
partial.residual=list(pch=".", col="#FF00FF80"),
axes=list(x=list(rotate=45)),
rows=1, cols=2)

summary(sdHI.SPC) # no significance 

```

# SD BETA #
```{r}
sdBETA.SPC <- gls(sdBETA ~ Slope + pctburn_lg, 
             data = SPC_data)

vif(sdBETA.SPC)

```

#diagnostic plots 
```{r}
plot(sdBETA.SPC, resid(., type = "p") ~ fitted(.), abline = 0)

plot(sdBETA.SPC, sdBETA ~ fitted(.) | site.ID, abline = c(0,1))

qqnorm(sdBETA.SPC, abline = c(0,1))

plot(predictorEffects(sdBETA.SPC, partial.residuals=TRUE),
partial.residual=list(pch=".", col="#FF00FF80"),
axes=list(x=list(rotate=45)),
rows=1, cols=2)

summary(sdBETA.SPC) # no significance/ t-value > 2 for burn 

```


# turb
```{r}
HI.turb <- gls(meanHI ~ Slope + pctburn_lg, 
             data = turb_data)

vif(HI.turb)

```

#diagnostic plots 
```{r}
plot(HI.turb, resid(., type = "p") ~ fitted(.), abline = 0)

plot(HI.turb, meanHI ~ fitted(.) | site.ID, abline = c(0,1))

qqnorm(HI.turb, abline = c(0,1))

plot(predictorEffects(HI.turb, partial.residuals=TRUE),
partial.residual=list(pch=".", col="#FF00FF80"),
axes=list(x=list(rotate=45)),
rows=1, cols=2)

summary(HI.turb) # no significancce

```

# BETA #
```{r}
BETA.turb <- gls(meanBETA ~ Slope + pctburn_lg, 
             data = turb_data)

vif(BETA.turb)

```

#diagnostic plots 
```{r}
plot(BETA.turb, resid(., type = "p") ~ fitted(.), abline = 0)

plot(BETA.turb, meanBETA ~ fitted(.) | site.ID, abline = c(0,1))

qqnorm(BETA.turb, abline = c(0,1))

plot(predictorEffects(BETA.turb, partial.residuals=TRUE),
partial.residual=list(pch=".", col="#FF00FF80"),
axes=list(x=list(rotate=45)),
rows=1, cols=2)

summary(BETA.turb) # no significance 

```

# SD HI #
```{r}
sdHI.turb <- gls(sdHI ~ Slope + pctburn_lg, 
             data = turb_data)

vif(sdHI.turb)

```

#diagnostic plots 
```{r}
plot(sdHI.turb, resid(., type = "p") ~ fitted(.), abline = 0)

plot(sdHI.turb, sdHI ~ fitted(.) | site.ID, abline = c(0,1))

qqnorm(sdHI.turb, abline = c(0,1))

plot(predictorEffects(sdHI.turb, partial.residuals=TRUE),
partial.residual=list(pch=".", col="#FF00FF80"),
axes=list(x=list(rotate=45)),
rows=1, cols=2)

summary(sdHI.turb) # no significance 

```

# SD BETA #
```{r}
sdBETA.turb <- gls(sdBETA ~ Slope + pctburn_lg, 
             data = turb_data)

vif(sdBETA.turb)

```

#diagnostic plots 
```{r}
plot(sdBETA.turb, resid(., type = "p") ~ fitted(.), abline = 0)

plot(sdBETA.turb, sdBETA ~ fitted(.) | site.ID, abline = c(0,1))

qqnorm(sdBETA.turb, abline = c(0,1))

plot(predictorEffects(sdBETA.turb, partial.residuals=TRUE),
partial.residual=list(pch=".", col="#FF00FF80"),
axes=list(x=list(rotate=45)),
rows=1, cols=2)

summary(sdBETA.turb) # no significance 

```




































































# HI model - year  
```{r}
HI.no3.year <- lmer(meanHI ~ Slope + pctburn_lg + (1|year), 
             data = NO3_data_year)

vif(HI.no3.year)
```
Vifs are low - all good 

# diagnostic plot 
```{r, echo=FALSE}
plot(HI.no3.year, type=c("p","smooth"), col.line=1)
plot(HI.no3.year,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)
lattice::qqmath(HI.no3.year)

```

```{r}
pr <- ggpredict(HI.no3.year, terms = c("Slope", "pctburn_lg"))

ggplot(pr, aes(x, predicted, colour = group)) +
  geom_point(position = position_dodge(.1)) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(.1)) +
  theme_classic()

tab_model(HI.no3.year) # burn is significant, R^2 is 0.222
summary(HI.no3.year)
ranef(HI.no3.year)

```

# HI model - all years 
```{r}
HI.no3 <- lm(meanHI ~ Slope + pctburn_lg, 
             data = NO3_data)

vif(HI.no3)
plot(HI.no3)
summary(HI.no3)
```

# BETA model- year 
```{r}
BETA.no3.year <- lmer(meanBETA ~ Slope + pctburn_lg + (1|year), 
             data = NO3_data_year) # boundary (singular) fit: see ?isSingular
vif(BETA.no3.year)
ranef(BETA.no3.year)
```


```{r, echo=FALSE}
plot(BETA.no3.year, type=c("p","smooth"), col.line=1)
plot(BETA.no3.year,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)
lattice::qqmath(BETA.no3.year)

```


```{r}
pr <- ggpredict(BETA.no3.year, terms = c("Slope", "pctburn_lg"))

ggplot(pr, aes(x, predicted, colour = group)) +
  geom_point(position = position_dodge(.1)) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(.1)) +
  theme_classic()

tab_model(BETA.no3.year) # burn is significant/R^2 os 0.303
summary(BETA.no3.year) # year is adding NO variance
# burn is significant
```

# BETA model - all years 
```{r}
BETA.no3 <- lm(meanBETA ~ Slope*pctburn_lg, 
             data = NO3_data)
plot(BETA.no3)
```

# sdHI model - year 
```{r}
sdHI.no3.year <- lmer(sdHI ~ Slope+pctburn_lg + (1|year), 
             data = NO3_data_year) #boundary (singular) fit: see ?isSingular
vif(sdHI.no3.year)
ranef(sdHI.no3.year)
```
Vifs pass
```{r, echo=FALSE}
plot(sdHI.no3.year, type=c("p","smooth"), col.line=1)
plot(sdHI.no3.year,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)
lattice::qqmath(sdHI.no3.year)
```

```{r}
pr <- ggpredict(sdHI.no3.year, terms = c("Slope", "pctburn_lg"))

ggplot(pr, aes(x, predicted, colour = group)) +
  geom_point(position = position_dodge(.1)) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(.1)) +
  theme_classic()

tab_model(sdHI.no3.year) # slope is significant/ R^2 is 0.415
summary(sdHI.no3.year)
```

# sdHI model 
```{r}
sdHI.no3 <- lm(sdHI ~ Slope*pctburn_lg, 
             data = NO3_data) 
vif(sdHI.no3)
plot(sdHI.no3)
```

# sdBETA model - year
```{r}
sdBETA.no3.year <- lmer(sdBETA ~ Slope+pctburn_lg + (1|year), 
             data = NO3_data_year) #boundary (singular) fit: see ?isSingular
vif(sdBETA.no3.year) 
ranef(sdBETA.no3.year)
```
Vifs pass 

```{r, echo=FALSE}
plot(sdBETA.no3.year, type=c("p","smooth"), col.line=1)
plot(sdBETA.no3.year,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)
lattice::qqmath(sdBETA.no3.year)
```
residuals dont look great. What if I log transform here

# let me log transform 
```{r}
NO3_data_year$logSDbeta <- log(abs(NO3_data_year$sdBETA))
# 
sdBETA.no3.year.log <- lmer(logSDbeta ~ Slope*pctburn_lg + (1|year), 
             data = NO3_data_year) # boundary (singular) fit: see ?isSingular

 
vif(sdBETA.no3.year.log)

```

```{r, echo=FALSE}
plot(sdBETA.no3.year.log, type=c("p","smooth"), col.line=1)
plot(sdBETA.no3.year.log,
      sqrt(abs(resid(.)))~fitted(.),
      type=c("p","smooth"), col.line=1)
 lattice::qqmath(sdBETA.no3.year.log)
```
This is better but we have two big points for CARI 2020 and POKE 2020 that could be causing this issue...Maybe have to be further transformed 

```{r}
# pr <- ggpredict(sdBETA.no3.year, terms = c("Slope", "pctburn_lg"))
# 
# ggplot(pr, aes(x, predicted, colour = group)) +
#   geom_point(position = position_dodge(.1)) +
#   geom_errorbar(
#     aes(ymin = conf.low, ymax = conf.high),
#     position = position_dodge(.1)) +
#   theme_classic()
# 
# tab_model(sdBETA.no3.year) # noth
```

# sdBETA model 
```{r}
sdBETA.no3 <- lm(sdBETA ~ Slope+pctburn_lg, 
             data = NO3_data) 
plot(sdBETA.no3)
summary(sdBETA.no3) # burn is significant 
```

# fDOM # 
```{r}
fDOM_data_year<- CV_all_year_fDOM[,c("site.ID", "year", "meanHI", "meanBETA", "sdHI", "sdBETA", "Slope", "fireyear_lg", "pctburn_lg", "areaburn_lg", "PF", "NDVI", "CatBurn", "CatPF")]

fDOM_data<- CV_all_fDOM[,c("site.ID", "meanHI", "meanBETA", "sdHI", "sdBETA", "Slope", "fireyear_lg", "pctburn_lg", "areaburn_lg", "PF", "NDVI", "CatBurn", "CatPF")]

ggpairs(fDOM_data_year,
        columns = c("meanHI","Slope", "pctburn_lg", "PF", "NDVI"),
        ggplot2::aes(colour = site.ID)) +
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A"))

ggsave("fDOM_HI_pairs.pdf",
       path = here("Output_from_analysis", "12_Catchment_Characteristics_models", "plots"),
       width = 10, height = 10)

```

```{r}
ggpairs(fDOM_data_year,
        columns = c("meanBETA","Slope", "pctburn_lg", "PF", "NDVI"),
        ggplot2::aes(colour = site.ID)) +
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A"))

ggsave("fDOM_BETA_pairs.pdf",
       path = here("Output_from_analysis", "12_Catchment_Characteristics_models", "plots"),
       width = 10, height = 10)
```

```{r}
ggpairs(fDOM_data_year,
        columns = c("sdHI","Slope", "pctburn_lg", "PF", "NDVI"),
        ggplot2::aes(colour = site.ID)) +
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A"))

ggsave("fDOM_sdHI_pairs.pdf",
       path = here("Output_from_analysis", "12_Catchment_Characteristics_models", "plots"),
       width = 10, height = 10)
```

```{r}
ggpairs(fDOM_data_year,
        columns = c("sdBETA","Slope", "pctburn_lg", "PF", "NDVI"),
        ggplot2::aes(colour = site.ID)) +
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A"))

ggsave("fDOM_sdBETA_pairs.pdf",
       path = here("Output_from_analysis", "12_Catchment_Characteristics_models", "plots"),
       width = 10, height = 10)
```

# HI model - year 
```{r}
HI.fDOM.year <- lmer(meanHI ~ Slope+pctburn_lg + (1|year), 
             data = fDOM_data_year) # boundary (singular) fit: see ?isSingular
vif(HI.fDOM.year)
ranef(HI.fDOM.year)
```

```{r, echo=FALSE}
plot(HI.fDOM.year, type=c("p","smooth"), col.line=1)
plot(HI.fDOM.year,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)
lattice::qqmath(HI.fDOM.year)
```
how would log transform help this?

# HI model - year 
```{r}
fDOM_data_year$logmeanHI <- log(abs(fDOM_data_year$meanHI))
HI.fDOM.year.log <- lmer(logmeanHI ~ Slope*pctburn_lg + (1|year), 
             data = fDOM_data_year) # boundary (singular) fit: see ?isSingular

```

```{r, echo=FALSE}
plot(HI.fDOM.year.log, type=c("p","smooth"), col.line=1)
plot(HI.fDOM.year.log,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)
lattice::qqmath(HI.fDOM.year.log)
```
May need further transformation 

```{r}
pr <- ggpredict(HI.fDOM.year, terms = c("Slope", "pctburn_lg"))

ggplot(pr, aes(x, predicted, colour = group)) +
  geom_point(position = position_dodge(.1)) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(.1)) +
  theme_classic()

tab_model(HI.fDOM.year) # slope is significant/R^2 = 0.525
summary(HI.fDOM.year)
```

# HI model - all years
```{r}
HI.fDOM <- lm(meanHI ~ Slope*pctburn_lg, 
             data = fDOM_data)

plot(HI.fDOM)

```

# BETA model - year 
```{r}
BETA.fDOM.year <- lmer(meanBETA ~ Slope*pctburn_lg + (1|year), 
             data = fDOM_data_year)
vif(BETA.fDOM.year)

```
Vifs pass

```{r, echo=FALSE}
plot(BETA.fDOM.year, type=c("p","smooth"), col.line=1)
plot(BETA.fDOM.year,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)
lattice::qqmath(BETA.fDOM.year)
```
let me log transform to see if its better:


```{r}
# log transform 
fDOM_data_year$logmeanBETA <- log(abs(fDOM_data_year$meanBETA))

BETA.fDOM.year.log <- lmer(logmeanBETA ~ Slope*pctburn_lg + (1|year), 
             data = fDOM_data_year) #boundary (singular) fit: see ?isSingular
vif(BETA.fDOM.year.log)

```


```{r, echo=FALSE}
plot(BETA.fDOM.year.log, type=c("p","smooth"), col.line=1)
plot(BETA.fDOM.year.log,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)
lattice::qqmath(BETA.fDOM.year.log)

summary(BETA.fDOM.year.log)
```
this looks worse TBH... may need further transformation 

```{r}
# pr <- ggpredict(BETA.fDOM.year.log, terms = c("Slope", "pctburn_lg"))
# 
# ggplot(pr, aes(x, predicted, colour = group)) +
#   geom_point(position = position_dodge(.1)) +
#   geom_errorbar(
#     aes(ymin = conf.low, ymax = conf.high),
#     position = position_dodge(.1)) +
#   theme_classic()
# 
# tab_model(BETA.fDOM.year.log)
```


# sdHI model 
```{r}
sdHI.fDOM.year <- lmer(sdHI ~ Slope*pctburn_lg + (1|year), 
             data = fDOM_data_year) # boundary (singular) fit: see ?isSingular
vif(sdHI.fDOM.year)
ranef(sdHI.fDOM.year)

```

```{r, echo=FALSE}
plot(sdHI.fDOM.year, type=c("p","smooth"), col.line=1)
plot(sdHI.fDOM.year,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)
lattice::qqmath(sdHI.fDOM.year)
```
Lets log transform 

```{r}
#log transform 
fDOM_data_year$logSDhi <- log(abs(fDOM_data_year$sdHI))
SDhi.fDOM.year.log <- lmer(logSDhi ~ Slope*pctburn_lg + (1|year), 
              data = fDOM_data_year)
vif(SDhi.fDOM.year.log)

```

```{r, echo=FALSE}
plot(SDhi.fDOM.year.log, type=c("p","smooth"), col.line=1)
plot(SDhi.fDOM.year.log,
      sqrt(abs(resid(.)))~fitted(.),
      type=c("p","smooth"), col.line=1)
lattice::qqmath(SDhi.fDOM.year.log)
```
this looks worse....lets interpret the regular model 

```{r}
pr <- ggpredict(sdHI.fDOM.year, terms = c("Slope", "pctburn_lg"))

ggplot(pr, aes(x, predicted, colour = group)) +
  geom_point(position = position_dodge(.1)) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(.1)) +
  theme_classic()

tab_model(sdHI.fDOM.year) # burn is significant 
```

# sdBETA model - year
```{r}
sdBETA.fDOM.year <- lmer(sdBETA ~ Slope*pctburn_lg + (1|year), 
             data = fDOM_data_year) # boundary (singular) fit: see ?isSingular
vif(sdBETA.fDOM.year)

```

```{r, echo=FALSE}
plot(sdBETA.fDOM.year, type=c("p","smooth"), col.line=1)
plot(sdBETA.fDOM.year,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)
lattice::qqmath(sdBETA.fDOM.year)
```
do i need to transform 

```{r}
# # log transform
# fDOM_data_year$logCVbeta <- log(abs(fDOM_data_year$CVbeta))
# 
# CVbeta.fDOM.year.log <- lmer(logCVbeta ~ CatPF*pctburn_lg + (1|year), 
#              data = fDOM_data_year)
# summary(CVbeta.fDOM.year.log) # year adds 0 variance and nothing is really explaining it here 

```

```{r, echo=FALSE}
# plot(CVbeta.fDOM.year.log, type=c("p","smooth"), col.line=1)
# plot(CVbeta.fDOM.year.log,
#      sqrt(abs(resid(.)))~fitted(.),
#      type=c("p","smooth"), col.line=1)
# lattice::qqmath(CVbeta.fDOM.year.log)
```
This still doesnt look great 

```{r}
pr <- ggpredict(sdBETA.fDOM.year, terms = c("Slope", "pctburn_lg"))

ggplot(pr, aes(x, predicted, colour = group)) +
  geom_point(position = position_dodge(.1)) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(.1)) +
  theme_classic()

tab_model(sdBETA.fDOM.year) # nothing is significant 
```

# sdBETA model
```{r}
sdBETA.fDOM <- lm(sdBETA ~ Slope*pctburn_lg, 
             data = fDOM_data) # boundary (singular) fit: see ?isSingular
vif(sdBETA.fDOM.year)
plot(sdBETA.fDOM)
```

# SPC # 

```{r}
SPC_data_year<- CV_all_year_SPC[,c("site.ID", "year", "meanHI", "meanBETA", "sdHI", "sdBETA", "Slope", "fireyear_lg", "pctburn_lg", "areaburn_lg", "PF", "NDVI", "CatBurn", "CatPF")]

SPC_data<- CV_all_SPC[,c("site.ID", "meanHI", "meanBETA", "sdHI", "sdBETA", "Slope", "fireyear_lg", "pctburn_lg", "areaburn_lg", "PF", "NDVI", "CatBurn", "CatPF")]

ggpairs(SPC_data_year,
        columns = c("meanHI","Slope", "pctburn_lg", "PF", "NDVI"),
        ggplot2::aes(colour = site.ID)) +
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A"))

ggsave("SPC_HI_pairs.pdf",
       path = here("Output_from_analysis", "12_Catchment_Characteristics_models", "plots"),
       width = 10, height = 10)
```

```{r}
ggpairs(SPC_data_year,
        columns = c("meanBETA","Slope", "pctburn_lg", "PF", "NDVI"),
        ggplot2::aes(colour = site.ID)) +
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A"))

ggsave("SPC_BETA_pairs.pdf",
       path = here("Output_from_analysis", "12_Catchment_Characteristics_models", "plots"),
       width = 10, height = 10)

```

```{r}
ggpairs(SPC_data_year,
        columns = c("sdHI","Slope", "pctburn_lg", "PF", "NDVI"),
        ggplot2::aes(colour = site.ID)) +
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A"))

ggsave("SPC_sdHI_pairs.pdf",
       path = here("Output_from_analysis", "12_Catchment_Characteristics_models", "plots"),
       width = 10, height = 10)

```

```{r}
ggpairs(SPC_data_year,
        columns = c("sdBETA","Slope", "pctburn_lg", "PF", "NDVI"),
        ggplot2::aes(colour = site.ID)) +
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A"))

ggsave("SPC_sdBETA_pairs.pdf",
       path = here("Output_from_analysis", "12_Catchment_Characteristics_models", "plots"),
       width = 10, height = 10)

```

# HI model - year 
```{r}
HI.SPC.year <- lmer(meanHI ~ Slope*pctburn_lg + (1|year), 
             data = SPC_data_year)
vif(HI.SPC.year)
```

```{r, echo=FALSE}
plot(HI.SPC.year, type=c("p","smooth"), col.line=1)
plot(HI.SPC.year,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)
lattice::qqmath(HI.SPC.year)
```
looks like we have some outliers here 

```{r}
pr <- ggpredict(HI.SPC.year, terms = c("Slope", "pctburn_lg"))

ggplot(pr, aes(x, predicted, colour = group)) +
  geom_point(position = position_dodge(.1)) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(.1)) +
  theme_classic()

tab_model(HI.SPC.year) # nothing significant 
```

# HI model - year 
```{r}
HI.SPC <- lm(meanHI ~ Slope*pctburn_lg, 
             data = SPC_data)
plot(HI.SPC)
```

# BETA model 
```{r}
BETA.SPC.year <- lmer(meanBETA ~ Slope*pctburn_lg + (1|year), 
             data = SPC_data_year)
vif(BETA.SPC.year)
```
VIFs pass 

```{r, echo=FALSE}
plot(BETA.SPC.year, type=c("p","smooth"), col.line=1)
plot(BETA.SPC.year,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)
lattice::qqmath(BETA.SPC.year)
```
I got one outlier 

```{r}
# # log transform 
# SPC_data_year$logmeanBETA <- log(abs(SPC_data_year$meanBETA))
# 
# BETA.SPC.year.log <- lmer(logmeanBETA ~ CatPF*pctburn_lg + (1|year), 
#              data = SPC_data_year)
# summary(BETA.SPC.year.log) # year is adding 0 variance 
# # nothing is really explaining this here 

```

```{r, echo=FALSE}
# plot(BETA.SPC.year.log, type=c("p","smooth"), col.line=1)
# plot(BETA.SPC.year.log,
#      sqrt(abs(resid(.)))~fitted(.),
#      type=c("p","smooth"), col.line=1)
# lattice::qqmath(BETA.SPC.year.log)
```

```{r}
pr <- ggpredict(BETA.SPC.year, terms = c("Slope", "pctburn_lg"))

ggplot(pr, aes(x, predicted, colour = group)) +
  geom_point(position = position_dodge(.1)) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(.1)) +
  theme_classic()

tab_model(BETA.SPC.year) #nothing is significant 
```


```{r}
BETA.SPC <- lm(meanBETA ~ Slope*pctburn_lg, 
             data = SPC_data)

plot(BETA.SPC)
```

# sdHI model 
```{r}
sdHI.SPC.year <- lmer(sdHI ~ Slope*pctburn_lg + (1|year), 
             data = SPC_data_year)
vif(sdHI.SPC.year)

```
Vifs pass 

```{r, echo=FALSE}
plot(sdHI.SPC.year, type=c("p","smooth"), col.line=1)
plot(sdHI.SPC.year,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)
lattice::qqmath(sdHI.SPC.year)
```
One point is really out of whack 
```{r}
pr <- ggpredict(sdHI.SPC.year, terms = c("Slope", "pctburn_lg"))

ggplot(pr, aes(x, predicted, colour = group)) +
  geom_point(position = position_dodge(.1)) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(.1)) +
  theme_classic()

tab_model(sdHI.SPC.year) # burn is significant 
```

# sdHI model 
```{r}
sdHI.SPC <- lm(sdHI ~ Slope*pctburn_lg, 
             data = SPC_data)
plot(sdHI.SPC)

```

# sdBETA model 
```{r}
sdBETA.SPC.year <- lmer(sdBETA ~ Slope*pctburn_lg + (1|year), 
             data = SPC_data_year)
vif(sdBETA.SPC.year)

```

```{r, echo=FALSE}
plot(sdBETA.SPC.year, type=c("p","smooth"), col.line=1)
plot(sdBETA.SPC.year,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)
lattice::qqmath(sdBETA.SPC.year)
```
looks like we got a couple outlier 

```{r}
pr <- ggpredict(sdBETA.SPC.year, terms = c("Slope", "pctburn_lg"))

ggplot(pr, aes(x, predicted, colour = group)) +
  geom_point(position = position_dodge(.1)) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(.1)) +
  theme_classic()

tab_model(sdBETA.SPC.year) # nothing is significant 
```

# turb # 
```{r}
turb_data_year<- CV_all_year_turb[,c("site.ID", "year", "meanHI", "meanBETA", "sdHI", "sdBETA", "Slope", "fireyear_lg", "pctburn_lg", "areaburn_lg", "PF", "NDVI", "CatBurn", "CatPF")]

turb_data<- CV_all_turb[,c("site.ID", "meanHI", "meanBETA", "sdHI", "sdBETA", "Slope", "fireyear_lg", "pctburn_lg", "areaburn_lg", "PF", "NDVI", "CatBurn", "CatPF")]

ggpairs(turb_data_year,
        columns = c("meanHI","Slope", "pctburn_lg", "PF", "NDVI"),
        ggplot2::aes(colour = site.ID)) +
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A"))

ggsave("turb_HI_pairs.pdf",
       path = here("Output_from_analysis", "12_Catchment_Characteristics_models", "plots"),
       width = 10, height = 10)
```

```{r}
ggpairs(turb_data_year,
        columns = c("meanBETA","Slope", "pctburn_lg", "PF", "NDVI"),
        ggplot2::aes(colour = site.ID)) +
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A"))

ggsave("turb_BETA_pairs.pdf",
       path = here("Output_from_analysis", "12_Catchment_Characteristics_models", "plots"),
       width = 10, height = 10)

```

```{r}
ggpairs(turb_data_year,
        columns = c("sdHI","Slope", "pctburn_lg", "PF", "NDVI"),
        ggplot2::aes(colour = site.ID)) +
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A"))

ggsave("turb_sdHI_pairs.pdf",
       path = here("Output_from_analysis", "12_Catchment_Characteristics_models", "plots"),
       width = 10, height = 10)

```

```{r}
ggpairs(turb_data_year,
        columns = c("sdBETA","Slope", "pctburn_lg", "PF", "NDVI"),
        ggplot2::aes(colour = site.ID)) +
  scale_color_manual(values = c("#3288BD", "#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A"))

ggsave("turb_sdBETA_pairs.pdf",
       path = here("Output_from_analysis", "12_Catchment_Characteristics_models", "plots"),
       width = 10, height = 10)

```

# HI model 
```{r}
HI.turb.year <- lmer(meanHI ~ Slope*pctburn_lg + (1|year), 
             data = turb_data_year)
vif(HI.turb.year)

```

```{r, echo=FALSE}
plot(HI.turb.year, type=c("p","smooth"), col.line=1)
plot(HI.turb.year,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)
lattice::qqmath(HI.turb.year)
```

```{r}
pr <- ggpredict(HI.turb.year, terms = c("Slope", "pctburn_lg"))

ggplot(pr, aes(x, predicted, colour = group)) +
  geom_point(position = position_dodge(.1)) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(.1)) +
  theme_classic()

tab_model(HI.turb.year) # nothing is significant 
summary(HI.turb.year)
```

```{r}
HI.turb <- lm(meanHI ~ Slope*pctburn_lg, 
             data = turb_data)
plot(HI.turb)

```

# BETA model 
```{r}
BETA.turb.year <- lmer(meanBETA ~ Slope*pctburn_lg + (1|year), 
             data = turb_data_year)

vif(BETA.turb.year)

```

```{r, echo=FALSE}
plot(BETA.turb.year, type=c("p","smooth"), col.line=1)
plot(BETA.turb.year,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)
lattice::qqmath(BETA.turb.year)
```

```{r}
pr <- ggpredict(BETA.turb.year, terms = c("Slope", "pctburn_lg"))

ggplot(pr, aes(x, predicted, colour = group)) +
  geom_point(position = position_dodge(.1)) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(.1)) +
  theme_classic()

tab_model(BETA.turb.year)
```

# BETA model 
```{r}
BETA.turb <- lm(meanBETA ~ Slope*pctburn_lg, 
             data = turb_data)

plot(BETA.turb)

```

# sdHI model 
```{r}
sdHI.turb.year <- lmer(sdHI ~ Slope*pctburn_lg + (1|year), 
             data = turb_data_year) # boundary (singular) fit: see ?isSingular
vif(sdHI.turb.year)

```

```{r, echo=FALSE}
plot(sdHI.turb.year, type=c("p","smooth"), col.line=1)
plot(sdHI.turb.year,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)
lattice::qqmath(sdHI.turb.year)
```
lets log transform 
```{r}
# # log transform 
# turb_data_year$logCVhi <- log(abs(turb_data_year$CVhi))
# 
# CVhi.turb.year.log <- lmer(logCVhi ~ CatPF*pctburn_lg + (1|year), 
#              data = turb_data_year)
# summary(CVhi.turb.year.log)
# 
# vif(CVhi.turb.year.log)

```

```{r, echo=FALSE}
# plot(CVhi.turb.year.log, type=c("p","smooth"), col.line=1)
# plot(CVhi.turb.year.log,
#      sqrt(abs(resid(.)))~fitted(.),
#      type=c("p","smooth"), col.line=1)
# lattice::qqmath(CVhi.turb.year.log)
```


```{r}
pr <- ggpredict(sdHI.turb.year, terms = c("Slope", "pctburn_lg"))

ggplot(pr, aes(x, predicted, colour = group)) +
  geom_point(position = position_dodge(.1)) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(.1)) +
  theme_classic()

tab_model(sdHI.turb.year)
```

# sdHI model 
```{r}
sdHI.turb <- lm(sdHI ~ Slope*pctburn_lg, 
             data = turb_data) 
plot(sdHI.turb)

```

# sdBETA model 
```{r}
sdBETA.turb.year <- lmer(sdBETA ~ Slope*pctburn_lg + (1|year), 
             data = turb_data_year) # boundary (singular) fit: see ?isSingular
vif(sdBETA.turb.year)
```

```{r, echo=FALSE}
plot(sdBETA.turb.year, type=c("p","smooth"), col.line=1)
plot(sdBETA.turb.year,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)
lattice::qqmath(sdBETA.turb.year)
```


```{r}
pr <- ggpredict(sdBETA.turb.year, terms = c("Slope", "pctburn_lg"))

ggplot(pr, aes(x, predicted, colour = group)) +
  geom_point(position = position_dodge(.1)) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(.1)) +
  theme_classic()

tab_model(sdBETA.turb.year) # nothing is significant 
```


# sdBETA model 
```{r}
sdBETA.turb <- lm(sdBETA ~ Slope*pctburn_lg, 
             data = turb_data) 
plot(sdBETA.turb)
```



### PLOTTING ###
# HI 
```{r}
ggplot(CV.all.year, aes(x = pctburn_lg, y = meanHI, color = CatPF)) +
  xlab("Burn") +
  ylab("Hysteresis") +
  geom_point() +
  geom_smooth(method = "lm", na.rm = TRUE, fullrange = TRUE, aes(group = CatPF)) +
  scale_color_manual(values = c("#0072B2", "#CC79A7"), "PF Extent") +
  stat_poly_eq(formula = y~x,
               label.y = "top", label.x = "left",
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
               parse = TRUE) + 
  theme_classic() +
  facet_wrap(~response_var, scales = "free")

ggsave(path = "~/Documents/Storms_clean_repo/plots/Catchment_characteristics", 
       filename = "HI_burn.pdf",
       width = 10, height = 10)


```

# BETA
```{r}
ggplot(CV.all.year, aes(x = pctburn_lg, y = meanBETA, color = CatPF)) +
  xlab("Burn") +
  ylab("BETA") +
  geom_point() +
  geom_smooth(method = "lm", na.rm = TRUE, fullrange = TRUE, aes(group = CatPF)) +
  scale_color_manual(values = c("#0072B2", "#CC79A7"), "PF Extent") +
  stat_poly_eq(formula = y~x,
               label.y = "top", label.x = "left",
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
               parse = TRUE) + 
  theme_classic() +
  facet_wrap(~response_var, scales = "free")

ggsave(path = "~/Documents/Storms_clean_repo/plots/Catchment_characteristics", 
       filename = "BETA_burn.pdf",
       width = 10, height = 10)

```


# CVhi
```{r}
ggplot(CV.all.year, aes(x = pctburn_lg, y = CVhi, color = CatPF)) +
  xlab("Burn") +
  ylab("CV Hysteresis") +
  geom_point() +
  geom_smooth(method = "lm", na.rm = TRUE, fullrange = TRUE, aes(group = CatPF)) +
  scale_color_manual(values = c("#0072B2", "#CC79A7"), "PF Extent") +
  stat_poly_eq(formula = y~x,
               label.y = "top", label.x = "left",
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
               parse = TRUE) + 
  theme_classic() +
  facet_wrap(~response_var, scales = "free")

ggsave(path = "~/Documents/Storms_clean_repo/plots/Catchment_characteristics", 
       filename = "CVhi_burn.pdf",
       width = 10, height = 10)


```

# CVbeta
```{r}
ggplot(CV.all.year, aes(x = pctburn_lg, y = CVbeta, color = CatPF)) +
  xlab("Burn") +
  ylab("CV BETA") +
  geom_point() +
  geom_smooth(method = "lm", na.rm = TRUE, fullrange = TRUE, aes(group = CatPF)) +
  scale_color_manual(values = c("#0072B2", "#CC79A7"), "PF Extent") +
  stat_poly_eq(formula = y~x,
               label.y = "top", label.x = "left",
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
               parse = TRUE) + 
  theme_classic() +
  facet_wrap(~response_var, scales = "free")

ggsave(path = "~/Documents/Storms_clean_repo/plots/Catchment_characteristics", 
       filename = "CVbeta_burn.pdf",
       width = 10, height = 10)



```
