---
title: "16_RainGauge"
output: html_document
---

This script reads in and plots Rain Gauge data at FRCH, STRT, VAUL, CARI, CRREL sites for 2021 from our HOBOs and POKE from LTER data ###

Step 1: Import raw data from HOBOware # File path directory DoD Project->2021 AK Sensors-> Rain Gauge-> "site"
Step 2: Plot data # HOBOware data comes in the form of cumulative precip....you have to put it in instanteous 15 minute intervals
Step 3: output csv with Site, DateTime, and Precip


# Import Libraries #
```{r}
library(readr)
library(ggplot2)
library(dplyr)
library(lubridate)
library(RColorBrewer)
library(gridExtra)
library(here)
```

```{r}
CPCRW <- read_csv("~/Documents/Storms_clean_repo/Climate/Precip/CPCRW_CREEL_percip_2022.csv",
                                    skip = 5)
Eielson <- read_csv("~/Documents/Storms_clean_repo/Climate/Precip/Eielson_2022_Precip.csv", 
                                skip = 6)
Salcha_2022 <- read_csv("~/Documents/Storms_clean_repo/Climate/Precip/USGS_Salcha_2022_precip.csv", 
                                    skip = 26)
```

# CPCRW Caribou Peak 
```{r}
# PLOT data 
ggplot(CPCRW) +
  geom_line(aes(x = Time, y = CPCRW$`CPCRW Caribou Peak: TippingBucket_TOT mm CPEAK[mm]`)) +
  xlab("Date") +
  ylab("Cumulative Precipitation (mm)") +
  ggtitle("CPCRW CARI Rain Gauge")

```
# CRRREL Main Met station 
```{r}
ggplot(CPCRW) +
  geom_line(aes(x = Time, y = CPCRW$`CPCRW CRREL Main Met Station: TippingBucket_TOT mm  CRREL[mm]`)) +
  xlab("Date") +
  ylab("Cumulative Precipitation (mm)") +
  ggtitle("CPCRW CRREL Rain Gauge")

```

```{r}
ggplot() +
  geom_line(data = CPCRW, aes(x = Time, y = CPCRW$`CPCRW Caribou Peak: TippingBucket_TOT mm CPEAK[mm]`), color = "blue") +
  geom_line(data = CPCRW, aes(x = Time, y = CPCRW$`CPCRW CRREL Main Met Station: TippingBucket_TOT mm  CRREL[mm]`)) +
  ggtitle("CPCRW/CRREL comparison Rain Gauge")

```
Caribou peak (blue) seems to record a lot more rain...in the past I have averaged between the two of these to get our "Poker" record 

```{r}
CPCRW$month <- format(as.Date(CPCRW$Time), "%m")

CPCRW %>% 
  group_by(month) %>% 
  summarise(CRREL = sum(`CPCRW CRREL Main Met Station: TippingBucket_TOT mm  CRREL[mm]`),
            CARI = sum(`CPCRW Caribou Peak: TippingBucket_TOT mm CPEAK[mm]`))

# CRREL: 202.946
# CARI: 279.91
```
```{r}
names(CPCRW) <- c("datetimeAK", "CARI", "CRREL", "month")
CPCRW$mean <- rowMeans(CPCRW[,c('CARI', 'CRREL')], na.rm=TRUE)

write.csv(CPCRW, "~/Documents/Storms_clean_repo/Climate/Precip/CPCRW.RainGauge.2022.final.csv")

```
# Eielson #
```{r}
Eielson$Date_Time <-mdy_hms(Eielson$Date_Time) 
Eielson$precip_accum_one_hour_set_1 <- as.numeric(Eielson$precip_accum_one_hour_set_1)

# # turn into instantaneous precip
# Eielson$inst_rainfall_mm = 0.2

min<-cut(Eielson$Date_Time, breaks="15 min")
Eielson.st <- as.data.frame(aggregate(precip_accum_one_hour_set_1 ~ min, data = Eielson, FUN=function(x) 
  sum=sum(x)))
Eielson.st$datetimeAK<-as.POSIXct(Eielson.st$min, "%Y-%m-%d %H:%M:%S", tz="America/Anchorage")

Eielson.st$precip_accum_one_hour_set_1 <- Eielson.st$precip_accum_one_hour_set_1 * 25.4

ggplot(Eielson.st) +
  geom_line(aes(x = datetimeAK, y = precip_accum_one_hour_set_1)) +
  xlab("Date") +
  ylab("Cumulative Precipitation (mm)") +
  ggtitle("CPCRW CARI Rain Gauge")

```


```{r}
Eielson.st$month <- format(as.Date(Eielson.st$datetimeAK), "%m")

Eielson.st %>% 
  group_by(month) %>% 
  summarise(Eielson = sum(precip_accum_one_hour_set_1))

# 159.1818 # total 

```


# CRRREL Main Met station 
```{r}
Salcha_2022 <- Salcha_2022[-1, ]

Salcha_2022$datetimeAK <- mdy_hm(Salcha_2022$datetime)
names(Salcha_2022) <- c("Agency", "Site", "dt", "tz", "precip", "type", "datetimeAK")
Salcha_2022$precip <- as.numeric(Salcha_2022$precip)

# # turn into instantaneous precip
# Eielson$inst_rainfall_mm = 0.2

min<-cut(Salcha_2022$datetimeAK, breaks="15 min")
Salcha.st <- as.data.frame(aggregate(precip ~ min, data = Salcha_2022, FUN=function(x) 
  sum=sum(x)))
Salcha.st$datetimeAK<-as.POSIXct(Salcha.st$min, "%Y-%m-%d %H:%M:%S", tz="America/Anchorage")

Salcha.st$precip <- Salcha.st$precip * 25.4


ggplot(Salcha.st) +
  geom_line(aes(x = datetimeAK, y = precip)) +
  xlab("Date") +
  ylab("Cumulative Precipitation (mm)") +
  ggtitle("Salcha Rain Gauge")

```

```{r}
Salcha.st$month <- format(as.Date(Salcha.st$datetimeAK), "%m")

Salcha.st %>% 
  group_by(month) %>% 
  summarise(Salcha = sum(precip))

# 159.1818 # total 
```
